### 2011-04-04 paper/paper.tex
Began paper

\documentclass{article}
\title{Word Sense Disambiguation}
\author{
Alec Story
Ansu Abraham
Craig Frey
Dustin Tiedemann
Michael Zhu
Thomas Levine
Whitney Foster
}

\begin{document}
\maketitle
\end{document}

### 2011-04-05 paper/paper.tex
part two

@@
 \documentclass{article}
-\title{Word Sense Disambiguation}
-\author{
-Alec Story
-Ansu Abraham
-Craig Frey
-Dustin Tiedemann
-Michael Zhu
-Thomas Levine
-Whitney Foster
-}
+\begin{document}
 
-\begin{document}
-\maketitle
-\end{document}
+\section{Selecting optimal feature combination}
+\newcommand\ward{forward} %or maybe backwards
+We used a \ward stepwise approach to indentifying optimal feature combinations.
+We first ran the system with all features on, producing a total of $256=2^8$ combinations.
+We then used backwards stepwise regression to identify feature combinations
+with a small number of features but with high performance

### 2011-04-11 scripts/score_calls.sh
scorer

@@ -1,5 +1,6 @@
 tmp=$1
-run=`echo $tmp|sed s/tmp//`
+key=$2
+run=`echo $tmp|sed s/^.*tmp//`
 
 #Convert to a nice format
 ./scoring/scorer2 $tmp $key  -v|sed -n -e 's/^score for //p'|

### 2011-04-11 scripts/make_calls.sh
generate more calls

@@ -5,13 +5,15 @@ key=$1
 
 #Edit the nested for loops to select a series of feature combinations
 run=1
-for classifier in -m -n -t; do
-  for bootstrap in '' '-b 4' '-b 16' ; do #Fix how a lack of bootstrapping for trees doesn't work well here
-    for colocation in '-l 0' '-l 1' '-l 2'; do # -l NUM is the colocation distance, 0 is "don't use it"
+for classifier in -n -t; do
+  for bootstrap in '' '-b 4' '-b 16' '-b 64'; do #Fix how a lack of bootstrapping for trees doesn't work well here
+    for colocation in '-l 0' '-l 1' '-l 2' '-l 3'; do # -l NUM is the colocation distance, 0 is "don't use it"
       for coocurrence in '' -r; do # -r enables cooccurrence usae
         for base_word in '' -e; do # -e enables base word usage
 #Run the actual system
-echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run" 
+echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
+#Remove runs with bootstrapping and trees
+grep -v '\-t \-b' 
 run=$((run+1))
         done
       done

### 2011-04-11 paper/paper.Rnw
more paper writing

\documentclass{article}
\title{Word Sense Disambiguation}
\author{
Alec Story
Ansu Abraham
Craig Frey
Dustin Tiedemann
Michael Zhu
Thomas Levine
Whitney Foster
}

\begin{document}
\maketitle

\section{Selecting optimal feature combination}
\newcommand\ward{forward} %or maybe backwards
We used a \ward stepwise approach to indentifying optimal feature combinations.
We first ran the system with all features on, producing a total of $256=2^8$ combinations.
We then used backwards stepwise regression to identify feature combinations
with a small number of features but with high performance

\section{Confidence Cutoffs}

NLTK provides probability measures for each of its guesses when using the
maximum entropy and the naive Bayes learning methods.  We harnessed these to
determine the cutoff for making a guess, or resorting to a ``U.''  Occasional
unknowns also occur because such unknowns are present in the training data, and
we made no effort to remove them, so the learning algorithm views them as any
other label.

% Should we mention which cutoff we used?  Which did we use?

\section{Bootstrapping}

We used the same probability measure from the confidence cutoffs to fuel a
bootstrapping method.  Instead of directly taking the output of the classifier,
we instead looked at its performance on the test data, and wherever it was very
confident, we copied that test instance to the training data, and repeated this
cycle for a fixed number of cycles.  Once we had enriched the training data, we
ran the classifier a final time to perform classification.

Fortunately, the classifiers were very fast, and almost all of the time the
system spends is in reading input and building feature sets, which don't need to
be repeated, so bootstrapping is very cheap to include.

% Should we mention which probability measure we used?  Which did we use?  How
% many iterations?

\end{document}

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/core/feature/function/AddressFunction.java
dependency parsing first pass, need to figure out what to do with dependency tree

@@ -1,0 +1,39 @@
+package org.maltparser.core.feature.function;
+
+import org.maltparser.core.feature.value.AddressValue;
+
+/**
+*
+*
+* @author Johan Hall
+*/
+public abstract class AddressFunction implements Function {
+	protected AddressValue address;
+	public AddressFunction() {
+		address = new AddressValue(this);
+	}
+	
+	/**
+	 * Returns the address value of address function
+	 * 
+	 * @return the address value of address function
+	 */
+	public AddressValue getAddressValue() {
+		return address;
+	}
+	
+	public boolean equals(Object obj) {
+		if (this == obj)
+			return true;
+		if (obj == null)
+			return false;
+		if (getClass() != obj.getClass())
+			return false;
+
+		return address.equals(((AddressFunction)obj).getAddressValue());
+	}
+
+	public String toString() {
+		return address.toString();
+	}
+}

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/core/feature/system/FeatureEngine.java

@@ -1,0 +1,163 @@
+package org.maltparser.core.feature.system;
+
+import java.io.IOException;
+import java.io.InputStream;
+import java.net.MalformedURLException;
+import java.net.URL;
+import java.util.HashMap;
+
+import javax.xml.parsers.DocumentBuilder;
+import javax.xml.parsers.DocumentBuilderFactory;
+import javax.xml.parsers.ParserConfigurationException;
+
+import org.maltparser.core.config.Configuration;
+import org.maltparser.core.config.ConfigurationRegistry;
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.core.feature.FeatureException;
+import org.maltparser.core.feature.function.Function;
+import org.maltparser.core.helper.Util;
+import org.maltparser.core.plugin.Plugin;
+import org.maltparser.core.plugin.PluginLoader;
+import org.w3c.dom.Element;
+import org.w3c.dom.NodeList;
+import org.xml.sax.SAXException;
+/**
+ *  
+ *
+ * @author Johan Hall
+ * @since 1.0
+**/
+public class FeatureEngine extends HashMap<String, FunctionDescription> {
+	public final static long serialVersionUID = 3256444702936019250L;
+	protected Configuration configuration;
+	public FeatureEngine(Configuration configuration) {
+		super();
+		setConfiguration(configuration);
+	}
+	
+	public Function newFunction(String functionName, ConfigurationRegistry registry) throws MaltChainedException {
+		FunctionDescription funcDesc = get(functionName);
+		if (funcDesc == null) {
+			return null;
+		}
+		return funcDesc.newFunction(registry);
+	}
+	
+	public void load(String urlstring) throws MaltChainedException {
+		load(Util.findURL(urlstring));
+	}
+	
+	public void load(PluginLoader plugins) throws MaltChainedException {
+		 for (Plugin plugin : plugins) {
+			URL url = null;
+			try {
+				url = new URL("jar:"+plugin.getUrl() + "!/appdata/plugin.xml");
+			} catch (MalformedURLException e) {
+				throw new FeatureException("Malformed URL: 'jar:"+plugin.getUrl() + "!plugin.xml'", e);
+			}
+			try { 
+				InputStream is = url.openStream();
+				is.close();
+			} catch (IOException e) {
+				continue;
+			}
+
+			load(url);
+		}
+	}
+	
+	public void load(URL specModelURL) throws MaltChainedException {
+        try {
+            DocumentBuilderFactory dbf = DocumentBuilderFactory.newInstance();
[…]

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/core/symbol/nullvalue/NullValues.java

@@ -1,0 +1,147 @@
+package org.maltparser.core.symbol.nullvalue;
+
+import java.util.HashMap;
+import java.util.SortedMap;
+import java.util.TreeMap;
+
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.core.symbol.SymbolException;
+import org.maltparser.core.symbol.SymbolTable;
+/**
+
+
+@author Johan Hall
+@since 1.0
+ */
+public abstract class NullValues {
+	protected enum NullValueDegree {
+		NONE, ONE, ROOTLABEL, ROOTNODE, NOVALUE
+	};
+	public enum NullValueId {
+		NO_NODE, ROOT_NODE, NO_VALUE
+	};
+	protected HashMap<NullValueId, String> nullValue2SymbolMap;
+	protected HashMap<NullValueId, Integer> nullValue2CodeMap;
+	protected HashMap<String, Integer> symbol2CodeMap;
+	protected SortedMap<Integer, String> code2SymbolMap;
+	protected SymbolTable table;
+	protected NullValueDegree nullValueEncoding;
+	protected String nullValueStrategy;
+	protected int nextCode;
+	
+	public NullValues(SymbolTable table) {
+		setSymbolTable(table);
+		nullValue2SymbolMap = new HashMap<NullValueId, String>();
+		nullValue2CodeMap = new HashMap<NullValueId, Integer>();
+		symbol2CodeMap = new HashMap<String, Integer>();
+		code2SymbolMap = new TreeMap<Integer, String>();
+	}
+	
+	private void setSymbolTable(SymbolTable table) {
+		this.table = table; 
+	}
+	
+	public SymbolTable getSymbolTable() {
+		return table;
+	}
+	
+	public String getNullValueStrategy() {
+		return nullValueStrategy;
+	}
+
+	protected void setNullValueStrategy(String nullValueStrategy) {
+		this.nullValueStrategy = nullValueStrategy;
+	}
+
+	public NullValueDegree getNullValueEncoding() {
+		return nullValueEncoding;
+	}
+	
+	public int getNextCode() {
+		return nextCode;
+	}
+
+	protected void setNextCode(int nextCode) {
+		this.nextCode = nextCode;
+	}
+	
+	public boolean isNullValue(int code) {
+		return code2SymbolMap.containsKey(code);
+	}
+	
[…]

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/core/symbol/trie/TrieSymbolTable.java

@@ -1,0 +1,343 @@
+package org.maltparser.core.symbol.trie;
+
+import java.io.BufferedReader;
+import java.io.BufferedWriter;
+import java.io.IOException;
+import java.util.Set;
+import java.util.SortedMap;
+import java.util.TreeMap;
+
+import org.apache.log4j.Logger;
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.core.io.dataformat.ColumnDescription;
+import org.maltparser.core.symbol.SymbolException;
+import org.maltparser.core.symbol.SymbolTable;
+import org.maltparser.core.symbol.nullvalue.InputNullValues;
+import org.maltparser.core.symbol.nullvalue.NullValues;
+import org.maltparser.core.symbol.nullvalue.OutputNullValues;
+import org.maltparser.core.symbol.nullvalue.NullValues.NullValueId;
+/**
+
+@author Johan Hall
+@since 1.0
+*/
+public class TrieSymbolTable implements SymbolTable {
+	private final String name;
+	private final Trie trie;
+	private final SortedMap<Integer, TrieNode> codeTable;
+	private int columnCategory;
+	private NullValues nullValues;
+	private int valueCounter;
+    /** Cache the hash code for the symbol table */
+    private int cachedHash;
+    
+	public TrieSymbolTable(String name, Trie trie, int columnCategory, String nullValueStrategy) throws MaltChainedException {
+		this.name = name;
+		this.trie = trie;
+		this.columnCategory = columnCategory;
+		codeTable = new TreeMap<Integer, TrieNode>();
+		if (columnCategory == ColumnDescription.INPUT) {
+			nullValues = new InputNullValues(nullValueStrategy, this);
+		} else if (columnCategory == ColumnDescription.DEPENDENCY_EDGE_LABEL) {
+			nullValues = new OutputNullValues(nullValueStrategy, this, null);
+		} else {
+			nullValues = new InputNullValues(nullValueStrategy, this);
+		}
+		valueCounter = nullValues.getNextCode();
+	}
+
+	public TrieSymbolTable(String name,  Trie trie, int columnCategory, String nullValueStrategy, String rootLabel) throws MaltChainedException {
+		this.name = name;
+		this.trie = trie;
+		this.columnCategory = columnCategory;
+		codeTable = new TreeMap<Integer, TrieNode>();
+		if (columnCategory == ColumnDescription.INPUT) {
[…]

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/core/syntaxgraph/MappablePhraseStructureGraph.java

@@ -1,0 +1,572 @@
+package org.maltparser.core.syntaxgraph;
+
+import java.util.Iterator;
+import java.util.NoSuchElementException;
+import java.util.Observable;
+import java.util.Set;
+import java.util.SortedMap;
+import java.util.SortedSet;
+import java.util.TreeMap;
+import java.util.TreeSet;
+
+
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.core.helper.SystemLogger;
+import org.maltparser.core.pool.ObjectPoolList;
+import org.maltparser.core.symbol.SymbolTable;
+import org.maltparser.core.symbol.SymbolTableHandler;
+import org.maltparser.core.syntaxgraph.ds2ps.LosslessMapping;
+import org.maltparser.core.syntaxgraph.edge.Edge;
+import org.maltparser.core.syntaxgraph.edge.GraphEdge;
+import org.maltparser.core.syntaxgraph.node.ComparableNode;
+import org.maltparser.core.syntaxgraph.node.DependencyNode;
+import org.maltparser.core.syntaxgraph.node.Node;
+import org.maltparser.core.syntaxgraph.node.NonTerminal;
+import org.maltparser.core.syntaxgraph.node.NonTerminalNode;
+import org.maltparser.core.syntaxgraph.node.PhraseStructureNode;
+import org.maltparser.core.syntaxgraph.node.Root;
+import org.maltparser.core.syntaxgraph.node.TokenNode;
+/**
+*
+*
+* @author Johan Hall
+*/
+public class MappablePhraseStructureGraph extends Sentence implements DependencyStructure, PhraseStructure {
+	private final ObjectPoolList<Edge> edgePool;
+	private final SortedSet<Edge> graphEdges;
+	private Root root;
+	private boolean singleHeadedConstraint;
+	private final SortedMap<Integer, NonTerminal> nonTerminalNodes;
+	private final ObjectPoolList<NonTerminal> nonTerminalPool;
+	private LosslessMapping mapping;
+	private RootLabels rootLabels;
+	
+	public MappablePhraseStructureGraph(SymbolTableHandler symbolTables) throws MaltChainedException {
+		super(symbolTables);
+		setSingleHeadedConstraint(true);
+		root = new Root();
+		root.setBelongsToGraph(this);
+		graphEdges = new TreeSet<Edge>();
+		edgePool = new ObjectPoolList<Edge>() {
[…]

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/core/syntaxgraph/reader/TigerXMLReader.java

@@ -1,0 +1,449 @@
+package org.maltparser.core.syntaxgraph.reader;
+
+import java.io.BufferedReader;
+import java.io.FileInputStream;
+import java.io.FileNotFoundException;
+import java.io.IOException;
+import java.io.InputStream;
+import java.io.InputStreamReader;
+import java.io.UnsupportedEncodingException;
+import java.net.URL;
+import java.util.SortedMap;
+import java.util.regex.PatternSyntaxException;
+
+import javax.xml.stream.XMLInputFactory;
+import javax.xml.stream.XMLStreamConstants;
+import javax.xml.stream.XMLStreamException;
+import javax.xml.stream.XMLStreamReader;
+
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.core.io.dataformat.DataFormatException;
+import org.maltparser.core.io.dataformat.DataFormatInstance;
+import org.maltparser.core.symbol.SymbolTable;
+import org.maltparser.core.syntaxgraph.MappablePhraseStructureGraph;
+import org.maltparser.core.syntaxgraph.PhraseStructure;
+import org.maltparser.core.syntaxgraph.SyntaxGraphException;
+import org.maltparser.core.syntaxgraph.TokenStructure;
+import org.maltparser.core.syntaxgraph.edge.Edge;
+import org.maltparser.core.syntaxgraph.node.NonTerminalNode;
+import org.maltparser.core.syntaxgraph.node.PhraseStructureNode;
+
+/**
+*
+*
+* @author Johan Hall
+*/
+public class TigerXMLReader implements SyntaxGraphReader {
+//	private TigerXMLHeader header;
+	private XMLStreamReader reader;
+	private int sentenceCount;
+	private DataFormatInstance dataFormatInstance;
+	private StringBuffer ntid;
+	private final StringBuilder graphRootID;
+//	private StringBuilder elementContent; 
+//	private StringBuilder valueName;
+//	private StringBuilder currentFeatureName;
+//	private Domain domain;
+//	private boolean collectChar = false;
+	private String optionString;
+	private int START_ID_OF_NONTERMINALS = 500;
+	
+	
+	public TigerXMLReader() {
+		this.ntid = new StringBuffer();
+//		elementContent = new StringBuilder();
+//		valueName = new StringBuilder();
+//		currentFeatureName = new StringBuilder(); 
+		graphRootID = new StringBuilder(); 
+	}
+	
[…]

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/core/syntaxgraph/writer/WriteChartItem.java

@@ -1,0 +1,245 @@
+package org.maltparser.core.syntaxgraph.writer;
+
+
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.core.flow.FlowChartInstance;
+import org.maltparser.core.flow.item.ChartItem;
+import org.maltparser.core.flow.spec.ChartItemSpecification;
+import org.maltparser.core.io.dataformat.DataFormatException;
+import org.maltparser.core.io.dataformat.DataFormatInstance;
+import org.maltparser.core.options.OptionManager;
+import org.maltparser.core.syntaxgraph.TokenStructure;
+
+/**
+*
+*
+* @author Johan Hall
+*/
+public class WriteChartItem extends ChartItem {
+	private String outputFormatName;
+	private String outputFileName;
+	private String outputCharSet;
+	private String writerOptions;
+	private Class<? extends SyntaxGraphWriter> graphWriterClass;
+	
+	private String nullValueStrategy;
+	private String rootLabels;
+	
+	private SyntaxGraphWriter writer;
+	private String sourceName;
+	private String optiongroupName;
+	private DataFormatInstance outputDataFormatInstance;
+	private TokenStructure cachedGraph = null;
+	
+	public WriteChartItem() { super(); }
+	
+	public void initialize(FlowChartInstance flowChartinstance, ChartItemSpecification chartItemSpecification) throws MaltChainedException {
+		super.initialize(flowChartinstance, chartItemSpecification);
+		
+		for (String key : chartItemSpecification.getChartItemAttributes().keySet()) {
+			if (key.equals("source")) {
+				sourceName = chartItemSpecification.getChartItemAttributes().get(key);
+			} else if (key.equals("optiongroup")) {
+				optiongroupName = chartItemSpecification.getChartItemAttributes().get(key);
+			}
+		}
+		
+		if (sourceName == null) {
+			sourceName = getChartElement("write").getAttributes().get("source").getDefaultValue();
+		} else if (optiongroupName == null) {
+			optiongroupName = getChartElement("write").getAttributes().get("optiongroup").getDefaultValue();
+		}
+		
+		setOutputFormatName(OptionManager.instance().getOptionValue(getOptionContainerIndex(), optiongroupName, "format").toString());
[…]

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/parser/algorithm/covington/CovingtonProjective.java

@@ -1,0 +1,42 @@
+package org.maltparser.parser.algorithm.covington;
+
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.core.syntaxgraph.DependencyStructure;
+import org.maltparser.parser.SingleMalt;
+
+/**
+ * 
+ * @author Joakim Nivre
+ * @author Johan Hall
+ * @since 1.0
+*/
+public class CovingtonProjective extends Covington {
+
+	public CovingtonProjective(SingleMalt configuration) throws MaltChainedException {
+		super(configuration);
+	}
+	
+	protected void updateLeft(DependencyStructure dg, int trans) throws MaltChainedException {
+		if (trans == SHIFT  || trans == RIGHTARC) {
+			left = leftstop - 1;
+		} else if (trans == NOARC) {
+			if (dg.getTokenNode(input.get(left).getIndex()) != null && dg.getTokenNode(input.get(left).getIndex()).hasHead()) {
+				left = dg.getTokenNode(input.get(left).getIndex()).getHead().getIndex();
+			} else {
+				left = leftstop - 1;
+			}
+		} else { 
+			left--;
+			while (left >= leftstop) {
+				if (input.get(right).findComponent() != input.get(left).findComponent()) {
+					break;
+				}
+				left--;
+			}
+		}
+	}
+	
+	public String getName() {
+		return "covproj";
+	}
+}

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/parser/algorithm/nivre/Nivre.java

@@ -1,0 +1,322 @@
+package org.maltparser.parser.algorithm.nivre;
+
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Stack;
+
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.core.symbol.SymbolTable;
+import org.maltparser.core.symbol.TableHandler;
+import org.maltparser.core.syntaxgraph.DependencyStructure;
+import org.maltparser.core.syntaxgraph.LabelSet;
+import org.maltparser.core.syntaxgraph.edge.Edge;
+import org.maltparser.core.syntaxgraph.node.DependencyNode;
+import org.maltparser.parser.SingleMalt;
+import org.maltparser.parser.algorithm.ParsingAlgorithm;
+import org.maltparser.parser.algorithm.ParsingException;
+import org.maltparser.parser.algorithm.helper.TransitionTable;
+import org.maltparser.parser.algorithm.helper.TransitionTableHandler;
+import org.maltparser.parser.history.GuideUserHistory;
+import org.maltparser.parser.history.History;
+import org.maltparser.parser.history.action.GuideUserAction;
+import org.maltparser.parser.history.container.ActionContainer;
+
+/**
+ * 
+ * @author Joakim Nivre
+ * @author Johan Hall
+ * @since 1.0
+*/
+public abstract class Nivre implements ParsingAlgorithm {	
+	// Transitions
+	protected static final int SHIFT = 1;
+
+	// Root Handling
+	public static final int STRICT = 1; //root tokens unattached, Reduce not permissible
+	public static final int RELAXED = 2; //root tokens unattached, Reduce permissible
+	public static final int NORMAL = 3; //root tokens attached to Root with RightArc
+
+	protected GuideUserHistory history;
+	protected ArrayList<ActionContainer> actionContainers;
+	protected ActionContainer transActionContainer;
+	protected ActionContainer pushActionContainer;
+	protected TransitionTable pushTable;
+	protected HashSet<ActionContainer> arcLabelActionContainers;
+	protected final SingleMalt configuration;
+	protected GuideUserAction currentAction;
+	protected HashMap<String, TableHandler> tableHandlers;
+	protected TransitionTableHandler transitionTableHandler;
+	protected int rootHandling;
+	protected boolean postProcessing;
+	protected final Stack<DependencyNode> stack;
+	protected final Stack<DependencyNode> input;
[…]

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/parser/algorithm/nivre/NivreStandard.java

@@ -1,0 +1,157 @@
+package org.maltparser.parser.algorithm.nivre;
+
+
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.core.syntaxgraph.DependencyStructure;
+import org.maltparser.core.syntaxgraph.LabelSet;
+import org.maltparser.core.syntaxgraph.edge.Edge;
+import org.maltparser.parser.SingleMalt;
+import org.maltparser.parser.algorithm.ParsingException;
+import org.maltparser.parser.algorithm.helper.TransitionTable;
+import org.maltparser.parser.history.container.ActionContainer;
+
+/**
+ * 
+ * @author Joakim Nivre
+ * @author Johan Hall
+ * @since 1.0
+*/
+public class NivreStandard extends Nivre {
+	protected static final int RIGHTARC = 2;
+	protected static final int LEFTARC = 3;
+	
+	public NivreStandard(SingleMalt configuration) throws MaltChainedException {
+		super(configuration);
+	}
+	
+	protected void transition(DependencyStructure parseDependencyGraph) throws MaltChainedException {
+		currentAction.getAction(actionContainers);
+		while (checkParserAction(parseDependencyGraph) == false) {
+			if (configuration.getMode() == SingleMalt.LEARN || configuration.predictFromKBestList(currentAction) == false) {
+				updateActionContainers(SHIFT, null); // default parser action
+				break;
+			}
+			currentAction.getAction(actionContainers);
+		}
+		Edge e = null;
+		switch (getTransition()) {
+		case LEFTARC:
+			e = parseDependencyGraph.addDependencyEdge(input.peek().getIndex(), stack.peek().getIndex());
+			addEdgeLabels(e);
+			stack.pop();
+			break;
+		case RIGHTARC:
+			e = parseDependencyGraph.addDependencyEdge(stack.peek().getIndex(), input.peek().getIndex());
+			addEdgeLabels(e);
+			input.pop();
+			if (!stack.peek().isRoot()) {
+				input.push(stack.pop());	
+			}
+			break;
+		default:
+			stack.push(input.pop()); // SHIFT
+			break;
+		}
+	}
+	
+	protected boolean checkParserAction(DependencyStructure dg) throws MaltChainedException {
+		int trans = getTransition();
+		if ((trans == LEFTARC || trans == RIGHTARC) && !isActionContainersLabeled()) {
+			// Label code is null for transitions LEFTARC and RIGHTARC
+			return false;
+		}
[…]

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/parser/guide/instance/InstanceModel.java

@@ -1,0 +1,13 @@
+package org.maltparser.parser.guide.instance;
+
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.parser.guide.Model;
+import org.maltparser.parser.history.action.SingleDecision;
+
+public interface InstanceModel extends Model {
+	public void addInstance(SingleDecision decision) throws MaltChainedException;
+	public boolean predict(SingleDecision decision) throws MaltChainedException;
+	public void train() throws MaltChainedException;
+	public void increaseFrequency();
+	public void decreaseFrequency();
+}

### 2011-04-11 MaltParser/malt-1.2/src/org/maltparser/parser/history/kbest/ScoredKBestList.java

@@ -1,0 +1,66 @@
+package org.maltparser.parser.history.kbest;
+
+import org.maltparser.core.exception.MaltChainedException;
+import org.maltparser.parser.history.action.SingleDecision;
+/**
+*
+* @author Johan Hall
+* @since 1.1
+**/
+public class ScoredKBestList extends KBestList{
+	public ScoredKBestList(SingleDecision action) {
+		this(-1, action);
+	}
+
+	public ScoredKBestList(Integer k, SingleDecision action) {
+		super(k, action);
+	}
+	
+	protected void initKBestList() {
+		for (int i=0; i < this.k; i++) {
+			kBestList.add(new ScoredCandidate());
+		}
+	}
+	
+	public void add(int actionCode, float score) throws MaltChainedException {
+		if (k != -1 && addCandidateIndex >= k) { return; }
+		if (addCandidateIndex >= kBestList.size()) { kBestList.add(new ScoredCandidate()); }
+		if (!(kBestList.get(addCandidateIndex) instanceof ScoredCandidate)) {
+			super.add(actionCode);
+			return;
+		}
+		ScoredCandidate scand = (ScoredCandidate)kBestList.get(addCandidateIndex);
+		scand.setActionCode(actionCode);
+		scand.setScore(score);
+		if (addCandidateIndex == 0) {
+			if (decision instanceof SingleDecision) {
+				((SingleDecision)decision).addDecision(actionCode);
+			}
+			topCandidateIndex++;
+		}
+		addCandidateIndex++;
+	}
+	
+	public void add(String symbol, float score) throws MaltChainedException {
+		if (decision instanceof SingleDecision) {
+			this.add(((SingleDecision)decision).getDecisionCode(symbol), score);
+		}
+	}
+	
+	public float peekNextKBestScore() {
+		if (!(kBestList.get(addCandidateIndex) instanceof ScoredCandidate)) {
+			return Float.NaN;
+		}
+		if (addCandidateIndex != 0 && topCandidateIndex < addCandidateIndex && topCandidateIndex < kBestList.size()) {
+			return ((ScoredCandidate)kBestList.get(topCandidateIndex)).getScore();
+		}
+		return Float.NaN;
+	}
+	
+	/* (non-Javadoc)
+	 * @see java.lang.Object#toString()
+	 */
+	public String toString() {
+		return super.toString();
+	}
+}

### 2011-04-11 parser.py

@@ -1,0 +1,13 @@
+#!/usr/bin/env python
+import os
+os.environ['MALTPARSERHOME']='MaltParser/malt-1.2'
+import nltk
+import nltk.parse.malt as malt
+
+m = malt.MaltParser()
+m.train_from_file('MaltParser/engmalt.linear.mco')
+
+STR = "There is beauty in the bellow of the blast."
+
+g = m.parse(STR)
+print g.tree()

### 2011-04-12 scripts/score_calls.sh
simplify scoring

@@ -1,7 +1,14 @@
-tmp=$1
-key=$2
-run=`echo $tmp|sed s/^.*tmp//`
+#!/bin/bash
+#This takes
+# 1 the directory with the tmp files and
+# 2 the key file
 
-#Convert to a nice format
-./scoring/scorer2 $tmp $key  -v|sed -n -e 's/^score for //p'|
-sed -e 's/: /,/' -e 's/^.*_/"/' -e 's/.bnc./.bnc","/' > experiment/trainingSystem/trainingSystem_$run.csv
+tmps=$1
+key=$2
+#run=`echo $tmp|sed s/^.*tmp//`
+
+for tmp in $tmps/tmp*[0-9]; do
+	#Convert to a nice format
+	./scoring/scorer2 $tmp $key  -v|sed -n -e 's/^score for //p'|
+	sed -e 's/: /,/' -e 's/^.*_/"/' -e 's/.bnc./.bnc","/' > $tmp.csv
+done

### 2011-04-12 scripts/calls2csv.sh
format calls as csv

@@ -1,4 +1,10 @@
 #!/bin/bash
 #Run the calls through this
 #./scripts/make_calls.sh |
-sed -e 's+> experiment/trainingSystem/tmp+,+' -e 's/-\([nm]\)  /-\1 -b 0 /' -e 's/-\([re]\)/-\1 1/g'| sed -e 's/   / -r 0 -e 0/'| sed -e 's/  -e/ -r 0 -e/' -e 's/-r 1  /-r 1 -e 0/'
+
+#Header
+echo 'classifier,bootstrap,colocation,coocurrence,base_word,run_id'
+#Fill in empty flags
+sed -e 's+> experiment/trainingSystem/tmp+,+' -e 's/-\([nmt]\)  /-\1 -b 0 /' -e 's/-\([re]\)/-\1 1/g'| sed -e 's/   / -r 0 -e 0/'| sed -e 's/  -e/ -r 0 -e/' -e 's/-r 1  /-r 1 -e 0/'|
+#Format as csv
+sed -e 's+^./classify.py -++' -e 's/ -[blre] /,/g' -e 's/ //g'

### 2011-04-12 parser.py
parser working, but untested because the classifier is teh brokez

@@ -7,7 +7,13 @@ import nltk.parse.malt as malt
 m = malt.MaltParser()
 m.train_from_file('MaltParser/engmalt.linear.mco')
 
-STR = "There is beauty in the bellow of the blast."
-
-g = m.parse(STR)
-print g.tree()
+STR2 = "Do you know what it is ,  and where I can get one ?  We suspect you had seen the Terrex Autospade ,  which is made by Wolf Tools .  It is quite a hefty spade , with bicycle - type handlebars and a sprung lever at the rear , which you step on to activate it . Used correctly ,  you should n't have to bend your back during general digging ,  although it wo n't lift out the soil and put in a barrow if you need to move it !  If gardening tends to give you backache ,  remember to take plenty of rest periods during the day ,  and never try to lift more than you can easily cope with ."
+def parse(pos, context, d):
+	tree = m.parse(" ".join(context))
+	l = tree.nodelist
+	deps = l[pos+1]['deps']
+	if len(deps) > 0:
+		dep = l[deps[0]]['word']
+	else:
+		dep = ""
+	d['dependency'] = dep

### 2011-04-12 paper/paper.Rnw
talked about the parser

@@
 \documentclass{article}
+\usepackage{url}
 \title{Word Sense Disambiguation}
@@
 Ansu Abraham
-Craig Frey
+Craig Frey\\
 Dustin Tiedemann
@@
 Thomas Levine
-Whitney Foster
+Whitney Foster\\
 }
@@
 
+\section{Dependency Parsing}
+
+We included as one feature the MaltParser dependency parser, and used the
+engmalt.linear.mco linear support vector machine
+configuration\footnote{\url{http://maltparser.org/mco/english_parser/engmalt.html}}
+for parsing (the other option was a an SVM with a polynomial kernel, which the
+Malt website said would just as accurately, more slowly, but with less memory,
+so we decided to go with the faster option).
+
 \end{document}

### 2011-04-12 experiment/combine.R
adjust spelling in script

@@ -1,13 +1,14 @@
 #library(leaps)
-
+calls='./calls.csv'
 #This takes a comma-separated list of file names
 combine=function(...){
 	#This takes a list of one or two elements.
 	# $files vector of file names
 	# $scores data.frame of data (optional)
 	score.bind=function(s) {if (length(s$files)==0) s$scores else{
-		scores.new=read.csv(s$files[1],header=T)
-		scores.new$id=s$files[1]
+		scores.new=read.csv(s$files[1],header=F)
+		names(scores.new)=c('word','sense','correct')
+		scores.new$run_id=s$files[1]
 		bound=rbind(s$scores,scores.new)
 		Recall(list(files=s$files[-1],scores=bound))}}
 	score.bind(list(files=c(...)))
@@ -16,11 +17,13 @@ combine=function(...){
 
 
 import=function(){
+	library(foreign)
 	#Read the identifiers for the different systems
-	systems=read.csv('system_combinations.csv')[1:8,] #,colClasses=c('character','logical','logical','logical'))	
+	systems=read.csv(calls)
+	systems$run_id=paste('tmp',systems$run_id,'.csv',sep='')
 
-	ids=paste('random_data/randomscores',systems$id[-5],'.csv',sep='')
-	systems$id[-5]=ids
+#	ids=paste(filehead,systems$run_id,'.csv',sep='')
+	ids=list.files()[grep('tmp[0-9]*.csv',list.files())]
 
 	#Combine the systems
 	scores=combine(ids)
@@ -28,7 +31,7 @@ import=function(){
 
 	#Add the information about feature use and
 	#return the data.frame with scores and feature turnings-on
-	merge(scores,systems,by='id',all=F)
+	merge(scores,systems,by='run_id',all=F)
 }
 
 stepping=function(scores){

### 2011-04-12 scripts/calls2csv.sh

@@ -3,7 +3,7 @@
 #./scripts/make_calls.sh |
 
 #Header
-echo 'classifier,bootstrap,colocation,coocurrence,base_word,run_id'
+echo 'classifier,bootstrap,colocation,cooccurrence,base_word,run_id'
 #Fill in empty flags
 sed -e 's+> experiment/trainingSystem/tmp+,+' -e 's/-\([nmt]\)  /-\1 -b 0 /' -e 's/-\([re]\)/-\1 1/g'| sed -e 's/   / -r 0 -e 0/'| sed -e 's/  -e/ -r 0 -e/' -e 's/-r 1  /-r 1 -e 0/'|
 #Format as csv

### 2011-04-12 parser.py
better parsing

@@ -5,15 +5,28 @@ import nltk
 import nltk.parse.malt as malt
 
 m = malt.MaltParser()
+#malt.demo() # this is sometimes needed?  I don't get it.
 m.train_from_file('MaltParser/engmalt.linear.mco')
 
 STR2 = "Do you know what it is ,  and where I can get one ?  We suspect you had seen the Terrex Autospade ,  which is made by Wolf Tools .  It is quite a hefty spade , with bicycle - type handlebars and a sprung lever at the rear , which you step on to activate it . Used correctly ,  you should n't have to bend your back during general digging ,  although it wo n't lift out the soil and put in a barrow if you need to move it !  If gardening tends to give you backache ,  remember to take plenty of rest periods during the day ,  and never try to lift more than you can easily cope with ."
 def parse(pos, context, d):
 	tree = m.parse(" ".join(context))
 	l = tree.nodelist
-	deps = l[pos+1]['deps']
+	node = l[pos]
+	deps = node['deps']
 	if len(deps) > 0:
 		dep = l[deps[0]]['word']
 	else:
 		dep = ""
+	parent = l[node['head']]['word']
 	d['dependency'] = dep
+	d['has_dependencies'] = len(deps)>0
+	d['dependency_count'] = len(deps)
+	d['parent'] = parent
+	return d
+
+if __name__ == "__main__":
+	pos = 56
+	context = STR2.split()
+	d = parse(pos, context, {})
+	print d

### 2011-04-12 experiment/combine.R
first training results

@@ -37,7 +37,7 @@ import=function(){
 stepping=function(scores){
 	fit=glm(correct~word+colocation*cooccurrence,data=scores,family='binomial')
 	#stepwise
-	step(fit)
+#	step(fit)
 	#best-subsets requires the response at the end
 	#stuff=import()
 	#bestglm(cbind(stuff[-4],stuff[4]))
@@ -45,7 +45,7 @@ stepping=function(scores){
 
 main=function(){
 	foo=stepping(import())
-	print('Best two-feature system:')
-	print(foo$call)
-	print(paste('Percentage correct under the best two-feature system: ',round(100*sum(round(foo$fitted.values)==foo$y)/length(foo$y)),'%',sep=''))
+#	print('Best two-feature system:')
+#	print(foo$call)
+#	print(paste('Percentage correct under the best two-feature system: ',round(100*sum(round(foo$fitted.values)==foo$y)/length(foo$y)),'%',sep=''))
 }

### 2011-04-12 scripts/score_calls.sh
preliminary data

@@ -9,6 +9,7 @@ key=$2
 
 for tmp in $tmps/tmp*[0-9]; do
 	#Convert to a nice format
-	./scoring/scorer2 $tmp $key  -v|sed -n -e 's/^score for //p'|
-	sed -e 's/: /,/' -e 's/^.*_/"/' -e 's/.bnc./.bnc","/' > $tmp.csv
+	./scoring/scorer2 $tmp $key  | #-v|
+	sed -n -e 's/^score for //p'|
+	sed -e 's/: /,/' -e 's/^.*_/"/' -e 's/.bnc./.bnc","/' #> $tmp.csv
 done

### 2011-04-12 classify.py
minor fix

@@ -4,7 +4,7 @@ import nltk
 import colocation
 import cooccurrence
 import pairing
-import parser
+import parser as dep_parser
 from nltk.corpus import senseval
 from optparse import OptionParser
 
@@ -33,7 +33,7 @@ def assign_features(item, instance):
 	if USE_COOCCURRENCE:
 		d = cooccurrence.cooccurrence(item, pos, context, d)
 	if USE_PARSING:
-		d = parser.parse(pos, context, d)
+		d = dep_parser.parse(pos, context, d)
 	return d
 
 def build_train(item, instances):

### 2011-04-12 scripts/calls2csv.sh
glue

@@ -7,4 +7,4 @@ echo 'classifier,bootstrap,colocation,cooccurrence,base_word,run_id'
 #Fill in empty flags
 sed -e 's+> experiment/trainingSystem/tmp+,+' -e 's/-\([nmt]\)  /-\1 -b 0 /' -e 's/-\([re]\)/-\1 1/g'| sed -e 's/   / -r 0 -e 0/'| sed -e 's/  -e/ -r 0 -e/' -e 's/-r 1  /-r 1 -e 0/'|
 #Format as csv
-sed -e 's+^./classify.py -++' -e 's/ -[blre] /,/g' -e 's/ //g'
+sed -e 's+^./classify.py -++' -e 's/ -[blrep]* /,/g' -e 's/ //g'

### 2011-04-12 scripts/make_calls.sh

@@ -2,17 +2,18 @@
 #Run this like so
 #wsd.sh [test data key] 
 key=$1
+batch=batch2
 
 #Edit the nested for loops to select a series of feature combinations
-run=1
-for classifier in -n -t; do
-  for bootstrap in '' '-b 4' '-b 16' '-b 64'; do #Fix how a lack of bootstrapping for trees doesn't work well here
+run=200
+for classifier in -pn -t; do
+  for bootstrap in '' '-b 1' '-b 2' '-b 4'; do #Fix how a lack of bootstrapping for trees doesn't work well here
     for colocation in '-l 0' '-l 1' '-l 2' '-l 3'; do # -l NUM is the colocation distance, 0 is "don't use it"
-      for coocurrence in '' -r; do # -r enables cooccurrence usae
+      for coocurrence in '' -r; do # -r enables cooccurrence usage
         for base_word in '' -e; do # -e enables base word usage
 #Run the actual system
 #echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
-echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word > experiment/fullTraining/tmp$run"|
+echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word > experiment/$batch/tmp$run"|
 #Remove runs with bootstrapping and trees
 grep -v '\-t \-b' 
 run=$((run+1))

### 2011-04-12 scripts/score_calls.sh

@@ -9,7 +9,7 @@ key=$2
 
 for tmp in $tmps/tmp*[0-9]; do
 	#Convert to a nice format
-	./scoring/scorer2 $tmp $key  | #-v|
+	./scoring/scorer2 $tmp $key   -v|
 	sed -n -e 's/^score for //p'|
-	sed -e 's/: /,/' -e 's/^.*_/"/' -e 's/.bnc./.bnc","/' #> $tmp.csv
+	sed -e 's/: /,/' -e 's/^.*_/"/' -e 's/.bnc./.bnc","/' > $tmp.csv
 done

### 2011-04-12 scripts/calls2csv.sh
handle dependency parsing calls

@@ -7,4 +7,4 @@ echo 'classifier,bootstrap,colocation,cooccurrence,base_word,run_id'
 #Fill in empty flags
 sed -e 's+> experiment/trainingSystem/tmp+,+' -e 's/-\([nmt]\)  /-\1 -b 0 /' -e 's/-\([re]\)/-\1 1/g'| sed -e 's/   / -r 0 -e 0/'| sed -e 's/  -e/ -r 0 -e/' -e 's/-r 1  /-r 1 -e 0/'|
 #Format as csv
-sed -e 's+^./classify.py -++' -e 's/ -[blrep]* /,/g' -e 's/ //g'
+sed -e 's+^./classify.py -++' -e 's/ -[ablrep]* /,/g' -e 's/ //g'

### 2011-04-12 scripts/make_calls.sh

@@ -11,12 +11,14 @@ for classifier in -pn -t; do
     for colocation in '-l 0' '-l 1' '-l 2' '-l 3'; do # -l NUM is the colocation distance, 0 is "don't use it"
       for coocurrence in '' -r; do # -r enables cooccurrence usage
         for base_word in '' -e; do # -e enables base word usage
+          for dependency in '' -a; do
 #Run the actual system
 #echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
-echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word > experiment/$batch/tmp$run"|
+echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word $dependency > experiment/$batch/tmp$run"|
 #Remove runs with bootstrapping and trees
 grep -v '\-t \-b' 
 run=$((run+1))
+          done
         done
       done
     done

### 2011-04-12 parser.py
hack to make parser work

@@ -26,6 +26,9 @@ def parse(pos, context, d):
 	return d
 
 if __name__ == "__main__":
+	#Uncomment the line below after the first run
+	open('/tmp/malt_train.conll', 'w').close(); malt.demo()
+	
 	pos = 56
 	context = STR2.split()
 	d = parse(pos, context, {})

### 2011-04-12 classify.py
safer parser

@@ -1,5 +1,5 @@
 #!/usr/bin/env python
-import os, os.path
+import os, os.path, sys
 import nltk
 import colocation
 import cooccurrence
@@ -24,6 +24,7 @@ CLASSIFIER=nltk.NaiveBayesClassifier
 #CLASSIFIER=nltk.MaxentClassifier #much slower, prints lots of crap
 
 def assign_features(item, instance):
+	print >> sys.stderr, "classifying an instance"
 	context = instance['context']
 	pos = instance['position']
 	d={}
@@ -82,6 +83,7 @@ def bootstrap(train, test, classified):
 def batch_classify(items, tests):
 	senses = []
 	for item in items:
+		print >> sys.stderr, "classifying %s" % item
 		lexitem = ".".join(item.split(".")[0:2])
 		trains=\
 			[dict(context=instance.context,\
@@ -168,8 +170,11 @@ if __name__ == '__main__':
 	if CLASSIFIER == None:
 		raise Exception("No classifier specified, use -n -t or -m")
 
+	print >> sys.stderr, "Gathering Items"
 	items = senseval.fileids()
+	print >> sys.stderr, "Gathering Tests"
 	tests = pairing.parse_file("EnglishLS.test/EnglishLS.test")
+	print >> sys.stderr, "Classifying"
 	senses = batch_classify(items, tests)
 
 	f = open('answers.txt')

### 2011-04-12 parser.py

@@ -1,6 +1,7 @@
 #!/usr/bin/env python
 import os
 os.environ['MALTPARSERHOME']='MaltParser/malt-1.2'
+import sys
 import nltk
 import nltk.parse.malt as malt
 
@@ -12,17 +13,25 @@ STR2 = "Do you know what it is ,  and where I can get one ?  We suspect you had 
 def parse(pos, context, d):
 	tree = m.parse(" ".join(context))
 	l = tree.nodelist
-	node = l[pos]
-	deps = node['deps']
-	if len(deps) > 0:
-		dep = l[deps[0]]['word']
+	if pos in range(len(l)):
+		node = l[pos]
+		deps = node['deps']
+		if len(deps) > 0:
+			dep = l[deps[0]]['word']
+		else:
+			dep = ""
+		parent = l[node['head']]['word']
+		d['dependency'] = dep
+		d['has_dependencies'] = len(deps)>0
+		d['dependency_count'] = len(deps)
+		d['parent'] = parent
 	else:
-		dep = ""
-	parent = l[node['head']]['word']
-	d['dependency'] = dep
-	d['has_dependencies'] = len(deps)>0
-	d['dependency_count'] = len(deps)
-	d['parent'] = parent
+		print >> sys.stderr, 'Warning, index %d out of range in nodelist' % pos
+		print >> sys.stderr, l
+		d['dependency'] = ""
+		d['has_dependencies'] = False
+		d['dependency_count'] = False
+		d['parent'] = ""
 	return d
 
 if __name__ == "__main__":

### 2011-04-12 wsd.sh
script to do EVERYTHINg

@@ -1,0 +1,6 @@
+#!/bin/bash
+batch=batch$1
+bash scripts/make_calls.sh > experiment/$batch/calls.sh
+cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
+bash experiment/$batch/calls.sh
+bash scripts/score_calls.sh experiment/$batch EnglishLS.test/EnglishLS.test.key

### 2011-04-12 scripts/make_calls.sh
wsd.sh runs everything now

@@ -1,23 +1,26 @@
 #!/bin/bash
-#Run this like so
+#Run this in the root directory like so
 #wsd.sh [test data key] 
 key=$1
-batch=batch2
+batch=$2
 
 #Edit the nested for loops to select a series of feature combinations
 run=200
+echo '#!/bin/bash'
 for classifier in -pn -t; do
   for bootstrap in '' '-b 1' '-b 2' '-b 4'; do #Fix how a lack of bootstrapping for trees doesn't work well here
     for colocation in '-l 0' '-l 1' '-l 2' '-l 3'; do # -l NUM is the colocation distance, 0 is "don't use it"
       for coocurrence in '' -r; do # -r enables cooccurrence usage
         for base_word in '' -e; do # -e enables base word usage
           for dependency in '' -a; do
+
 #Run the actual system
 #echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
 echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word $dependency > experiment/$batch/tmp$run"|
 #Remove runs with bootstrapping and trees
 grep -v '\-t \-b' 
 run=$((run+1))
+
           done
         done
       done

### 2011-04-12 wsd.sh

@@ -1,6 +1,8 @@
 #!/bin/bash
 batch=batch$1
-bash scripts/make_calls.sh > experiment/$batch/calls.sh
+key=EnglishLS.test/EnglishLS.test.key
+mkdir experiment/$batch
+bash scripts/make_calls.sh $key $batch> experiment/$batch/calls.sh
 cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
 bash experiment/$batch/calls.sh
-bash scripts/score_calls.sh experiment/$batch EnglishLS.test/EnglishLS.test.key
+bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-12 scripts/calls2csv.sh
calls2csv takes arbitrary

@@ -5,6 +5,6 @@
 #Header
 echo 'classifier,bootstrap,colocation,cooccurrence,base_word,run_id'
 #Fill in empty flags
-sed -e 's+> experiment/trainingSystem/tmp+,+' -e 's/-\([nmt]\)  /-\1 -b 0 /' -e 's/-\([re]\)/-\1 1/g'| sed -e 's/   / -r 0 -e 0/'| sed -e 's/  -e/ -r 0 -e/' -e 's/-r 1  /-r 1 -e 0/'|
+sed -e 's+> experiment/[^/]*/tmp+,+' -e 's/-\([nmt]\)  /-\1 -b 0 /' -e 's/-\([re]\)/-\1 1/g'| sed -e 's/   / -r 0 -e 0/'| sed -e 's/  -e/ -r 0 -e/' -e 's/-r 1  /-r 1 -e 0/'|
 #Format as csv
 sed -e 's+^./classify.py -++' -e 's/ -[blre] /,/g' -e 's/ //g'

### 2011-04-12 scripts/make_calls.sh
run number

@@ -5,7 +5,7 @@ key=$1
 batch=$2
 
 #Edit the nested for loops to select a series of feature combinations
-run=200
+run=1000
 echo '#!/bin/bash'
 for classifier in -pn -t; do
   for bootstrap in '' '-b 1' '-b 2' '-b 4'; do #Fix how a lack of bootstrapping for trees doesn't work well here

### 2011-04-12 scripts/make_calls-smp2.sh
allow for smp

@@ -1,0 +1,29 @@
+#!/bin/bash
+#Run this in the root directory like so
+#wsd.sh [test data key] 
+key=$1
+batch=$2
+
+#Edit the nested for loops to select a series of feature combinations
+run=1000
+echo '#!/bin/bash'
+for classifier in -pn -t; do
+  for bootstrap in '' '-b 2' '-b 4' ; do #Fix how a lack of bootstrapping for trees doesn't work well here
+    for colocation in '-l 0' '-l 1' '-l 2' '-l 3'; do # -l NUM is the colocation distance, 0 is "don't use it"
+      for coocurrence in '' -r; do # -r enables cooccurrence usage
+        for base_word in '' -e; do # -e enables base word usage
+          for dependency in '' -a; do
+
+#Run the actual system
+#echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
+echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word $dependency > experiment/$batch/tmp$run"|
+#Remove runs with bootstrapping and trees
+grep -v '\-t \-b' 
+run=$((run+1))
+
+          done
+        done
+      done
+    done
+  done
+done

### 2011-04-12 scripts/make_calls-smp3.sh

@@ -1,0 +1,29 @@
+#!/bin/bash
+#Run this in the root directory like so
+#wsd.sh [test data key] 
+key=$1
+batch=$2
+
+#Edit the nested for loops to select a series of feature combinations
+run=1000
+echo '#!/bin/bash'
+for classifier in -pn -t; do
+  for bootstrap in '' '-b 1' '-b 4' ; do #Fix how a lack of bootstrapping for trees doesn't work well here
+    for colocation in '-l 0' '-l 1' '-l 2' '-l 3'; do # -l NUM is the colocation distance, 0 is "don't use it"
+      for coocurrence in '' -r; do # -r enables cooccurrence usage
+        for base_word in '' -e; do # -e enables base word usage
+          for dependency in '' -a; do
+
+#Run the actual system
+#echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
+echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word $dependency > experiment/$batch/tmp$run"|
+#Remove runs with bootstrapping and trees
+grep -v '\-t \-b' 
+run=$((run+1))
+
+          done
+        done
+      done
+    done
+  done
+done

### 2011-04-12 scripts/make_calls-smp4.sh

@@ -1,0 +1,29 @@
+#!/bin/bash
+#Run this in the root directory like so
+#wsd.sh [test data key] 
+key=$1
+batch=$2
+
+#Edit the nested for loops to select a series of feature combinations
+run=1000
+echo '#!/bin/bash'
+for classifier in -pn -t; do
+  for bootstrap in '' '-b 1' '-b 2' ; do #Fix how a lack of bootstrapping for trees doesn't work well here
+    for colocation in '-l 0' '-l 1' '-l 2' '-l 3'; do # -l NUM is the colocation distance, 0 is "don't use it"
+      for coocurrence in '' -r; do # -r enables cooccurrence usage
+        for base_word in '' -e; do # -e enables base word usage
+          for dependency in '' -a; do
+
+#Run the actual system
+#echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
+echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word $dependency > experiment/$batch/tmp$run"|
+#Remove runs with bootstrapping and trees
+grep -v '\-t \-b' 
+run=$((run+1))
+
+          done
+        done
+      done
+    done
+  done
+done

### 2011-04-12 wsd1.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+batch=batch$1
+key=EnglishLS.test/EnglishLS.test.key
+mkdir experiment/$batch
+bash scripts/make_calls-smp1.sh $key $batch> experiment/$batch/calls.sh
+cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
+bash experiment/$batch/calls.sh
+bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-12 wsd2.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+batch=batch$1
+key=EnglishLS.test/EnglishLS.test.key
+mkdir experiment/$batch
+bash scripts/make_calls2.sh $key $batch> experiment/$batch/calls.sh
+cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
+bash experiment/$batch/calls.sh
+bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-12 wsd3.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+batch=batch$1
+key=EnglishLS.test/EnglishLS.test.key
+mkdir experiment/$batch
+bash scripts/make_calls3.sh $key $batch> experiment/$batch/calls.sh
+cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
+bash experiment/$batch/calls.sh
+bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-12 wsd4.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+batch=batch$1
+key=EnglishLS.test/EnglishLS.test.key
+mkdir experiment/$batch
+bash scripts/make_calls4.sh $key $batch> experiment/$batch/calls.sh
+cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
+bash experiment/$batch/calls.sh
+bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-12 scripts/make_calls-smp2.sh
smp

@@ -5,7 +5,7 @@ key=$1
 batch=$2
 
 #Edit the nested for loops to select a series of feature combinations
-run=1000
+run=2000
 echo '#!/bin/bash'
 for classifier in -pn -t; do
   for bootstrap in '' '-b 2' '-b 4' ; do #Fix how a lack of bootstrapping for trees doesn't work well here

### 2011-04-12 scripts/make_calls-smp3.sh

@@ -5,7 +5,7 @@ key=$1
 batch=$2
 
 #Edit the nested for loops to select a series of feature combinations
-run=1000
+run=3000
 echo '#!/bin/bash'
 for classifier in -pn -t; do
   for bootstrap in '' '-b 1' '-b 4' ; do #Fix how a lack of bootstrapping for trees doesn't work well here

### 2011-04-12 scripts/make_calls-smp4.sh

@@ -5,7 +5,7 @@ key=$1
 batch=$2
 
 #Edit the nested for loops to select a series of feature combinations
-run=1000
+run=4000
 echo '#!/bin/bash'
 for classifier in -pn -t; do
   for bootstrap in '' '-b 1' '-b 2' ; do #Fix how a lack of bootstrapping for trees doesn't work well here

### 2011-04-12 wsd2.sh
make_calls-smp

@@ -2,7 +2,7 @@
 batch=batch$1
 key=EnglishLS.test/EnglishLS.test.key
 mkdir experiment/$batch
-bash scripts/make_calls2.sh $key $batch> experiment/$batch/calls.sh
+bash scripts/make_calls-smp2.sh $key $batch> experiment/$batch/calls.sh
 cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
 bash experiment/$batch/calls.sh
 bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-12 wsd3.sh

@@ -2,7 +2,7 @@
 batch=batch$1
 key=EnglishLS.test/EnglishLS.test.key
 mkdir experiment/$batch
-bash scripts/make_calls3.sh $key $batch> experiment/$batch/calls.sh
+bash scripts/make_calls-smp3.sh $key $batch> experiment/$batch/calls.sh
 cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
 bash experiment/$batch/calls.sh
 bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-12 wsd4.sh

@@ -2,7 +2,7 @@
 batch=batch$1
 key=EnglishLS.test/EnglishLS.test.key
 mkdir experiment/$batch
-bash scripts/make_calls4.sh $key $batch> experiment/$batch/calls.sh
+bash scripts/make_calls-smp4.sh $key $batch> experiment/$batch/calls.sh
 cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
 bash experiment/$batch/calls.sh
 bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-12 experiment/batch3/calls.sh
calls for the experiment runs

@@ -1,0 +1,484 @@
+#!/bin/bash
+./classify.py -pn -b 1 -l 0    > experiment/batch3/tmp1000
+./classify.py -pn -b 1 -l 0   -a > experiment/batch3/tmp1001
+./classify.py -pn -b 1 -l 0  -e  > experiment/batch3/tmp1002
+./classify.py -pn -b 1 -l 0  -e -a > experiment/batch3/tmp1003
+./classify.py -pn -b 1 -l 0 -r   > experiment/batch3/tmp1004
+./classify.py -pn -b 1 -l 0 -r  -a > experiment/batch3/tmp1005
+./classify.py -pn -b 1 -l 0 -r -e  > experiment/batch3/tmp1006
+./classify.py -pn -b 1 -l 0 -r -e -a > experiment/batch3/tmp1007
+./classify.py -pn -b 1 -l 1    > experiment/batch3/tmp1008
+./classify.py -pn -b 1 -l 1   -a > experiment/batch3/tmp1009
+./classify.py -pn -b 1 -l 1  -e  > experiment/batch3/tmp1010
+./classify.py -pn -b 1 -l 1  -e -a > experiment/batch3/tmp1011
+./classify.py -pn -b 1 -l 1 -r   > experiment/batch3/tmp1012
+./classify.py -pn -b 1 -l 1 -r  -a > experiment/batch3/tmp1013
+./classify.py -pn -b 1 -l 1 -r -e  > experiment/batch3/tmp1014
+./classify.py -pn -b 1 -l 1 -r -e -a > experiment/batch3/tmp1015
+./classify.py -pn -b 1 -l 2    > experiment/batch3/tmp1016
+./classify.py -pn -b 1 -l 2   -a > experiment/batch3/tmp1017
+./classify.py -pn -b 1 -l 2  -e  > experiment/batch3/tmp1018
+./classify.py -pn -b 1 -l 2  -e -a > experiment/batch3/tmp1019
+./classify.py -pn -b 1 -l 2 -r   > experiment/batch3/tmp1020
+./classify.py -pn -b 1 -l 2 -r  -a > experiment/batch3/tmp1021
+./classify.py -pn -b 1 -l 2 -r -e  > experiment/batch3/tmp1022
+./classify.py -pn -b 1 -l 2 -r -e -a > experiment/batch3/tmp1023
+./classify.py -pn -b 1 -l 3    > experiment/batch3/tmp1024
[…]

### 2011-04-12 wsd1.sh
fix saving of calls

@@ -2,7 +2,7 @@
 batch=batch$1
 key=EnglishLS.test/EnglishLS.test.key
 mkdir experiment/$batch
-bash scripts/make_calls-smp1.sh $key $batch> experiment/$batch/calls.sh
-cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
-bash experiment/$batch/calls.sh
-bash scripts/score_calls.sh experiment/$batch $key
+bash scripts/make_calls-smp1.sh $key $batch> experiment/$batch/calls1.sh
+cat experiment/$batch/calls1.sh|bash scripts/calls2csv.sh > experiment/$batch/calls1.csv
+bash experiment/$batch/calls1.sh
+bash scripts/score_calls1.sh experiment/$batch $key

### 2011-04-12 wsd2.sh

@@ -2,7 +2,7 @@
 batch=batch$1
 key=EnglishLS.test/EnglishLS.test.key
 mkdir experiment/$batch
-bash scripts/make_calls-smp2.sh $key $batch> experiment/$batch/calls.sh
-cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
-bash experiment/$batch/calls.sh
-bash scripts/score_calls.sh experiment/$batch $key
+bash scripts/make_calls-smp2.sh $key $batch> experiment/$batch/calls2.sh
+cat experiment/$batch/calls2.sh|bash scripts/calls2csv.sh > experiment/$batch/calls2.csv
+bash experiment/$batch/calls2.sh
+bash scripts/score_calls2.sh experiment/$batch $key

### 2011-04-13 scripts/make_calls-all.sh
possibiblity to run all feature combinations

@@ -1,0 +1,29 @@
+#!/bin/bash
+#Run this in the root directory like so
+#wsd.sh [test data key] 
+key=$1
+batch=$2
+
+#Edit the nested for loops to select a series of feature combinations
+run=9000
+echo '#!/bin/bash'
+for classifier in -pn -t; do
+  for bootstrap in '' '-b 1' '-b 2' '-b 4'; do #Fix how a lack of bootstrapping for trees doesn't work well here
+    for colocation in '-l 0' '-l 1' '-l 2' '-l 4' '-l 8'; do # -l NUM is the colocation distance, 0 is "don't use it"
+      for coocurrence in '' -r; do # -r enables cooccurrence usage
+        for base_word in '' -e; do # -e enables base word usage
+          for dependency in '' -a; do
+
+#Run the actual system
+#echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
+echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word $dependency > experiment/$batch/tmp$run"|
+#Remove runs with bootstrapping and trees
+grep -v '\-t \-b' 
+run=$((run+1))
+
+          done
+        done
+      done
+    done
+  done
+done

### 2011-04-13 wsd-all.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+batch=batch$1
+key=EnglishLS.test/EnglishLS.test.key
+mkdir experiment/$batch
+bash scripts/make_calls-all.sh $key $batch> experiment/$batch/calls.sh
+cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
+bash experiment/$batch/calls.sh
+bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-13 experiment/analyze.R
tabulate results

@@ -105,6 +105,12 @@ main=function(){
 	ag=import.aggregated()
 	ag$f=2*ag$precision*ag$recall/(ag$precision+ag$recall)
 
+	measures=c('precision','recall','f')
+	ag.fine=subset(ag,grain=='fine')
+	ag.mixed=subset(ag,grain=='mixed')
+	ag.coarse=subset(ag,grain=='coarse')
+	write.csv(cbind(ag.fine,ag.mixed[measures],ag.coarse[measures])[order(ag.mixed$f),],'finemixedcoarse.csv',row.names=F)
+
 	write.csv(ag[rowSums(ag[c(
 		"bootstrap","colocation","cooccurrence","base_word","dependency_parsing"
 	)])<=1,],row.names=F,file='onefeature.csv')

### 2011-04-13 classify.py
slight safety mod

@@ -34,7 +34,10 @@ def assign_features(item, instance):
 	if USE_COOCCURRENCE:
 		d = cooccurrence.cooccurrence(item, pos, context, d)
 	if USE_PARSING:
-		d = dep_parser.parse(pos, context, d)
+		try:
+			d = dep_parser.parse(pos, context, d)
+		except:
+			pass
 	return d
 
 def build_train(item, instances):

### 2011-04-13 paper/paper.Rnw

@@
 
+\section{Looking through Different Corpora}
+
+In order to get more data to use with the bootstrapping algorithm, we attempted to search through the Brown corpus and return all of the words that were being disambiguated in the Senseval 3 task.
+To do this we needed to find all of the instances of the words that we needed to disambiguate and return a context (list of words) and the position of the word in that list.
+We also made sure that we the context that we returned both started at the beginning of the sentence and ended at the end of a sentence and had a minimum of 25 words returned on either side of the word.
+This data would then be converted into the form of the data that we received from the Senseval document and ran through the bootstrapping algorithm to have more data to train with.
+However when we actually tested this feature alone we found it to be very uninformative.
+First, there were very few instances of the words that we were looking for (ex: activate only appeared 3 times), which made searching through the entire corpus to find these words more time consuming than it was helpful.
+Therefore, we decided not to use it for the actual test because it was not informative enough by itself.
+
 \end{document}

### 2011-04-13 paper/methods.tex
analysis

\section{Methods}
\newcommand\few{few}
We ran the system with several hundred different combinations of features.
We used two approaches to identifying the best feature combinations, and then
we did more detailed analysis on the top \few systems.

\subsection{Identification of the best feature combinations}
We identified optimal feature combinations through backward stepwise simple linear regression
and through the creation and visual analysis of charts. The former has the
advantage of discovering relationships and testing them more quantitatively
but has the disadvantage of making assumptions about normality, linearity and equal variance.
The latter has the advantage of elucidating more complex and higher-order relationships

\subsubsection{Stepwise regression}
We ran backward stepwise regression with the F-measure from the coarse-grained scores
regressed on predictors representing the feature combination.
The saturated model contained the following predictors and all interactions
\begin{itemize}
\item Classifier (naive Bayes or decision list)
\item Colocation window length (0--8)
\item Cooccurrence handling (on or off)
\item Base word handling (on or off)
\item Bootstrap iterations (0--4)
\item Dependency parsing (on or off)
\end{itemize}
The predictor combination yeilding the lowest value of the Akaike information criterion
included the following parameters.
\begin{itemize}
\item Intercept
\item Classifier
\item Colocation window size
\item Coocurrence
\item Base word handling
\item Classifier$\times$colocation window size interaction
\item Classifier$\times$cooccurrence interaction
\end{itemize}
This does not include bootstrap iterations, indicating that changes
in bootstrap iterations does not substantially change the F-measure.

%Discuss the coefficients in the regression table
                         Estimate Std. Error t value Pr(>|t|)    
(Intercept)               0.572768   0.006419  89.229  < 2e-16 ***
classifiert               0.050648   0.015703   3.225  0.00162 ** 
colocation                0.003961   0.001146   3.455  0.00076 ***
cooccurrence              0.025666   0.005986   4.288 3.65e-05 ***
base_word                 0.011615   0.005599   2.074  0.04017 *  
classifiert:colocation   -0.013670   0.005475  -2.497  0.01388 *  
classifiert:cooccurrence -0.025294   0.016931  -1.494  0.13780

%lm(formula = f(foo) ~ classifier + colocation + cooccurrence + 
%    base_word + classifier:colocation + classifier:cooccurrence, 
%    data = foo)

\subsubsection{Graphical methods}

\subsection{Characterization of the top feature combinations}

### 2011-04-13 experiment/analyze.R

@@ -17,14 +17,13 @@ combine=function(...){
 
 
 
-import.instances=function(){
-	library(foreign)
+import.instances=function(run_ids){
 	#Read the identifiers for the different systems
 	systems=read.csv(calls)
 	systems$run_id=paste('tmp',systems$run_id,'.csv',sep='')
 
 #	ids=paste(filehead,systems$run_id,'.csv',sep='')
-	ids=list.files()[grep('tmp[0-9]*.csv',list.files())]
+	ids=paste(run_ids,'.csv',sep='')
 
 	#Combine the systems
 	scores=combine(ids)
@@ -99,17 +98,34 @@ plot.lowerorder=function(ag){
 	p <- ggplot(ag,aes(bootstrap,resid.recall,group=base_word))
 	print(p+geom_point(aes(colour = factor(base_word))))
 }
+
+plot.instances=function(inst){
+        p <- ggplot(inst,aes(colocation,correct,group=word))
+	print(p+geom_point(aes(colour=word)))
+#        print(p+geom_point(aes(colour = classifier))+
+#                geom_line(data=subset(makelines,cooccurrence==0),aes(linetype='Cooccurrence Off'))+
+#                geom_line(data=subset(makelines,cooccurrence==1),aes(linetype='Ooocurrence On'))
+#        )
+
+
+}
+
+f=function(frame){
+	2*frame$precision*frame$recall/(frame$precision+frame$recall)
+}
+
 main=function(){
 	library(ggplot2)
 	pdf('plots.pdf')
 	ag=import.aggregated()
-	ag$f=2*ag$precision*ag$recall/(ag$precision+ag$recall)
+	ag$f=f(ag)
 
 	measures=c('precision','recall','f')
 	ag.fine=subset(ag,grain=='fine')
 	ag.mixed=subset(ag,grain=='mixed')
 	ag.coarse=subset(ag,grain=='coarse')
-	write.csv(cbind(ag.fine,ag.mixed[measures],ag.coarse[measures])[order(ag.mixed$f),],'finemixedcoarse.csv',row.names=F)
+	write.csv(cbind(ag.fine,ag.mixed[measures],ag.coarse[measures])[order(ag.mixed$f,decreasing=T),],'finemixedcoarse.csv',row.names=F)
+
 
 	write.csv(ag[rowSums(ag[c(
 		"bootstrap","colocation","cooccurrence","base_word","dependency_parsing"
@@ -135,4 +151,22 @@ main=function(){
 
 	
 	dev.off()
[…]

### 2011-04-13 experiment/analyze.R
blah

@@ -83,8 +83,8 @@ plot.aggregated=function(ag){
 		geom_line(data=subset(makelines,cooccurrence==0),aes(linetype='Cooccurrence Off'))+
 		geom_line(data=subset(makelines,cooccurrence==1),aes(linetype='Ooocurrence On'))
 	)
-
 }
+
 plot.lowerorder=function(ag){
 	#Let's look at the residuals of those lines
 	ag$resid.f=lm(f~factor(colocation)*classifier*cooccurrence,data=ag)$residuals
@@ -99,6 +99,8 @@ plot.lowerorder=function(ag){
 	p <- ggplot(ag,aes(bootstrap,resid.recall,group=base_word))
 	print(p+geom_point(aes(colour = factor(base_word))))
 }
+
+
 main=function(){
 	library(ggplot2)
 	pdf('plots.pdf')
@@ -129,4 +131,11 @@ main=function(){
 
 	
 	dev.off()
+}
+
+plot.step=function(){
+	ag=subset(import.aggregated(),grain='mixed')
+	ag$f=f(ag)
+	b=ggplot(ag,aes(colocation,f,group=c(cooccurrence,classifier)))
+	b+geom_point(aes(color=cooccurrence))
 }

### 2011-04-13 paper/methods.tex
stepwise graphs

@@
 but has the disadvantage of making assumptions about normality, linearity and equal variance.
-The latter has the advantage of elucidating more complex and higher-order relationships
+The latter has the advantage of elucidating more complex and higher-order relationships.
 
@@
 \subsubsection{Graphical methods}
+We began by plotting the predictors that seemed most influential in the
+stepwise regression.
+
+%lassifiert, colocation, cooccurrence  
+%Interpret this graph
 

### 2011-04-13 experiment/analyze.R

@@ -139,9 +139,21 @@ main=function(){
 	dev.off()
 }
 
-plot.step=function(){
+plot.step.import=function(){
 	ag=subset(import.aggregated(),grain='mixed')
 	ag$f=f(ag)
+	ag$cooccurrence=factor(ag$cooccurrence)
+	ag
+}
+
+plot.step1=function(){
+	plot.step.import()
 	b=ggplot(ag,aes(colocation,f,group=c(cooccurrence,classifier)))
-	b+geom_point(aes(color=cooccurrence))
+	b+geom_point(aes(color=cooccurrence,shape=classifier))
+}
+plot.step2=function(){
+	ag=subset(plot.step.import(),cooccurrence<=4&cooccurrence>=2)
+	resid_cooccurrence=lm(f~cooccurrence,data=ag)$residuals
+	b=ggplot(ag,aes(classifier,resid,group=base_word))
+	b+geom_point(aes(shape=classifier))
 }

### 2011-04-13 experiment/analyze.R
three-step graphical analysis

@@ -143,17 +143,29 @@ plot.step.import=function(){
 	ag=subset(import.aggregated(),grain='mixed')
 	ag$f=f(ag)
 	ag$cooccurrence=factor(ag$cooccurrence)
+	ag$base_word=factor(ag$base_word)
 	ag
 }
 
+#Most significant terms from the stepwise regression
 plot.step1=function(){
 	plot.step.import()
 	b=ggplot(ag,aes(colocation,f,group=c(cooccurrence,classifier)))
 	b+geom_point(aes(color=cooccurrence,shape=classifier))
 }
+
+#Select optimal colocation window and keep looking
 plot.step2=function(){
-	ag=subset(plot.step.import(),cooccurrence<=4&cooccurrence>=2)
-	resid_cooccurrence=lm(f~cooccurrence,data=ag)$residuals
-	b=ggplot(ag,aes(classifier,resid,group=base_word))
-	b+geom_point(aes(shape=classifier))
+	ag=subset(plot.step.import(),colocation>=2&colocation<=4)
+#	ag$resid_cooccurrence=lm(f~cooccurrence,data=ag)$residuals
+#	b=ggplot(ag,aes(cooccurrence,resid_cooccurrence,group=c(base_word,classifier)))
+	b=ggplot(ag,aes(cooccurrence,f,group=c(base_word,classifier)))
+	b+geom_point(aes(colour=base_word,shape=classifier))
+}
+
+#Little effect of bootstrapping or base-word handling. Bootstrapping seems to plateau at 2 iterations.
+plot.step3=function(){
+	ag=subset(plot.step.import(),colocation>=2&colocation<=4&cooccurrence==1&classifier=='pn')
+	b=ggplot(ag,aes(bootstrap,f,group=c(base_word)))
+	b+geom_point(aes(colour=base_word))
 }

### 2011-04-13 experiment/analyze.R
get by-word information

@@ -43,15 +43,6 @@ import.aggregated=function(){
 	merge(scores,systems,by='run_id',all=F)
 }
 
-stepping=function(scores){
-	fit=glm(correct~word+colocation*cooccurrence,data=scores,family='binomial')
-	#stepwise
-#	step(fit)
-	#best-subsets requires the response at the end
-	#stuff=import()
-	#bestglm(cbind(stuff[-4],stuff[4]))
-}
-
 mymean=function(x){
 	if (is.numeric(x)){
 		mean(x)
@@ -100,7 +91,7 @@ plot.lowerorder=function(ag){
 }
 
 
-main=function(){
+blah=function(){
 	library(ggplot2)
 	pdf('plots.pdf')
 	ag=import.aggregated()
@@ -151,24 +142,57 @@ plot.step.import=function(){
 }
 
 #Most significant terms from the stepwise regressio
+plot.step0=function(){
+	ag=plot.step.import()
+	ggplot(ag,aes(dependency_parsing,f,group=c(cooccurrence)))+
+	geom_point(aes(color=cooccurrence))+
+	opts(title = expression("Performance of all of our systems as a function of dependency parsing"))
+}
+
 plot.step1=function(){
 	ag=plot.step.import()
-	b=ggplot(ag,aes(colocation,f,group=c(cooccurrence,classifier)))
-	b+geom_point(aes(color=cooccurrence,shape=classifier))
+	ggplot(ag,aes(colocation,f,group=c(cooccurrence)))+
+	geom_point(aes(color=cooccurrence))+
+	opts(title = expression("Performance of all of our systems"))
 }
 
 #Select optimal colocation window and keep looking
 plot.step2=function(){
 	ag=subset(plot.step.import(),colocation>=2&colocation<=4)
-#	ag$resid_cooccurrence=lm(f~cooccurrence,data=ag)$residuals
-#	b=ggplot(ag,aes(cooccurrence,resid_cooccurrence,group=c(base_word,classifier)))
-	b=ggplot(ag,aes(cooccurrence,f,group=c(base_word,classifier)))
-	b+geom_point(aes(colour=base_word,shape=classifier))
+	ggplot(ag,aes(classifier,f,group=c(base_word)))+
+	geom_point(aes(colour=base_word))+
+	opts(title=expression('Performance of the systems with colocation windows between 2 and 4'))
 }
 
 #Little effect of bootstrapping or base-word handling. Bootstrapping seems to plateau at 2 iterations.
[…]

### 2011-04-13 scripts/scores_by_word.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+system=$1
+for word in nltk_data/corpora/senseval/*.pos
+do
+word=`echo $word|sed -e s+nltk_data/corpora/senseval/++ -e s+\.pos$++`
+grep "^$word" $system|grep -v U$ > tmp-$word
+for grain in coarse mixed; do
+	./scoring/scorer2 tmp-$word EnglishLS.test/EnglishLS.test.key EnglishLS.test/EnglishLS.sensemap -g "$grain"|
+        sed -e 's+^.*tmp-+"+' -e 's+ using key.*$++' -e 's+(.*)++' -e 's+^.*:++' -e 's/[ %]//g' -e '/^$/d ' |tr '\n' ','|sed -e 's/,$//' -e "s/,/,$grain,/"
+        echo 
+done
+grain=fine
+        ./scoring/scorer2 tmp-$word EnglishLS.test/EnglishLS.test.key |
+        sed -e 's+^.*tmp-+"+' -e 's+ using key.*$++' -e 's+(.*)++' -e 's+^.*:++' -e 's/[ %]//g' -e '/^$/d ' |tr '\n' ','|sed -e 's/,$//' -e "s/,/,$grain,/"
+        echo 
+done

### 2011-04-13 scripts/scores_by_word.sh
get corpus size

@@ -1,5 +1,9 @@
 #!/bin/bash
 system=$1
+
+wc -l nltk_data/corpora/senseval/*.pos|sed 's+ nltk_data/corpora/senseval/+,+'|grep -v total$ > tmp-trainingsize
+
+echo run_id,grain,precision,recall,corpus_size
 for word in nltk_data/corpora/senseval/*.pos
 do
 word=`echo $word|sed -e s+nltk_data/corpora/senseval/++ -e s+\.pos$++`
@@ -7,10 +11,10 @@ grep "^$word" $system|grep -v U$ > tmp-$word
 for grain in coarse mixed; do
 	./scoring/scorer2 tmp-$word EnglishLS.test/EnglishLS.test.key EnglishLS.test/EnglishLS.sensemap -g "$grain"|
         sed -e 's+^.*tmp-+"+' -e 's+ using key.*$++' -e 's+(.*)++' -e 's+^.*:++' -e 's/[ %]//g' -e '/^$/d ' |tr '\n' ','|sed -e 's/,$//' -e "s/,/,$grain,/"
-        echo 
+        echo ',' `grep $word tmp-trainingsize | cut -d , -f 1`
 done
 grain=fine
         ./scoring/scorer2 tmp-$word EnglishLS.test/EnglishLS.test.key |
         sed -e 's+^.*tmp-+"+' -e 's+ using key.*$++' -e 's+(.*)++' -e 's+^.*:++' -e 's/[ %]//g' -e '/^$/d ' |tr '\n' ','|sed -e 's/,$//' -e "s/,/,$grain,/"
-        echo 
+        echo ',' `grep $word tmp-trainingsize | cut -d , -f 1`
 done

### 2011-04-13 experiment/analyze.R
baseline

@@ -133,12 +133,12 @@ blah=function(){
 
 f=function(ag) 2*ag$precision*ag$recall/(ag$precision+ag$recall)
 
-plot.step.import=function(){
+plot.step.import=function(sub='mixed'){
 	ag=subset(import.aggregated(),grain='mixed')
 	ag$f=f(ag)
 	ag$cooccurrence=factor(ag$cooccurrence)
 	ag$base_word=factor(ag$base_word)
-	ag
+	if (!is.na(sub)) subset(ag,grain==sub) else ag
 }
 
 #Most significant terms from the stepwise regressio
@@ -185,6 +185,7 @@ rank.scores=function(){
 		fine=subset(foo,grain=='fine')$run_id,
 		mixed=subset(foo,grain=='mixed')$run_id
 	)
+#head(foo)[c('run_id','f','precision','recall','classifier','attempted','bootstrap','colocation','cooccurrence','base_word','dependency_parsing')]
 }
 
 stepping=function(){
@@ -195,4 +196,13 @@ stepping=function(){
 	print(plot.step3())
 	dev.off()
 	step(lm(f~classifier*bootstrap*colocation*cooccurrence*base_word*dependency_parsing,data=plot.step.import()))
+}
+
+
+plot.baseline=function(){
+	ag=subset(plot.step.import(sub=NA),
+		bootstrap==0&colocation==0&cooccurrence==0&base_word==0&dependency_parsing==0)
+	ggplot(ag,aes(grain,f,group=classifier))+
+	geom_line(aes(color=classifier))+
+	opts(title = expression("Baseline performance"))
 }

### 2011-04-14 experiment/analyze.R
plots

@@ -134,43 +134,56 @@ blah=function(){
 f=function(ag) 2*ag$precision*ag$recall/(ag$precision+ag$recall)
 
 plot.step.import=function(sub='mixed'){
-	ag=subset(import.aggregated(),grain='mixed')
+	ag=import.aggregated()
+	offon=c('Off','On')
+	if (!is.na(sub)) ag=subset(ag,grain==sub)
 	ag$f=f(ag)
 	ag$cooccurrence=factor(ag$cooccurrence)
 	ag$base_word=factor(ag$base_word)
-	if (!is.na(sub)) subset(ag,grain==sub) else ag
+	ag$dependency_parsing=factor(ag$dependency_parsing)
+	levels(ag$classifier)=c('Naive Bayes','Decision tree')
+	levels(ag$base_word)<-offon
+	levels(ag$cooccurrence)<-offon
+	levels(ag$dependency_parsing)<-offon
+	ag
 }
 
 #Most significant terms from the stepwise regressio
 plot.step0=function(){
 	ag=plot.step.import()
 	ggplot(ag,aes(dependency_parsing,f,group=c(cooccurrence)))+
-	geom_point(aes(color=cooccurrence))+
-	opts(title = expression("Performance of all of our systems as a function of dependency parsing"))
+	geom_point(aes(color=cooccurrence),position=position_jitter(w=0.1, h=0))+
+	opts(title = expression("Dependency parsing is only helpful when colocation is off"))
+#	scale_x_continuous('Dependency parsing on (1) or off (0)') + scale_y_continuous('Mixed-grained F-measure')
 }
 
 plot.step1=function(){
 	ag=plot.step.import()
 	ggplot(ag,aes(colocation,f,group=c(cooccurrence)))+
-	geom_point(aes(color=cooccurrence))+
-	opts(title = expression("Performance of all of our systems"))
+	geom_point(aes(color=cooccurrence),position=position_jitter(w=0.1, h=0))+
+	opts(title = expression("The optimal colocation window is between 2 and 4 words"))
+#	opts(title = expression("Performance of all of our systems"))+
+#	scale_x_continuous('Colocation window size') + scale_y_continuous('Mixed-grained F-measure')
 }
 
 #Select optimal colocation window and keep looking
 plot.step2=function(){
 	ag=subset(plot.step.import(),colocation>=2&colocation<=4)
 	ggplot(ag,aes(classifier,f,group=c(base_word)))+
-	geom_point(aes(colour=base_word))+
[…]

### 2011-04-14 paper/paper.tex
parttwo paper format
paper from piratepad

@@
 \documentclass{article}
+\usepackage{url}
+\title{Word Sense Disambiguation\\
+\small{Leveraging the NLTK Toolkit and External Tools}}
+\author{
+Alec Story
+Ansu Abraham
+Craig Frey\\
+Dustin Tiedemann
+Michael Zhu
+Thomas Levine
+Whitney Foster\\
+}
+
 \begin{document}
+\maketitle
 
-\section{Selecting optimal feature combination}
+\section{Overview}
+We  chose to implement our system in Python, and chose to use the machine learning algorithms in the NLTK toolkit which is also Python-based.
+
+We wrote our main control program, classify.py, so that it can choose either [we're just doing nb and decision trees now right?] classifier and any combination of  features.
+On top of this we wrote bash scripts that automated looping through every combination of classifiers and features, along with porting the results directly into the scorer.
+Classify.py includes a help switch -h, that explains the switches that control the different classifiers and features along with any additional parameters that a certain feature might support (for example, collocation has a window size parameter which defaults to 0)
+Performance was excellent for most of the features, allowing us to typically run all of the words in the test set through every combination a classifier and feature set in under an hour.
+(The number of runs can get quite high when you factor in several parameters per feature, not just on/off)
+
+A baseline was run by choosing the most frequent sense for each word.
+
+\subsection{Data details}
+The  NLTK has a corpus reader  that imports Senseval-2 files.
+The Senseval-3  file format is slightly  different which necessitated a few changes.
+We separated the training  and test files by word into .pos files to match  what the existing  parser looked for.
+In the interest of time we modified  the training and  test files to contain a single tagged word per chunk  (but still  allowing for multiple senses) again to match the Senseval-2  format.
+
+\subsection{Selecting optimal feature combination}
 \newcommand\ward{forward} %or maybe backwards
@@
 with a small number of features but with high performance
+
+\section{System}
+
+We made heavy use of python's NLTK package\footnote{\url{http://www.nltk.org/}}, using its classifiers as our machine learning engines, and several of its other packages for analysis.
+
+\subsection{Classifiers}
+
+The NLTK was used to implement two machine learning algorithms, naive Bayes and decision trees.
+
+\subsubsection{Naive Bayes}
+
+The NLTK implements a naïve bayes classifier which chooses the best sense given a dictionary of features and assigns confidence probabilities to the chosen sense.
+Naive bayes does assume an independence of features.
+The probability of each feature contributes to the overall choice.
+
+\subsubsection{Decision Tree}
+
+The NLTK also implements a decision list classifier in which a sequence of tests is applied to each target-word feature vector.
+Each test indicates a particular sense of the word: if the test succeeds, the sense of the test is returned otherwise the next test in the sequence is performed.
+
+Naive Bayes supported probability estimation, while the decision tree did not.
+
+\subsection{Confidence Cutoffs}
+
+NLTK provides probability measures for each of its guesses when using the
+maximum entropy and the naive Bayes learning methods.  We harnessed these to
+determine the cutoff for making a guess, or resorting to a ``U'' if we were unconfident in the tagging.
+Occasional unknowns also occur because such unknowns are present in the training data, and we made no effort to remove them, so the learning algorithm views them as any other label.
+
+% Should we mention which cutoff we used?  Which did we use?
+
+\subsection{Bootstrapping}
+
+We used the same probability measure from the confidence cutoffs to fuel a
+bootstrapping method.  Instead of directly taking the output of the classifier,
+we instead looked at its performance on the test data, and wherever it was very
+confident, we copied that test instance to the training data, and repeated this
+cycle for a fixed number of cycles.  Once we had enriched the training data, we
+ran the classifier a final time to perform classification.
+
+Fortunately, the classifiers were very fast, and almost all of the time the
+system spends is in reading input and building feature sets, which don't need to
+be repeated, so bootstrapping is very cheap to include.
+
+% Should we mention which probability measure we used?  Which did we use?  How
+% many iterations?
+
+\subsection{Base Word}
+
+Because the target words were grouped by part of speech, we included the word as it appears literally in context as a feature.
+For example, ``activate'' versus ``activating,'' which both appear under activate.v.
+
+\subsection{Dependency Parsing}
+
+We included as one feature the MaltParser dependency parser, and used the
+engmalt.linear.mco linear support vector machine
+configuration\footnote{\url{http://maltparser.org/mco/english_parser/engmalt.html}}
+for parsing (the other option was an SVM with a polynomial kernel, which the
+Malt website said would run just as accurately, more slowly, but with less memory,
+so we decided to go with the faster option).
+
+From the parser we rendered several features:
+\begin{description}
+
+\item[The Dependency:] whatever the first of the list of dependencies given for the target word is.
+It is difficult to represent lists in the key and value feature format, so we did not attempt to.
+Instead, we use the rest of the features as mitigating factors.
+The empty string if there is no dependency.
+
+\item[Presence of Absence of Dependency]
+
+\item[Number of Dependencies]
+
+\item[The Parent:] the word with the target word as (one of) its dependencies.
+
+\end{description}
+
+Dependency parsing is fairly slow, requiring about a second per instance to run on a computer running an Atom D525 processor (which is fairly underpowered, but modern).
+To help alleviate this problem, we wrote a system that saves parses for each context, and only calls the parser if it observes a new parse, so we could reuse parsing information across runs of our program.
+Because this file is several hundred megabytes in size, it is not included in our submitted code.
+
+\subsection{Collocation}
+
+Encodes the part-of-speech tag of words to the left and right of the target word.
+The number of words extracted is determined by a variable window size (context) which the function takes in as an input.
+Half the window size is taken from left the word and half from the right of the word; thus window size is the total number of words examined.
+For an odd window size, it rounds up half the window size up for the part left of the word and rounds down for the part right of the word.
+
+We rendered a feature for each position covered, and set its value to be the word at that position.
+
+We also used nltk's part of speech tagger to tag the context, and included those as we did the literal words in the feature set.
+This was trained on nltk's \verb+maximum entropy treebank pos tagger+ data, which is included with the nltk package.
+
+\subsection{Cooccurrence}
+Looks through the training data and compiles a list of most common words for each item in the data.
+When the test data is run, the feature looks for the created vector and uses that instead of trying to make a new one.
+Next the extractor takes a window of words around the head word and generates the 0, 1 tuple of features for inclusion to the dictionary.
+This word list is used as the keys of the feature vector when using the test data as a list of words that may cooccur with each item in the data.
+The value associated with each key in the feature vector starts out as 0 (for occurring 0 times in the window near a test word) If a key in the feature vector does occur with a word in the test data, the value associated with the key changes to 1 even if the key occurs more than once.
+This is necessary because the machine learning algorithm we used does not attempt to analyze the keys beyond simple equality, so higher numbers than one could have masked the possibly more important distinction between 0 and not-0.
+In other words, keeping track of the instances of occurrence vs clustering them into 2 groups reduces the sparsity of the data and allows for a higher chance of accurate classifications based on the limited training data that we have.
+This is an especially important consideration since the feature vectors that select the most common words by looking through all the instances of unique lexical items in the training data are unsupervised.
+
+\section{Methods}
+\newcommand\few{few}
+We ran the system with several hundred different combinations of features over all the words in the input set.
+
+We identified optimal feature combinations through backward stepwise simple linear regression
+and through the creation and visual analysis of charts. The former has the
+advantage of discovering relationships and testing them more quantitatively
+but has the disadvantage of making assumptions about normality, linearity and equal variance.
+The latter has the advantage of elucidating more complex and higher-order relationships.
+
+We ran a more detailed analysis on the top \few systems.
+This analysis included consideration of all three grain-levels of score and scores by word.
+
+\section{Results}
+
+\subsubsection{Stepwise regression}
+We ran backward stepwise regression with the F-measure from the coarse-grained scores
+regressed on predictors representing the feature combination.
+The saturated model contained the following predictors and all interactions
+\begin{itemize}
+\item Classifier (naive Bayes or decision list)
+\item Collocation window length (0--8)
+\item Cooccurrence handling (on or off)
+\item Base word handling (on or off)
+\item Bootstrap iterations (0--4)
+\item Dependency parsing (on or off)
+\end{itemize}
+The predictor combination yeilding the lowest value of the Akaike information criterion
+included the following parameters.
+\begin{itemize}
+\item Intercept
+\item Classifier
+\item Collocation window size
+\item Coocurrence
+\item Base word handling
+\item Classifier$\times$collocation window size interaction
+\item Classifier$\times$cooccurrence interaction
+\end{itemize}
+This does not include bootstrap iterations, indicating that changes
+in bootstrap iterations does not substantially change the F-measure.
+
+%Discuss the coefficients in the regression table
+Call:
+lm(formula = f ~ classifier + collocation + cooccurrence + base_word +     dependency_parsing + classifier:collocation + classifier:cooccurrence +     collocation:cooccurrence + collocation:dependency_parsing +     cooccurrence:dependency_parsing + collocation:cooccurrence:dependency_parsing,     data = plot.step.import())
+
+Coefficients:
+\begin{tabular}{l r}
+                                (Intercept) & 0.5557355 \\
+                                classifiert & 0.0444331  \\
+                                 collocation & 0.0030636  \\
+                              cooccurrence1 & 0.0276413 \\
+                                 base_word1 & 0.0124008  \\
+                         dependency_parsing & -0.0019423 \\
+                     classifiert:collocation & -0.0132109 \\
+                  classifiert:cooccurrence1 & -0.0271825 \\
+                   collocation:cooccurrence1 & -0.0007417 \\
+              collocation:dependency_parsing & -0.0003464 \\
+           cooccurrence1:dependency_parsing & -0.1611043 \\
+collocation:cooccurrence1:dependency_parsing & 0.0147078  \\
+\end{tabular}
+
+%The negative interaction terms may indicate that the interacting features provide
+similar functionality and blah blah blah
+
+\subsubsection{Graphical methods}
+We began by plotting the predictors that seemed most influential in the
+stepwise regression.
+
+%stepwise graph 1
+%classifiert, collocation, cooccurrence  
+%Interpret this graph
+
+Collocation window of size 2--4 had the best performance, so we looked more closely at those.
+
+%stepwise graph 2
+
+more discussin of graphs
+
+%stepwise graph 33
+
+\subsection{Characterization of the top feature combinations}
+
+%Let's get a comparison between our best performer(s) and the baseline
+
+\section{Discussion}
+
+\subsection{Bootstrapping}
+
+Bootstrapping did not seem to be an effective method for improving accuracy.
+This is probably because the input data is not very clean, and additionally our system is probably not very accurately estimating confidence.
+When the system is not confident, it bootstraps very few examples, so it does not significantly change the model.
+
+\subsection{Methods We Discarded}
+
+We attempted some preliminary testing on a variety of features, but did not include them because they did not seem to provide insight:
+
+\subsubsection{Sentence Length}
+For the sentence containing the word of interest, we extracted sentence length in both characters and words. We ran two preliminary tests to see whether this feature might be useful.
+
+First, we used nearest-neighbor clustering to sort the lengths for a particular word into as many groups as the word had senses.
+The clusters did not seem to be related to a particular word sense; the chance of a particular instance being in a particular group seemed to be independent of its sense.
+
+Second, we plotted histograms sentence length.
+The distributions appeared to be unimodal, further suggesting that the lengths could not be nicely grouped into sense clusters, or any clusters for that matter.
+
+\subsubsection{Common Words in Context}
+An idea for a feature extractor was to take the most common words in a context of a lexeme and use those words as features.
+Based off of the cooccurrence code, this would generate a vector from the training data, find the most common words from the test data, and then run the collected data through the classifier.
+
+Unfortunately, this feature extractor did not give very good results.
+Both the precision and recall for this feature extractor alone on the EnglishLS test data were 0.039.
+This is to be expected since it is essentially the cooccurrence feature extractor but without grouping data into buckets.
+The sparsity problem is even more noticeable in this extractor.
+
+\subsubsection{Part of Speech Tagging For Target Words}
+We built a part-of-speech tagger and trained it on the Brown corpus.
+We planned on using it to tag words, but the target words were already grouped by part of speech, (activate.\texttbf{v}) so we did not use it.
+
+%We're using this now, just on a different corpus, right?
+%\subsubsection{Bootstrapping on the Brown Corpus} 
+%The instances of the target words in the Brown corpus were very few, e.g., activate appeared only 3 times, and bootstrapping didn't seem to be very accurate in general.
+
+\subsubsection{Dependency Parsing}
+
+For all of its sophistication, the dependency parser didn't seem to improve results.
+This is probably because most of the relationships caught by the parser would have been caught by the collocation feature extractor as well, since most dependency relations are among nearby words.
+
+\subsubsection{Collocation}
+
+Collocation seemed to be a fairly powerful disambugator, which is to be expected, since function words near to the target word can be very strong predictors of how the word is being used in context.
+Effectiveness was strongest with words close to the target, and weaker the farther away we extended the feature.
+
+\subsubsection{Interactions Between Features}
+
+In principle, adding more features should not decrease our accuracy assuming that they're at worst non-predictive, and not somehow anti-predictive, where they fool the machine learning algorithm during training and fail spectacularly on the test corpora.
+However, because the size of the datasets is so small, it is probable that the machine learning algorithm has too many features and too few examples to reliably disambiguate between them, which is why we see decreased effectiveness as we turn up the number of features, particularly with the size of the collocation features.
+This suggests that, if the training corpus is small, it is appropriate to study which features are the most useful, and only include those, rather than our initial approach of throwing them all together and letting the learning algorithm sort it out.
+
+\end{description}
+
+\end{document}

### 2011-04-14 paper/paper.tex
added \end

--- 2011-04-05 paper/paper.tex
@@
 \documentclass{article}
+\usepackage{url}
+\title{Word Sense Disambiguation\\
+\small{Leveraging the NLTK Toolkit and External Tools}}
+\author{
+Alec Story
+Ansu Abraham
+Craig Frey\\
+Dustin Tiedemann
+Michael Zhu
+Thomas Levine
+Whitney Foster\\
+}
+
 \begin{document}
+\maketitle
 
-\section{Selecting optimal feature combination}
+\section{Overview}
+
+We  chose to implement our system in Python, and chose to use the machine
+learning algorithms in the NLTK toolkit which is also Python-based.
+
+We wrote our main control program, classify.py, so that it can choose either
+[we're just doing nb and decision trees now right?] classifier and any
+combination of  features. On top of this we wrote bash scripts that automated
+looping through every combination of classifiers and features, along with
+porting the results directly into the scorer.  Classify.py includes a help
+switch -h, that explains the switches that control the different classifiers
+and features along with any additional parameters that a certain feature might
+support (for example, collocation has a window size parameter which defaults to
+0) Performance was excellent for most of the features, allowing us to typically
+run all of the words in the test set through every combination a classifier and
+feature set in under an hour. (The number of runs can get quite high when you
+factor in several parameters per feature, not just on/off)
+
+A baseline was run by choosing the most frequent sense for each word.
+
+\subsection{Data details}
+
+The  NLTK has a corpus reader  that imports Senseval-2 files. The Senseval-3
+file format is slightly  different which necessitated a few changes. We
+separated the training  and test files by word into .pos files to match  what
+the existing  parser looked for. In the interest of time we modified  the
+training and  test files to contain a single tagged word per chunk  (but still
+allowing for multiple senses) again to match the Senseval-2  format.
+
+\subsection{Selecting optimal feature combination}
 \newcommand\ward{forward} %or maybe backwards
+
 We used a \ward stepwise approach to indentifying optimal feature combinations.
-We first ran the system with all features on, producing a total of $256=2^8$ combinations.
-We then used backwards stepwise regression to identify feature combinations
-with a small number of features but with high performance
+We first ran the system with all features on, producing a total of $256=2^8$
+combinations.  We then used backwards stepwise regression to identify feature
+combinations with a small number of features but with high performance
+
+\section{System}
+
+We made heavy use of python's NLTK
+package\footnote{\url{http://www.nltk.org/}}, using its classifiers as our
+machine learning engines, and several of its other packages for analysis.
+
+\subsection{Classifiers}
+
+The NLTK was used to implement two machine learning algorithms, naive Bayes and
+decision trees.
+
+\subsubsection{Naive Bayes}
+
+The NLTK implements a naï bayes classifier which chooses the best sense given a
+dictionary of features and assigns confidence probabilities to the chosen
+sense. Naive bayes does assume an independence of features. The probability of
+each feature contributes to the overall choice.
+
+\subsubsection{Decision Tree}
+
+The NLTK also implements a decision list classifier in which a sequence of
+tests is applied to each target-word feature vector. Each test indicates a
+particular sense of the word: if the test succeeds, the sense of the test is
+returned otherwise the next test in the sequence is performed.
+
+Naive Bayes supported probability estimation, while the decision tree did not.
+
+\subsection{Confidence Cutoffs}
+
+NLTK provides probability measures for each of its guesses when using the
+maximum entropy and the naive Bayes learning methods.  We harnessed these to
+determine the cutoff for making a guess, or resorting to a ``U'' if we were
+unconfident in the tagging.  Occasional unknowns also occur because such
+unknowns are present in the training data, and we made no effort to remove
+them, so the learning algorithm views them as any other label.
+
+% Should we mention which cutoff we used?  Which did we use?
+
+\subsection{Bootstrapping}
+
+We used the same probability measure from the confidence cutoffs to fuel a
+bootstrapping method.  Instead of directly taking the output of the classifier,
+we instead looked at its performance on the test data, and wherever it was very
+confident, we copied that test instance to the training data, and repeated this
+cycle for a fixed number of cycles.  Once we had enriched the training data, we
+ran the classifier a final time to perform classification.
+
+Fortunately, the classifiers were very fast, and almost all of the time the
+system spends is in reading input and building feature sets, which don't need
+to be repeated, so bootstrapping is very cheap to include.
+
+% Should we mention which probability measure we used?  Which did we use?  How
+% many iterations?
+
+\section{Looking through Different Corpora}
+
+In order to get more data to use with the bootstrapping algorithm, we attempted
+to search through the Brown corpus and return all of the words that were being
+disambiguated in the Senseval 3 task.  To do this we needed to find all of the
+instances of the words that we needed to disambiguate and return a context
+(list of words) and the position of the word in that list.  We also made sure
+that we the context that we returned both started at the beginning of the
+sentence and ended at the end of a sentence and had a minimum of 25 words
+returned on either side of the word.  This data would then be converted into
+the form of the data that we received from the Senseval document and ran
+through the bootstrapping algorithm to have more data to train with.  However
+when we actually tested this feature alone we found it to be very
+uninformative.  First, there were very few instances of the words that we were
+looking for (ex: activate only appeared 3 times), which made searching through
+the entire corpus to find these words more time consuming than it was helpful.
+Therefore, we decided not to use it for the actual test because it was not
+informative enough by itself.
+
+\subsection{Base Word}
+
+Because the target words were grouped by part of speech, we included the word
+as it appears literally in context as a feature.  For example, ``activate''
+versus ``activating,'' which both appear under activate.v.
+
+\subsection{Dependency Parsing}
+
+We included as one feature the MaltParser dependency parser, and used the
+engmalt.linear.mco linear support vector machine
+configuration\footnote{\url{http://maltparser.org/mco/english_parser/engmalt.html}}
+for parsing (the other option was an SVM with a polynomial kernel, which the
+Malt website said would run just as accurately, more slowly, but with less
+memory, so we decided to go with the faster option).
+
+From the parser we rendered several features:
+
+\begin{description}
+
+\item[The Dependency:] whatever the first of the list of dependencies given for
+the target word is.  It is difficult to represent lists in the key and value
+feature format, so we did not attempt to.  Instead, we use the rest of the
+features as mitigating factors.  The empty string if there is no dependency.
+
+\item[Presence of Absence of Dependency]
+
+\item[Number of Dependencies]
+
+\item[The Parent:] the word with the target word as (one of) its dependencies.
+
+\end{description}
+
+Dependency parsing is fairly slow, requiring about a second per instance to run
+on a computer running an Atom D525 processor (which is fairly underpowered, but
+modern).  To help alleviate this problem, we wrote a system that saves parses
+for each context, and only calls the parser if it observes a new parse, so we
+could reuse parsing information across runs of our program.  Because this file
+is several hundred megabytes in size, it is not included in our submitted code.
+\subsection{Collocation}
+
+Encodes the part-of-speech tag of words to the left and right of the target
+word. The number of words extracted is determined by a variable window size
+(context) which the function takes in as an input. Half the window size is
+taken from left the word and half from the right of the word; thus window size
+is the total number of words examined. For an odd window size, it rounds up
+half the window size up for the part left of the word and rounds down for the
+part right of the word.
+
+\end{document}

### 2011-04-14 paper/paper.tex
the rest of the paper and cleanup

--- 2011-04-14 paper/paper.tex
@@
 \section{Overview}
-We  chose to implement our system in Python, and chose to use the machine learning algorithms in the NLTK toolkit which is also Python-based.
 
-We wrote our main control program, classify.py, so that it can choose either [we're just doing nb and decision trees now right?] classifier and any combination of  features.
-On top of this we wrote bash scripts that automated looping through every combination of classifiers and features, along with porting the results directly into the scorer.
-Classify.py includes a help switch -h, that explains the switches that control the different classifiers and features along with any additional parameters that a certain feature might support (for example, collocation has a window size parameter which defaults to 0)
-Performance was excellent for most of the features, allowing us to typically run all of the words in the test set through every combination a classifier and feature set in under an hour.
-(The number of runs can get quite high when you factor in several parameters per feature, not just on/off)
+We  chose to implement our system in Python, and chose to use the machine
+learning algorithms in the NLTK toolkit which is also Python-based.
+
+We wrote our main control program, classify.py, so that it can choose either
+[we're just doing nb and decision trees now right?] classifier and any
+combination of  features. On top of this we wrote bash scripts that automated
+looping through every combination of classifiers and features, along with
+porting the results directly into the scorer.  Classify.py includes a help
+switch -h, that explains the switches that control the different classifiers
+and features along with any additional parameters that a certain feature might
+support (for example, collocation has a window size parameter which defaults to
+0) Performance was excellent for most of the features, allowing us to typically
+run all of the words in the test set through every combination a classifier and
+feature set in under an hour. (The number of runs can get quite high when you
+factor in several parameters per feature, not just on/off)
 
@@
 \subsection{Data details}
-The  NLTK has a corpus reader  that imports Senseval-2 files.
-The Senseval-3  file format is slightly  different which necessitated a few changes.
-We separated the training  and test files by word into .pos files to match  what the existing  parser looked for.
-In the interest of time we modified  the training and  test files to contain a single tagged word per chunk  (but still  allowing for multiple senses) again to match the Senseval-2  format.
+
+The  NLTK has a corpus reader  that imports Senseval-2 files. The Senseval-3
+file format is slightly  different which necessitated a few changes. We
+separated the training  and test files by word into .pos files to match  what
+the existing  parser looked for. In the interest of time we modified  the
+training and  test files to contain a single tagged word per chunk  (but still
+allowing for multiple senses) again to match the Senseval-2  format.
 
@@
 \newcommand\ward{forward} %or maybe backwards
+
 We used a \ward stepwise approach to indentifying optimal feature combinations.
-We first ran the system with all features on, producing a total of $256=2^8$ combinations.
-We then used backwards stepwise regression to identify feature combinations
-with a small number of features but with high performance
+We first ran the system with all features on, producing a total of $256=2^8$
+combinations.  We then used backwards stepwise regression to identify feature
+combinations with a small number of features but with high performance
 
@@
 
-We made heavy use of python's NLTK package\footnote{\url{http://www.nltk.org/}}, using its classifiers as our machine learning engines, and several of its other packages for analysis.
+We made heavy use of python's NLTK
+package\footnote{\url{http://www.nltk.org/}}, using its classifiers as our
+machine learning engines, and several of its other packages for analysis.
 
@@
 
-The NLTK was used to implement two machine learning algorithms, naive Bayes and decision trees.
+The NLTK was used to implement two machine learning algorithms, naive Bayes and
+decision trees.
 
@@
 
-The NLTK implements a naïve bayes classifier which chooses the best sense given a dictionary of features and assigns confidence probabilities to the chosen sense.
-Naive bayes does assume an independence of features.
-The probability of each feature contributes to the overall choice.
+The NLTK implements a naï bayes classifier which chooses the best sense given a
+dictionary of features and assigns confidence probabilities to the chosen
+sense. Naive bayes does assume an independence of features. The probability of
+each feature contributes to the overall choice.
 
@@
 
-The NLTK also implements a decision list classifier in which a sequence of tests is applied to each target-word feature vector.
-Each test indicates a particular sense of the word: if the test succeeds, the sense of the test is returned otherwise the next test in the sequence is performed.
+The NLTK also implements a decision list classifier in which a sequence of
+tests is applied to each target-word feature vector. Each test indicates a
+particular sense of the word: if the test succeeds, the sense of the test is
+returned otherwise the next test in the sequence is performed.
 
@@
 maximum entropy and the naive Bayes learning methods.  We harnessed these to
-determine the cutoff for making a guess, or resorting to a ``U'' if we were unconfident in the tagging.
-Occasional unknowns also occur because such unknowns are present in the training data, and we made no effort to remove them, so the learning algorithm views them as any other label.
+determine the cutoff for making a guess, or resorting to a ``U'' if we were
+unconfident in the tagging.  Occasional unknowns also occur because such
+unknowns are present in the training data, and we made no effort to remove
+them, so the learning algorithm views them as any other label.
 
@@
 Fortunately, the classifiers were very fast, and almost all of the time the
-system spends is in reading input and building feature sets, which don't need to
-be repeated, so bootstrapping is very cheap to include.
+system spends is in reading input and building feature sets, which don't need
+to be repeated, so bootstrapping is very cheap to include.
 
@@
 
+\section{Looking through Different Corpora}
+
+In order to get more data to use with the bootstrapping algorithm, we attempted
+to search through the Brown corpus and return all of the words that were being
+disambiguated in the Senseval 3 task.  To do this we needed to find all of the
+instances of the words that we needed to disambiguate and return a context
+(list of words) and the position of the word in that list.  We also made sure
+that we the context that we returned both started at the beginning of the
+sentence and ended at the end of a sentence and had a minimum of 25 words
+returned on either side of the word.  This data would then be converted into
+the form of the data that we received from the Senseval document and ran
+through the bootstrapping algorithm to have more data to train with.  However
+when we actually tested this feature alone we found it to be very
+uninformative.  First, there were very few instances of the words that we were
+looking for (ex: activate only appeared 3 times), which made searching through
+the entire corpus to find these words more time consuming than it was helpful.
+Therefore, we decided not to use it for the actual test because it was not
+informative enough by itself.
+
 \subsection{Base Word}
 
-Because the target words were grouped by part of speech, we included the word as it appears literally in context as a feature.
-For example, ``activate'' versus ``activating,'' which both appear under activate.v.
+Because the target words were grouped by part of speech, we included the word
+as it appears literally in context as a feature.  For example, ``activate''
+versus ``activating,'' which both appear under activate.v.
 
@@
 for parsing (the other option was an SVM with a polynomial kernel, which the
-Malt website said would run just as accurately, more slowly, but with less memory,
-so we decided to go with the faster option).
+Malt website said would run just as accurately, more slowly, but with less
+memory, so we decided to go with the faster option).
 
 From the parser we rendered several features:
+
 \begin{description}
 
-\item[The Dependency:] whatever the first of the list of dependencies given for the target word is.
-It is difficult to represent lists in the key and value feature format, so we did not attempt to.
-Instead, we use the rest of the features as mitigating factors.
-The empty string if there is no dependency.
+\item[The Dependency:] whatever the first of the list of dependencies given for
+the target word is.  It is difficult to represent lists in the key and value
+feature format, so we did not attempt to.  Instead, we use the rest of the
+features as mitigating factors.  The empty string if there is no dependency.
 
@@
 
-Dependency parsing is fairly slow, requiring about a second per instance to run on a computer running an Atom D525 processor (which is fairly underpowered, but modern).
-To help alleviate this problem, we wrote a system that saves parses for each context, and only calls the parser if it observes a new parse, so we could reuse parsing information across runs of our program.
-Because this file is several hundred megabytes in size, it is not included in our submitted code.
-
+Dependency parsing is fairly slow, requiring about a second per instance to run
+on a computer running an Atom D525 processor (which is fairly underpowered, but
+modern).  To help alleviate this problem, we wrote a system that saves parses
+for each context, and only calls the parser if it observes a new parse, so we
+could reuse parsing information across runs of our program.  Because this file
+is several hundred megabytes in size, it is not included in our submitted code.
 \subsection{Collocation}
 
-Encodes the part-of-speech tag of words to the left and right of the target word.
-The number of words extracted is determined by a variable window size (context) which the function takes in as an input.
-Half the window size is taken from left the word and half from the right of the word; thus window size is the total number of words examined.
-For an odd window size, it rounds up half the window size up for the part left of the word and rounds down for the part right of the word.
+Encodes the part-of-speech tag of words to the left and right of the target
+word. The number of words extracted is determined by a variable window size
+(context) which the function takes in as an input. Half the window size is
+taken from left the word and half from the right of the word; thus window size
+is the total number of words examined. For an odd window size, it rounds up
+half the window size up for the part left of the word and rounds down for the
+part right of the word.
 
-We rendered a feature for each position covered, and set its value to be the word at that position.
+We rendered a feature for each position covered, and set its value to be the
+word at that position.
 
-We also used nltk's part of speech tagger to tag the context, and included those as we did the literal words in the feature set.
-This was trained on nltk's \verb+maximum entropy treebank pos tagger+ data, which is included with the nltk package.
+We also used nltk's part of speech tagger to tag the context, and included those
+as we did the literal words in the feature set.  This was trained on nltk's
+\verb+maximum entropy treebank pos tagger+ data, which is included with the nltk
+package.
 
 \subsection{Cooccurrence}
-Looks through the training data and compiles a list of most common words for each item in the data.
-When the test data is run, the feature looks for the created vector and uses that instead of trying to make a new one.
-Next the extractor takes a window of words around the head word and generates the 0, 1 tuple of features for inclusion to the dictionary.
-This word list is used as the keys of the feature vector when using the test data as a list of words that may cooccur with each item in the data.
-The value associated with each key in the feature vector starts out as 0 (for occurring 0 times in the window near a test word) If a key in the feature vector does occur with a word in the test data, the value associated with the key changes to 1 even if the key occurs more than once.
-This is necessary because the machine learning algorithm we used does not attempt to analyze the keys beyond simple equality, so higher numbers than one could have masked the possibly more important distinction between 0 and not-0.
-In other words, keeping track of the instances of occurrence vs clustering them into 2 groups reduces the sparsity of the data and allows for a higher chance of accurate classifications based on the limited training data that we have.
-This is an especially important consideration since the feature vectors that select the most common words by looking through all the instances of unique lexical items in the training data are unsupervised.
+
+Looks through the training data and compiles a list of most common words for
+each item in the data. When the test data is run, the feature looks for the
+created vector and uses that instead of trying to make a new one. Next the
+extractor takes a window of words around the head word and generates the 0, 1
+tuple of features for inclusion to the dictionary. This word list is used as the
+keys of the feature vector when using the test data as a list of words that may
+cooccur with each item in the data. The value associated with each key in the
+feature vector starts out as 0 (for occurring 0 times in the window near a test
+word) If a key in the feature vector does occur with a word in the test data,
+the value associated with the key changes to 1 even if the key occurs more than
+once.  This is necessary because the machine learning algorithm we used does not
+attempt to analyze the keys beyond simple equality, so higher numbers than one
+could have masked the possibly more important distinction between 0 and not-0.
+In other words, keeping track of the instances of occurrence vs clustering them
+into 2 groups reduces the sparsity of the data and allows for a higher chance of
+accurate classifications based on the limited training data that we have. This
+is an especially important consideration since the feature vectors that select
+the most common words by looking through all the instances of unique lexical
+items in the training data are unsupervised.
 
@@
 \newcommand\few{few}
-We ran the system with several hundred different combinations of features over all the words in the input set.
 
-We identified optimal feature combinations through backward stepwise simple linear regression
-and through the creation and visual analysis of charts. The former has the
-advantage of discovering relationships and testing them more quantitatively
-but has the disadvantage of making assumptions about normality, linearity and equal variance.
-The latter has the advantage of elucidating more complex and higher-order relationships.
+We ran the system with several hundred different combinations of features over
+all the words in the input set.
 
-We ran a more detailed analysis on the top \few systems.
-This analysis included consideration of all three grain-levels of score and scores by word.
+We identified optimal feature combinations through backward stepwise simple
+linear regression and through the creation and visual analysis of charts. The
+former has the advantage of discovering relationships and testing them more
+quantitatively but has the disadvantage of making assumptions about normality,
+linearity and equal variance.  The latter has the advantage of elucidating more
+complex and higher-order relationships.
+
+We ran a more detailed analysis on the top \few systems.  This analysis included
+consideration of all three grain-levels of score and scores by word.
 
@@
 \subsubsection{Stepwise regression}
-We ran backward stepwise regression with the F-measure from the coarse-grained scores
-regressed on predictors representing the feature combination.
-The saturated model contained the following predictors and all interactions
+
+We ran backward stepwise regression with the F-measure from the coarse-grained
+scores regressed on predictors representing the feature combination.  The
+saturated model contained the following predictors and all interactions
+
 \begin{itemize}
@@
 \end{itemize}
+
 The predictor combination yeilding the lowest value of the Akaike information criterion
 included the following parameters.
+
 \begin{itemize}
@@
 \end{itemize}
+
 This does not include bootstrap iterations, indicating that changes
@@
 %Discuss the coefficients in the regression table
-Call:
-lm(formula = f ~ classifier + collocation + cooccurrence + base_word +     dependency_parsing + classifier:collocation + classifier:cooccurrence +     collocation:cooccurrence + collocation:dependency_parsing +     cooccurrence:dependency_parsing + collocation:cooccurrence:dependency_parsing,     data = plot.step.import())
+%Call:
+%lm(formula = f ~ classifier + collocation + cooccurrence + base_word +     dependency_parsing + classifier:collocation + classifier:cooccurrence +     collocation:cooccurrence + collocation:dependency_parsing +     cooccurrence:dependency_parsing + collocation:cooccurrence:dependency_parsing,     data = plot.step.import())
 
 Coefficients:
+
 \begin{tabular}{l r}
@@
                               cooccurrence1 & 0.0276413 \\
-                                 base_word1 & 0.0124008  \\
-                         dependency_parsing & -0.0019423 \\
+                                 base word1 & 0.0124008  \\
+                         dependency parsing & -0.0019423 \\
                      classifiert:collocation & -0.0132109 \\
@@
                    collocation:cooccurrence1 & -0.0007417 \\
-              collocation:dependency_parsing & -0.0003464 \\
-           cooccurrence1:dependency_parsing & -0.1611043 \\
-collocation:cooccurrence1:dependency_parsing & 0.0147078  \\
+              collocation:dependency parsing & -0.0003464 \\
+           cooccurrence1:dependency parsing & -0.1611043 \\
+collocation:cooccurrence1:dependency parsing & 0.0147078  \\
 \end{tabular}
@@
 
-\subsubsection{Sentence Length}
-For the sentence containing the word of interest, we extracted sentence length in both characters and words. We ran two preliminary tests to see whether this feature might be useful.
+\subsubsection{Sentence Length} For the sentence containing the word of
+interest, we extracted sentence length in both characters and words. We ran two
+preliminary tests to see whether this feature might be useful.
 
-First, we used nearest-neighbor clustering to sort the lengths for a particular word into as many groups as the word had senses.
-The clusters did not seem to be related to a particular word sense; the chance of a particular instance being in a particular group seemed to be independent of its sense.
+First, we used nearest-neighbor clustering to sort the lengths for a particular
+word into as many groups as the word had senses. The clusters did not seem to be
+related to a particular word sense; the chance of a particular instance being in
+a particular group seemed to be independent of its sense.
 
-Second, we plotted histograms sentence length.
-The distributions appeared to be unimodal, further suggesting that the lengths could not be nicely grouped into sense clusters, or any clusters for that matter.
+Second, we plotted histograms sentence length. The distributions appeared to be
+unimodal, further suggesting that the lengths could not be nicely grouped into
+sense clusters, or any clusters for that matter.
 
 \subsubsection{Common Words in Context}
-An idea for a feature extractor was to take the most common words in a context of a lexeme and use those words as features.
-Based off of the cooccurrence code, this would generate a vector from the training data, find the most common words from the test data, and then run the collected data through the classifier.
 
-Unfortunately, this feature extractor did not give very good results.
-Both the precision and recall for this feature extractor alone on the EnglishLS test data were 0.039.
-This is to be expected since it is essentially the cooccurrence feature extractor but without grouping data into buckets.
-The sparsity problem is even more noticeable in this extractor.
+An idea for a feature extractor was to take the most common words in a context
+of a lexeme and use those words as features. Based off of the cooccurrence code,
+this would generate a vector from the training data, find the most common words
+from the test data, and then run the collected data through the classifier.
+
+Unfortunately, this feature extractor did not give very good results. Both the
+precision and recall for this feature extractor alone on the EnglishLS test data
+were 0.039. This is to be expected since it is essentially the cooccurrence
+feature extractor but without grouping data into buckets. The sparsity problem
+is even more noticeable in this extractor.
 
 \subsubsection{Part of Speech Tagging For Target Words}
-We built a part-of-speech tagger and trained it on the Brown corpus.
-We planned on using it to tag words, but the target words were already grouped by part of speech, (activate.\texttbf{v}) so we did not use it.
+
+We built a part-of-speech tagger and trained it on the Brown corpus. We planned
+on using it to tag words, but the target words were already grouped by part of
+speech, (activate.\textbf{v}) so we did not use it.
 
@@
 
-For all of its sophistication, the dependency parser didn't seem to improve results.
-This is probably because most of the relationships caught by the parser would have been caught by the collocation feature extractor as well, since most dependency relations are among nearby words.
+For all of its sophistication, the dependency parser didn't seem to improve
+results.  This is probably because most of the relationships caught by the
+parser would have been caught by the collocation feature extractor as well,
+since most dependency relations are among nearby words.
 
@@
 
-Collocation seemed to be a fairly powerful disambugator, which is to be expected, since function words near to the target word can be very strong predictors of how the word is being used in context.
-Effectiveness was strongest with words close to the target, and weaker the farther away we extended the feature.
+Collocation seemed to be a fairly powerful disambugator, which is to be
+expected, since function words near to the target word can be very strong
+predictors of how the word is being used in context.  Effectiveness was
+strongest with words close to the target, and weaker the farther away we
+extended the feature.
 
@@
 
-In principle, adding more features should not decrease our accuracy assuming that they're at worst non-predictive, and not somehow anti-predictive, where they fool the machine learning algorithm during training and fail spectacularly on the test corpora.
-However, because the size of the datasets is so small, it is probable that the machine learning algorithm has too many features and too few examples to reliably disambiguate between them, which is why we see decreased effectiveness as we turn up the number of features, particularly with the size of the collocation features.
-This suggests that, if the training corpus is small, it is appropriate to study which features are the most useful, and only include those, rather than our initial approach of throwing them all together and letting the learning algorithm sort it out.
-
-\end{description}
+In principle, adding more features should not decrease our accuracy assuming
+that they're at worst non-predictive, and not somehow anti-predictive, where
+they fool the machine learning algorithm during training and fail spectacularly
+on the test corpora.  However, because the size of the datasets is so small, it
+is probable that the machine learning algorithm has too many features and too
+few examples to reliably disambiguate between them, which is why we see
+decreased effectiveness as we turn up the number of features, particularly with
+the size of the collocation features.  This suggests that, if the training
+corpus is small, it is appropriate to study which features are the most useful,
+and only include those, rather than our initial approach of throwing them all
+together and letting the learning algorithm sort it out.
 

### 2011-04-14 paper/paper.tex
byword sheet

--- 2011-04-14 paper/paper.tex
@@
 %Discuss the coefficients in the regression table
-Call:
-lm(formula = f ~ classifier + collocation + cooccurrence + base_word +     dependency_parsing + classifier:collocation + classifier:cooccurrence +     collocation:cooccurrence + collocation:dependency_parsing +     cooccurrence:dependency_parsing + collocation:cooccurrence:dependency_parsing,     data = plot.step.import())
-
-Coefficients:
-\begin{tabular}{l r}
-                                (Intercept) & 0.5557355 \\
-                                classifiert & 0.0444331  \\
-                                 collocation & 0.0030636  \\
-                              cooccurrence1 & 0.0276413 \\
-                                 base_word1 & 0.0124008  \\
-                         dependency_parsing & -0.0019423 \\
-                     classifiert:collocation & -0.0132109 \\
-                  classifiert:cooccurrence1 & -0.0271825 \\
-                   collocation:cooccurrence1 & -0.0007417 \\
-              collocation:dependency_parsing & -0.0003464 \\
-           cooccurrence1:dependency_parsing & -0.1611043 \\
-collocation:cooccurrence1:dependency_parsing & 0.0147078  \\
-\end{tabular}
 

### 2011-04-14 paper/paper.tex

@@
 
-Dependency parsing is fairly slow, requiring about a second per instance to run on a computer running an Atom D525 processor (which is fairly underpowered, but modern).
-To help alleviate this problem, we wrote a system that saves parses for each context, and only calls the parser if it observes a new parse, so we could reuse parsing information across runs of our program.
-Because this file is several hundred megabytes in size, it is not included in our submitted code.
-
+Dependency parsing is fairly slow, requiring about a second per instance to run
+on a computer running an Atom D525 processor (which is fairly underpowered, but
+modern).  To help alleviate this problem, we wrote a system that saves parses
+for each context, and only calls the parser if it observes a new parse, so we
+could reuse parsing information across runs of our program.  Because this file
+is several hundred megabytes in size, it is not included in our submitted code.
 \subsection{Collocation}

### 2011-04-14 paper/paper.tex
minor editing

@@
 We  chose to implement our system in Python, and chose to use the machine
-learning algorithms in the NLTK toolkit which is also Python-based.
+learning algorithms in NLTK which is also Python-based.
+We also used NLTK for its part of speech tagger, dependecy parser, and to import the Senseval data.
+We coded the rest of the assignment on our own.
 
@@
 
-The NLTK implements a naï bayes classifier which chooses the best sense given a
+The NLTK implements a naïve bayes classifier which chooses the best sense given a
 dictionary of features and assigns confidence probabilities to the chosen
@@
 (list of words) and the position of the word in that list.  We also made sure
-that we the context that we returned both started at the beginning of the
+that the context that we returned both started at the beginning of the
 sentence and ended at the end of a sentence and had a minimum of 25 words
@@
 
-Encodes the part-of-speech tag of words to the left and right of the target word.
-The number of words extracted is determined by a variable window size (context) which the function takes in as an input.
-Half the window size is taken from left the word and half from the right of the word; thus window size is the total number of words examined.
-For an odd window size, it rounds up half the window size up for the part left of the word and rounds down for the part right of the word.
-
-We rendered a feature for each position covered, and set its value to be the word at that position.
-
-We also used nltk's part of speech tagger to tag the context, and included those as we did the literal words in the feature set.
-This was trained on nltk's \verb+maximum entropy treebank pos tagger+ data, which is included with the nltk package.
-
-\subsection{Cooccurrence}
-Looks through the training data and compiles a list of most common words for each item in the data.
-When the test data is run, the feature looks for the created vector and uses that instead of trying to make a new one.
-Next the extractor takes a window of words around the head word and generates the 0, 1 tuple of features for inclusion to the dictionary.
-This word list is used as the keys of the feature vector when using the test data as a list of words that may cooccur with each item in the data.
-The value associated with each key in the feature vector starts out as 0 (for occurring 0 times in the window near a test word) If a key in the feature vector does occur with a word in the test data, the value associated with the key changes to 1 even if the key occurs more than once.
-This is necessary because the machine learning algorithm we used does not attempt to analyze the keys beyond simple equality, so higher numbers than one could have masked the possibly more important distinction between 0 and not-0.
-In other words, keeping track of the instances of occurrence vs clustering them into 2 groups reduces the sparsity of the data and allows for a higher chance of accurate classifications based on the limited training data that we have.
-This is an especially important consideration since the feature vectors that select the most common words by looking through all the instances of unique lexical items in the training data are unsupervised.
-
-\section{Methods}
-\newcommand\few{few}
-We ran the system with several hundred different combinations of features over all the words in the input set.
-
-We identified optimal feature combinations through backward stepwise simple linear regression
-and through the creation and visual analysis of charts. The former has the
-advantage of discovering relationships and testing them more quantitatively
-but has the disadvantage of making assumptions about normality, linearity and equal variance.
-The latter has the advantage of elucidating more complex and higher-order relationships.
-
-We ran a more detailed analysis on the top \few systems.
-This analysis included consideration of all three grain-levels of score and scores by word.
-
-\section{Results}
-
-\subsubsection{Stepwise regression}
-We ran backward stepwise regression with the F-measure from the coarse-grained scores
-regressed on predictors representing the feature combination.
-The saturated model contained the following predictors and all interactions
-\begin{itemize}
-\item Classifier (naive Bayes or decision list)
-\item Collocation window length (0--8)
-\item Cooccurrence handling (on or off)
-\item Base word handling (on or off)
-\item Bootstrap iterations (0--4)
-\item Dependency parsing (on or off)
-\end{itemize}
-The predictor combination yeilding the lowest value of the Akaike information criterion
-included the following parameters.
-\begin{itemize}
-\item Intercept
-\item Classifier
-\item Collocation window size
-\item Coocurrence
-\item Base word handling
-\item Classifier$\times$collocation window size interaction
-\item Classifier$\times$cooccurrence interaction
-\end{itemize}
-This does not include bootstrap iterations, indicating that changes
-in bootstrap iterations does not substantially change the F-measure.
-
-%Discuss the coefficients in the regression table
-
-%The negative interaction terms may indicate that the interacting features provide
-similar functionality and blah blah blah
-
-\subsubsection{Graphical methods}
-We began by plotting the predictors that seemed most influential in the
-stepwise regression.
-
-%stepwise graph 1
-%classifiert, collocation, cooccurrence  
-%Interpret this graph
-
-Collocation window of size 2--4 had the best performance, so we looked more closely at those.
-
-%stepwise graph 2
-
-more discussin of graphs
-
-%stepwise graph 33
-
-\subsection{Characterization of the top feature combinations}
-
-%Let's get a comparison between our best performer(s) and the baseline
-
-\section{Discussion}
-
-\subsection{Bootstrapping}
-
-Bootstrapping did not seem to be an effective method for improving accuracy.
-This is probably because the input data is not very clean, and additionally our system is probably not very accurately estimating confidence.
-When the system is not confident, it bootstraps very few examples, so it does not significantly change the model.
-
-\subsection{Methods We Discarded}
-
-We attempted some preliminary testing on a variety of features, but did not include them because they did not seem to provide insight:
-
-\subsubsection{Sentence Length}
-For the sentence containing the word of interest, we extracted sentence length in both characters and words. We ran two preliminary tests to see whether this feature might be useful.
-
-First, we used nearest-neighbor clustering to sort the lengths for a particular word into as many groups as the word had senses.
-The clusters did not seem to be related to a particular word sense; the chance of a particular instance being in a particular group seemed to be independent of its sense.
-
-Second, we plotted histograms sentence length.
-The distributions appeared to be unimodal, further suggesting that the lengths could not be nicely grouped into sense clusters, or any clusters for that matter.
-
-\subsubsection{Common Words in Context}
-An idea for a feature extractor was to take the most common words in a context of a lexeme and use those words as features.
-Based off of the cooccurrence code, this would generate a vector from the training data, find the most common words from the test data, and then run the collected data through the classifier.
-
-Unfortunately, this feature extractor did not give very good results.
-Both the precision and recall for this feature extractor alone on the EnglishLS test data were 0.039.
-This is to be expected since it is essentially the cooccurrence feature extractor but without grouping data into buckets.
-The sparsity problem is even more noticeable in this extractor.
-
-\subsubsection{Part of Speech Tagging For Target Words}
-We built a part-of-speech tagger and trained it on the Brown corpus.
-We planned on using it to tag words, but the target words were already grouped by part of speech, (activate.\texttbf{v}) so we did not use it.
-
-%We're using this now, just on a different corpus, right?
-%\subsubsection{Bootstrapping on the Brown Corpus} 
-%The instances of the target words in the Brown corpus were very few, e.g., activate appeared only 3 times, and bootstrapping didn't seem to be very accurate in general.
-
-\subsubsection{Dependency Parsing}
-
-For all of its sophistication, the dependency parser didn't seem to improve results.
-This is probably because most of the relationships caught by the parser would have been caught by the collocation feature extractor as well, since most dependency relations are among nearby words.
-
-\subsubsection{Collocation}
-
-Collocation seemed to be a fairly powerful disambugator, which is to be expected, since function words near to the target word can be very strong predictors of how the word is being used in context.
-Effectiveness was strongest with words close to the target, and weaker the farther away we extended the feature.
-
-\subsubsection{Interactions Between Features}
-
-In principle, adding more features should not decrease our accuracy assuming that they're at worst non-predictive, and not somehow anti-predictive, where they fool the machine learning algorithm during training and fail spectacularly on the test corpora.
-However, because the size of the datasets is so small, it is probable that the machine learning algorithm has too many features and too few examples to reliably disambiguate between them, which is why we see decreased effectiveness as we turn up the number of features, particularly with the size of the collocation features.
-This suggests that, if the training corpus is small, it is appropriate to study which features are the most useful, and only include those, rather than our initial approach of throwing them all together and letting the learning algorithm sort it out.
-
-\end{description}
-
-\end{document}
+Encodes the part-of-speech tag of words to the left and right of the target
+word. The number of words extracted is determined by a variable window size
+(context) which the function takes in as an input. Half the window size is
+taken from left the word and half from the right of the word; thus window size
+is the total number of words examined. For an odd window size, it rounds up
+half the window size up for the part left of the word and rounds down for the
+part right of the word.

### 2011-04-14 paper/paper.tex

--- 2011-04-14 paper/paper.tex
@@
 
-Encodes the part-of-speech tag of words to the left and right of the target word.
-The number of words extracted is determined by a variable window size (context) which the function takes in as an input.
-Half the window size is taken from left the word and half from the right of the word; thus window size is the total number of words examined.
-For an odd window size, it rounds up half the window size up for the part left of the word and rounds down for the part right of the word.
+Encodes the part-of-speech tag of words to the left and right of the target
+word. The number of words extracted is determined by a variable window size
+(context) which the function takes in as an input. Half the window size is
+taken from left the word and half from the right of the word; thus window size
+is the total number of words examined. For an odd window size, it rounds up
+half the window size up for the part left of the word and rounds down for the
+part right of the word.
 
-We rendered a feature for each position covered, and set its value to be the word at that position.
+We rendered a feature for each position covered, and set its value to be the
+word at that position.
 
-We also used nltk's part of speech tagger to tag the context, and included those as we did the literal words in the feature set.
-This was trained on nltk's \verb+maximum entropy treebank pos tagger+ data, which is included with the nltk package.
+We also used nltk's part of speech tagger to tag the context, and included those
+as we did the literal words in the feature set.  This was trained on nltk's
+\verb+maximum entropy treebank pos tagger+ data, which is included with the nltk
+package.
 
 \subsection{Cooccurrence}
-Looks through the training data and compiles a list of most common words for each item in the data.
-When the test data is run, the feature looks for the created vector and uses that instead of trying to make a new one.
-Next the extractor takes a window of words around the head word and generates the 0, 1 tuple of features for inclusion to the dictionary.
-This word list is used as the keys of the feature vector when using the test data as a list of words that may cooccur with each item in the data.
-The value associated with each key in the feature vector starts out as 0 (for occurring 0 times in the window near a test word) If a key in the feature vector does occur with a word in the test data, the value associated with the key changes to 1 even if the key occurs more than once.
-This is necessary because the machine learning algorithm we used does not attempt to analyze the keys beyond simple equality, so higher numbers than one could have masked the possibly more important distinction between 0 and not-0.
-In other words, keeping track of the instances of occurrence vs clustering them into 2 groups reduces the sparsity of the data and allows for a higher chance of accurate classifications based on the limited training data that we have.
-This is an especially important consideration since the feature vectors that select the most common words by looking through all the instances of unique lexical items in the training data are unsupervised.
+
+Looks through the training data and compiles a list of most common words for
+each item in the data. When the test data is run, the feature looks for the
+created vector and uses that instead of trying to make a new one. Next the
+extractor takes a window of words around the head word and generates the 0, 1
+tuple of features for inclusion to the dictionary. This word list is used as the
+keys of the feature vector when using the test data as a list of words that may
+cooccur with each item in the data. The value associated with each key in the
+feature vector starts out as 0 (for occurring 0 times in the window near a test
+word) If a key in the feature vector does occur with a word in the test data,
+the value associated with the key changes to 1 even if the key occurs more than
+once.  This is necessary because the machine learning algorithm we used does not
+attempt to analyze the keys beyond simple equality, so higher numbers than one
+could have masked the possibly more important distinction between 0 and not-0.
+In other words, keeping track of the instances of occurrence vs clustering them
+into 2 groups reduces the sparsity of the data and allows for a higher chance of
+accurate classifications based on the limited training data that we have. This
+is an especially important consideration since the feature vectors that select
+the most common words by looking through all the instances of unique lexical
+items in the training data are unsupervised.
 
@@
 %Discuss the coefficients in the regression table
+%Call:
+%lm(formula = f ~ classifier + collocation + cooccurrence + base_word +     dependency_parsing + classifier:collocation + classifier:cooccurrence +     collocation:cooccurrence + collocation:dependency_parsing +     cooccurrence:dependency_parsing + collocation:cooccurrence:dependency_parsing,     data = plot.step.import())
+
+Coefficients:
+
+\begin{tabular}{l r}
+                                (Intercept) & 0.5557355 \\
+                                classifiert & 0.0444331  \\
+                                 collocation & 0.0030636  \\
+                              cooccurrence1 & 0.0276413 \\
+                                 base word1 & 0.0124008  \\
+                         dependency parsing & -0.0019423 \\
+                     classifiert:collocation & -0.0132109 \\
+                  classifiert:cooccurrence1 & -0.0271825 \\
+                   collocation:cooccurrence1 & -0.0007417 \\
+              collocation:dependency parsing & -0.0003464 \\
+           cooccurrence1:dependency parsing & -0.1611043 \\
+collocation:cooccurrence1:dependency parsing & 0.0147078  \\
+\end{tabular}
 

### 2011-04-14 paper/paper.tex
images in badly

@@
 \usepackage{url}
+\usepackage{longtable}
+\usepackage{graphicx}
 \title{Word Sense Disambiguation\\
@@
 We  chose to implement our system in Python, and chose to use the machine
-learning algorithms in NLTK which is also Python-based.
-We also used NLTK for its part of speech tagger, dependecy parser, and to import the Senseval data.
-We coded the rest of the assignment on our own.
+learning algorithms in the NLTK toolkit which is also Python-based.
 
@@
 
-The NLTK implements a naïve bayes classifier which chooses the best sense given a
+The NLTK implements a naï bayes classifier which chooses the best sense given a
 dictionary of features and assigns confidence probabilities to the chosen
@@
 (list of words) and the position of the word in that list.  We also made sure
-that the context that we returned both started at the beginning of the
+that we the context that we returned both started at the beginning of the
 sentence and ended at the end of a sentence and had a minimum of 25 words
@@
 
-\subsubsection{Stepwise regression}
+\subsection{Stepwise regression}
 
@@
 
-\subsubsection{Graphical methods}
+\subsection{Graphical methods}
 We began by plotting the predictors that seemed most influential in the
@@
 
+\includegraphics{pg_0001}
 %stepwise graph 1
@@
 
-%stepwise graph 2
+\includegraphics{pg_0002}
 
@@
 
-%stepwise graph 33
+\includegraphics{pg_0003}
 
-\subsection{Characterization of the top feature combinations}
+\includegraphics{pg_0004}
 
-%Let's get a comparison between our best performer(s) and the baseline
+\subsection{Best Run Results}
+
+\begin{longtable}{l | r r r r r r r}
+		&	&	\multicolumn{2}{c}{Fine Grain}	&	\multicolumn{2}{c}{Course Grain}	&	\multicolumn{2}{c}{Mixed}\\
+Word	&	Corpus Size	&	Precision	&	Recall	&	Precision	&	Recall	&	Precision	&	Recall\\
+\hline
+provide.v	&	1094	&	0.906	&	0.015	&	0.938	&	0.015	&	0.922	&	0.015\\
+watch.v	&	806	&	0.878	&	0.011	&	0.918	&	0.011	&	0.918	&	0.011\\
+remain.v	&	1118	&	0.871	&	0.015	&	0.871	&	0.015	&	0.871	&	0.015\\
+hot.a	&	696	&	0.853	&	0.007	&	0.853	&	0.007	&	0.853	&	0.007\\
+arm.n	&	2137	&	0.841	&	0.027	&	0.841	&	0.027	&	0.841	&	0.027\\
+eat.v	&	1463	&	0.833	&	0.018	&	0.833	&	0.018	&	0.833	&	0.018\\
+add.v	&	2148	&	0.806	&	0.026	&	0.806	&	0.026	&	0.806	&	0.026\\
+plan.n	&	1353	&	0.797	&	0.016	&	0.835	&	0.017	&	0.835	&	0.017\\
+talk.v	&	1174	&	0.797	&	0.014	&	0.797	&	0.014	&	0.797	&	0.014\\
+use.v	&	214	&	0.786	&	0.003	&	0.786	&	0.003	&	0.786	&	0.003\\
+smell.v	&	874	&	0.784	&	0.01	&	0.804	&	0.01	&	0.804	&	0.01\\
+audience.n	&	1637	&	0.768	&	0.019	&	0.96	&	0.024	&	0.904	&	0.023\\
+expect.v	&	1275	&	0.756	&	0.015	&	0.756	&	0.015	&	0.756	&	0.015\\
+mean.v	&	646	&	0.737	&	0.007	&	0.737	&	0.007	&	0.737	&	0.007\\
+appear.v	&	2139	&	0.731	&	0.024	&	0.731	&	0.024	&	0.731	&	0.024\\
+express.v	&	887	&	0.731	&	0.01	&	0.769	&	0.01	&	0.769	&	0.01\\
+interest.n	&	1489	&	0.728	&	0.015	&	0.728	&	0.015	&	0.728	&	0.015\\
+sort.n	&	1566	&	0.728	&	0.017	&	0.88	&	0.021	&	0.853	&	0.02\\
+begin.v	&	1478	&	0.723	&	0.012	&	0.723	&	0.012	&	0.723	&	0.012\\
+note.v	&	1064	&	0.712	&	0.012	&	0.712	&	0.012	&	0.712	&	0.012\\
+receive.v	&	422	&	0.708	&	0.004	&	0.708	&	0.004	&	0.708	&	0.004\\
+decide.v	&	982	&	0.705	&	0.011	&	0.705	&	0.011	&	0.705	&	0.011\\
+wash.v	&	534	&	0.7	&	0.005	&	0.867	&	0.007	&	0.717	&	0.005\\
+climb.v	&	1073	&	0.698	&	0.011	&	0.698	&	0.011	&	0.698	&	0.011\\
+degree.n	&	2085	&	0.695	&	0.021	&	0.78	&	0.023	&	0.775	&	0.023\\
+bank.n	&	2113	&	0.684	&	0.02	&	0.744	&	0.022	&	0.718	&	0.021\\
+ask.v	&	2150	&	0.659	&	0.015	&	0.659	&	0.015	&	0.659	&	0.015\\
+rule.v	&	478	&	0.655	&	0.005	&	0.655	&	0.005	&	0.655	&	0.005\\
+activate.v	&	1874	&	0.65	&	0.017	&	0.65	&	0.017	&	0.65	&	0.017\\
+organization.n	&	905	&	0.648	&	0.009	&	0.778	&	0.011	&	0.75	&	0.01\\
+operate.v	&	286	&	0.643	&	0.002	&	0.714	&	0.003	&	0.714	&	0.003\\
+hear.v	&	510	&	0.633	&	0.005	&	0.7	&	0.005	&	0.7	&	0.005\\
+win.v	&	631	&	0.633	&	0.005	&	0.633	&	0.005	&	0.633	&	0.005\\
+shelter.n	&	1604	&	0.63	&	0.013	&	0.63	&	0.013	&	0.63	&	0.013\\
+party.n	&	1863	&	0.622	&	0.014	&	0.622	&	0.014	&	0.622	&	0.014\\
+source.n	&	527	&	0.607	&	0.004	&	0.607	&	0.004	&	0.607	&	0.004\\
+difference.n	&	1841	&	0.604	&	0.014	&	0.637	&	0.015	&	0.632	&	0.015\\
+write.v	&	355	&	0.579	&	0.003	&	0.579	&	0.003	&	0.579	&	0.003\\
+argument.n	&	1831	&	0.577	&	0.01	&	0.676	&	0.012	&	0.669	&	0.012\\
+atmosphere.n	&	1332	&	0.574	&	0.009	&	0.574	&	0.009	&	0.574	&	0.009\\
+paper.n	&	1914	&	0.574	&	0.009	&	0.721	&	0.011	&	0.689	&	0.011\\
+lose.v	&	574	&	0.552	&	0.004	&	0.552	&	0.004	&	0.552	&	0.004\\
+produce.v	&	1496	&	0.538	&	0.012	&	0.538	&	0.012	&	0.538	&	0.012\\
+encounter.v	&	1046	&	0.534	&	0.008	&	0.966	&	0.014	&	0.615	&	0.009\\
+image.n	&	1176	&	0.508	&	0.008	&	0.508	&	0.008	&	0.508	&	0.008\\
+disc.n	&	1633	&	0.488	&	0.005	&	0.488	&	0.005	&	0.488	&	0.005\\
+difficulty.n	&	378	&	0.474	&	0.002	&	0.842	&	0.004	&	0.719	&	0.003\\
+suspend.v	&	1032	&	0.456	&	0.007	&	0.456	&	0.007	&	0.456	&	0.007\\
+treat.v	&	903	&	0.442	&	0.005	&	0.465	&	0.005	&	0.465	&	0.005\\
+important.a	&	305	&	0.438	&	0.002	&	0.562	&	0.002	&	0.531	&	0.002\\
+miss.v	&	470	&	0.435	&	0.003	&	0.435	&	0.003	&	0.435	&	0.003\\
+judgment.n	&	502	&	0.429	&	0.003	&	0.429	&	0.003	&	0.429	&	0.003\\
+performance.n	&	1398	&	0.396	&	0.005	&	0.562	&	0.007	&	0.521	&	0.006\\
+play.v	&	838	&	0.389	&	0.004	&	0.389	&	0.004	&	0.389	&	0.004\\
+different.a	&	796	&	0.378	&	0.004	&	0.556	&	0.006	&	0.489	&	0.006\\
+solid.a	&	475	&	0.25	&	0.001	&	0.25	&	0.001	&	0.25	&	0.001\\
+simple.a	&	298	&	0.182	&	0.001	&	0.545	&	0.002	&	0.409	&	0.001\\
+
+\end{longtable}
 

### 2011-04-14 paper/paper.tex

--- 2011-04-14 paper/paper.tex
@@
 
-Looks through the training data and compiles a list of most common words for
-each item in the data. When the test data is run, the feature looks for the
-created vector and uses that instead of trying to make a new one. Next the
-extractor takes a window of words around the head word and generates the 0, 1
-tuple of features for inclusion to the dictionary. This word list is used as the
-keys of the feature vector when using the test data as a list of words that may
-cooccur with each item in the data. The value associated with each key in the
-feature vector starts out as 0 (for occurring 0 times in the window near a test
-word) If a key in the feature vector does occur with a word in the test data,
-the value associated with the key changes to 1 even if the key occurs more than
-once.  This is necessary because the machine learning algorithm we used does not
-attempt to analyze the keys beyond simple equality, so higher numbers than one
-could have masked the possibly more important distinction between 0 and not-0.
-In other words, keeping track of the instances of occurrence vs clustering them
-into 2 groups reduces the sparsity of the data and allows for a higher chance of
-accurate classifications based on the limited training data that we have. This
-is an especially important consideration since the feature vectors that select
-the most common words by looking through all the instances of unique lexical
+Looks through the training data and compiles a list of most common
+words for each item in the data in the form of a vector. When the test
+data is run, the feature looks for the previously made vector and uses that instead of
+trying to make a new one. Next the extractor takes a window of words
+around the head word and generates the 0, 1 tuple of features for
+inclusion to the dictionary. This list constitues the features in the
+feature vector rather than the list of common words. The value
+associated with each key in the feature vector starts out as 0 (for
+occurring 0 times in the window near a test word) If a key in the
+feature vector does occur with a word in the test data, the value
+associated with the key changes to 1 even if the key occurs more than
+once.  This is necessary because the machine learning algorithm we
+used does not attempt to analyze the keys beyond simple equality, so
+higher numbers than one could have masked the possibly more important
+distinction between 0 and not-0. In other words, keeping track of the
+instances of occurrence vs clustering them into 2 groups reduces the
+sparsity of the data and allows for a higher chance of accurate classifications
+based on the limited training data that we have. This is an especially
+important consideration since the feature vectors that select the most
+common words by looking through all the instances of unique lexical
 items in the training data are unsupervised.
@@
 
+\end{description}
+
 \end{document}

### 2011-04-14 paper/paper.tex

--- 2011-04-14 paper/paper.tex
@@
 \usepackage{longtable}
-\usepackage{graphicx}
 \title{Word Sense Disambiguation\\
@@
 
-\includegraphics{pg_0001}
 %stepwise graph 1
@@
 
-\includegraphics{pg_0002}
+%stepwise graph 2
 
@@
 
-\includegraphics{pg_0003}
+%stepwise graph 33
 
-\includegraphics{pg_0004}
+\subsection{Characterization of the top feature combinations}
+
+%Let's get a comparison between our best performer(s) and the baseline
 

### 2011-04-14 paper/paper.tex

@@
 
-Looks through the training data and compiles a list of most common
-words for each item in the data in the form of a vector. When the test
-data is run, the feature looks for the previously made vector and uses that instead of
-trying to make a new one. Next the extractor takes a window of words
-around the head word and generates the 0, 1 tuple of features for
-inclusion to the dictionary. This list constitues the features in the
-feature vector rather than the list of common words. The value
-associated with each key in the feature vector starts out as 0 (for
-occurring 0 times in the window near a test word) If a key in the
-feature vector does occur with a word in the test data, the value
-associated with the key changes to 1 even if the key occurs more than
-once.  This is necessary because the machine learning algorithm we
-used does not attempt to analyze the keys beyond simple equality, so
-higher numbers than one could have masked the possibly more important
-distinction between 0 and not-0. In other words, keeping track of the
-instances of occurrence vs clustering them into 2 groups reduces the
-sparsity of the data and allows for a higher chance of accurate classifications
-based on the limited training data that we have. This is an especially
-important consideration since the feature vectors that select the most
-common words by looking through all the instances of unique lexical
+Looks through the training data and compiles a list of most common words for
+each item in the data. When the test data is run, the feature looks for the
+created vector and uses that instead of trying to make a new one. Next the
+extractor takes a window of words around the head word and generates the 0, 1
+tuple of features for inclusion to the dictionary. This word list is used as the
+keys of the feature vector when using the test data as a list of words that may
+cooccur with each item in the data. The value associated with each key in the
+feature vector starts out as 0 (for occurring 0 times in the window near a test
+word) If a key in the feature vector does occur with a word in the test data,
+the value associated with the key changes to 1 even if the key occurs more than
+once.  This is necessary because the machine learning algorithm we used does not
+attempt to analyze the keys beyond simple equality, so higher numbers than one
+could have masked the possibly more important distinction between 0 and not-0.
+In other words, keeping track of the instances of occurrence vs clustering them
+into 2 groups reduces the sparsity of the data and allows for a higher chance of
+accurate classifications based on the limited training data that we have. This
+is an especially important consideration since the feature vectors that select
+the most common words by looking through all the instances of unique lexical
 items in the training data are unsupervised.
@@
 
-\end{description}
-
 \end{document}

### 2011-04-14 paper/paper.tex

@@
 \usepackage{longtable}
+\usepackage{graphicx}
 \title{Word Sense Disambiguation\\
@@
 We  chose to implement our system in Python, and chose to use the machine
-learning algorithms in the NLTK toolkit which is also Python-based.
+learning algorithms in NLTK which is also Python-based.
+We also used NLTK for its part of speech tagger, dependecy parser, and to import the Senseval data.
+We coded the rest of the assignment on our own.
 
 We wrote our main control program, classify.py, so that it can choose either
-[we're just doing nb and decision trees now right?] classifier and any
+Naive Bayes or Decision Trees classifier and any 
 combination of  features. On top of this we wrote bash scripts that automated
@@
 
-\section{Looking through Different Corpora}
+\subsection{Looking through Different Corpora}
 
@@
 
+\includegraphics[width=\textwidth]{pg_0001}
 %stepwise graph 1
@@
 
-%stepwise graph 2
+\includegraphics[width=\textwidth]{pg_0002}
 
@@
 
-%stepwise graph 33
+\includegraphics[width=\textwidth]{pg_0003}
 
-\subsection{Characterization of the top feature combinations}
-
-%Let's get a comparison between our best performer(s) and the baseline
+\includegraphics[width=\textwidth]{pg_0004}
 

### 2011-04-14 paper/paper.tex
fixed minor stuff

@@
 \usepackage{url}
-\usepackage{longtable}
-\usepackage{graphicx}
 \title{Word Sense Disambiguation\\
@@
 
-\subsection{Stepwise regression}
+\subsubsection{Stepwise regression}
 
@@
 
-\subsection{Graphical methods}
+\subsubsection{Graphical methods}
 We began by plotting the predictors that seemed most influential in the
@@
 
-\includegraphics[width=\textwidth]{pg_0001}
 %stepwise graph 1
@@
 
-\includegraphics[width=\textwidth]{pg_0002}
+%stepwise graph 2
 
-more discussin of graphs
+more discussion of graphs
 
-\includegraphics[width=\textwidth]{pg_0003}
+%stepwise graph 33
 
-\includegraphics[width=\textwidth]{pg_0004}
+\subsection{Characterization of the top feature combinations}
 
-\subsection{Best Run Results}
-
-\begin{longtable}{l | r r r r r r r}
-		&	&	\multicolumn{2}{c}{Fine Grain}	&	\multicolumn{2}{c}{Course Grain}	&	\multicolumn{2}{c}{Mixed}\\
-Word	&	Corpus Size	&	Precision	&	Recall	&	Precision	&	Recall	&	Precision	&	Recall\\
-\hline
-provide.v	&	1094	&	0.906	&	0.015	&	0.938	&	0.015	&	0.922	&	0.015\\
-watch.v	&	806	&	0.878	&	0.011	&	0.918	&	0.011	&	0.918	&	0.011\\
-remain.v	&	1118	&	0.871	&	0.015	&	0.871	&	0.015	&	0.871	&	0.015\\
-hot.a	&	696	&	0.853	&	0.007	&	0.853	&	0.007	&	0.853	&	0.007\\
-arm.n	&	2137	&	0.841	&	0.027	&	0.841	&	0.027	&	0.841	&	0.027\\
-eat.v	&	1463	&	0.833	&	0.018	&	0.833	&	0.018	&	0.833	&	0.018\\
-add.v	&	2148	&	0.806	&	0.026	&	0.806	&	0.026	&	0.806	&	0.026\\
-plan.n	&	1353	&	0.797	&	0.016	&	0.835	&	0.017	&	0.835	&	0.017\\
-talk.v	&	1174	&	0.797	&	0.014	&	0.797	&	0.014	&	0.797	&	0.014\\
-use.v	&	214	&	0.786	&	0.003	&	0.786	&	0.003	&	0.786	&	0.003\\
-smell.v	&	874	&	0.784	&	0.01	&	0.804	&	0.01	&	0.804	&	0.01\\
-audience.n	&	1637	&	0.768	&	0.019	&	0.96	&	0.024	&	0.904	&	0.023\\
-expect.v	&	1275	&	0.756	&	0.015	&	0.756	&	0.015	&	0.756	&	0.015\\
-mean.v	&	646	&	0.737	&	0.007	&	0.737	&	0.007	&	0.737	&	0.007\\
-appear.v	&	2139	&	0.731	&	0.024	&	0.731	&	0.024	&	0.731	&	0.024\\
-express.v	&	887	&	0.731	&	0.01	&	0.769	&	0.01	&	0.769	&	0.01\\
-interest.n	&	1489	&	0.728	&	0.015	&	0.728	&	0.015	&	0.728	&	0.015\\
-sort.n	&	1566	&	0.728	&	0.017	&	0.88	&	0.021	&	0.853	&	0.02\\
-begin.v	&	1478	&	0.723	&	0.012	&	0.723	&	0.012	&	0.723	&	0.012\\
-note.v	&	1064	&	0.712	&	0.012	&	0.712	&	0.012	&	0.712	&	0.012\\
-receive.v	&	422	&	0.708	&	0.004	&	0.708	&	0.004	&	0.708	&	0.004\\
-decide.v	&	982	&	0.705	&	0.011	&	0.705	&	0.011	&	0.705	&	0.011\\
-wash.v	&	534	&	0.7	&	0.005	&	0.867	&	0.007	&	0.717	&	0.005\\
-climb.v	&	1073	&	0.698	&	0.011	&	0.698	&	0.011	&	0.698	&	0.011\\
-degree.n	&	2085	&	0.695	&	0.021	&	0.78	&	0.023	&	0.775	&	0.023\\
-bank.n	&	2113	&	0.684	&	0.02	&	0.744	&	0.022	&	0.718	&	0.021\\
-ask.v	&	2150	&	0.659	&	0.015	&	0.659	&	0.015	&	0.659	&	0.015\\
-rule.v	&	478	&	0.655	&	0.005	&	0.655	&	0.005	&	0.655	&	0.005\\
-activate.v	&	1874	&	0.65	&	0.017	&	0.65	&	0.017	&	0.65	&	0.017\\
-organization.n	&	905	&	0.648	&	0.009	&	0.778	&	0.011	&	0.75	&	0.01\\
-operate.v	&	286	&	0.643	&	0.002	&	0.714	&	0.003	&	0.714	&	0.003\\
-hear.v	&	510	&	0.633	&	0.005	&	0.7	&	0.005	&	0.7	&	0.005\\
-win.v	&	631	&	0.633	&	0.005	&	0.633	&	0.005	&	0.633	&	0.005\\
-shelter.n	&	1604	&	0.63	&	0.013	&	0.63	&	0.013	&	0.63	&	0.013\\
-party.n	&	1863	&	0.622	&	0.014	&	0.622	&	0.014	&	0.622	&	0.014\\
-source.n	&	527	&	0.607	&	0.004	&	0.607	&	0.004	&	0.607	&	0.004\\
-difference.n	&	1841	&	0.604	&	0.014	&	0.637	&	0.015	&	0.632	&	0.015\\
-write.v	&	355	&	0.579	&	0.003	&	0.579	&	0.003	&	0.579	&	0.003\\
-argument.n	&	1831	&	0.577	&	0.01	&	0.676	&	0.012	&	0.669	&	0.012\\
-atmosphere.n	&	1332	&	0.574	&	0.009	&	0.574	&	0.009	&	0.574	&	0.009\\
-paper.n	&	1914	&	0.574	&	0.009	&	0.721	&	0.011	&	0.689	&	0.011\\
-lose.v	&	574	&	0.552	&	0.004	&	0.552	&	0.004	&	0.552	&	0.004\\
-produce.v	&	1496	&	0.538	&	0.012	&	0.538	&	0.012	&	0.538	&	0.012\\
-encounter.v	&	1046	&	0.534	&	0.008	&	0.966	&	0.014	&	0.615	&	0.009\\
-image.n	&	1176	&	0.508	&	0.008	&	0.508	&	0.008	&	0.508	&	0.008\\
-disc.n	&	1633	&	0.488	&	0.005	&	0.488	&	0.005	&	0.488	&	0.005\\
-difficulty.n	&	378	&	0.474	&	0.002	&	0.842	&	0.004	&	0.719	&	0.003\\
-suspend.v	&	1032	&	0.456	&	0.007	&	0.456	&	0.007	&	0.456	&	0.007\\
-treat.v	&	903	&	0.442	&	0.005	&	0.465	&	0.005	&	0.465	&	0.005\\
-important.a	&	305	&	0.438	&	0.002	&	0.562	&	0.002	&	0.531	&	0.002\\
-miss.v	&	470	&	0.435	&	0.003	&	0.435	&	0.003	&	0.435	&	0.003\\
-judgment.n	&	502	&	0.429	&	0.003	&	0.429	&	0.003	&	0.429	&	0.003\\
-performance.n	&	1398	&	0.396	&	0.005	&	0.562	&	0.007	&	0.521	&	0.006\\
-play.v	&	838	&	0.389	&	0.004	&	0.389	&	0.004	&	0.389	&	0.004\\
-different.a	&	796	&	0.378	&	0.004	&	0.556	&	0.006	&	0.489	&	0.006\\
-solid.a	&	475	&	0.25	&	0.001	&	0.25	&	0.001	&	0.25	&	0.001\\
-simple.a	&	298	&	0.182	&	0.001	&	0.545	&	0.002	&	0.409	&	0.001\\
-
-\end{longtable}
+%Let's get a comparison between our best performer(s) and the baseline
 

### 2011-04-14 paper/paper.tex
fixed minor stuff
baseline data in
minor changes

--- 2011-04-14 paper/paper.tex
@@
 We wrote our main control program, classify.py, so that it can choose either
-[we're just doing nb and decision trees now right?] classifier and any
-combination of  features. On top of this we wrote bash scripts that automated
+the Naive Bayes classifier or the Decision Tree classifier and any combination of
+features. On top of this we wrote bash scripts that automated
 looping through every combination of classifiers and features, along with
@@
 
-The NLTK was used to implement two machine learning algorithms, naive Bayes and
+The NLTK was used to implement two machine learning algorithms, Naive Bayes and
 decision trees.
@@
 
-The NLTK implements a naï bayes classifier which chooses the best sense given a
+The NLTK implements a Naive Bayes classifier which chooses the best sense given a
 dictionary of features and assigns confidence probabilities to the chosen
-sense. Naive bayes does assume an independence of features. The probability of
+sense. Naive Bayes does assume an independence of features. The probability of
 each feature contributes to the overall choice.
@@
 
-%The negative interaction terms may indicate that the interacting features provide
-similar functionality and blah blah blah
+%The negative interaction terms may indicate that the interacting
+features provide similar functionality and blah blah blah
 

### 2011-04-14 paper/paper.tex

--- 2011-04-14 paper/paper.tex
@@
 
-\subsection{Looking through Different Corpora}
-
-In order to get more data to use with the bootstrapping algorithm, we attempted
-to search through the Brown corpus and return all of the words that were being
-disambiguated in the Senseval 3 task.  To do this we needed to find all of the
-instances of the words that we needed to disambiguate and return a context
-(list of words) and the position of the word in that list.  We also made sure
-that the context that we returned both started at the beginning of the
-sentence and ended at the end of a sentence and had a minimum of 25 words
-returned on either side of the word.  This data would then be converted into
-the form of the data that we received from the Senseval document and ran
-through the bootstrapping algorithm to have more data to train with.  However
-when we actually tested this feature alone we found it to be very
-uninformative.  First, there were very few instances of the words that we were
-looking for (ex: activate only appeared 3 times), which made searching through
-the entire corpus to find these words more time consuming than it was helpful.
-Therefore, we decided not to use it for the actual test because it was not
-informative enough by itself.
-
 \subsection{Base Word}
@@
 %\subsubsection{Bootstrapping on the Brown Corpus}
+
+\subsection{Looking through Different Corpora}
+
+In order to get more data to use with the bootstrapping algorithm, we attempted
+to search through the Brown corpus and return all of the words that were being
+disambiguated in the Senseval 3 task.  To do this we needed to find all of the
+instances of the words that we needed to disambiguate and return a context
+(list of words) and the position of the word in that list.  We also made sure
+that the context that we returned both started at the beginning of the
+sentence and ended at the end of a sentence and had a minimum of 25 words
+returned on either side of the word.  This data would then be converted into
+the form of the data that we received from the Senseval document and ran
+through the bootstrapping algorithm to have more data to train with.  However
+when we actually tested this feature alone we found it to be very
+uninformative.  First, there were very few instances of the words that we were
+looking for (ex: activate only appeared 3 times), which made searching through
+the entire corpus to find these words more time consuming than it was helpful.
+Therefore, we decided not to use it for the actual test because it was not
+informative enough by itself.
+
 %The instances of the target words in the Brown corpus were very few, e.g., activate appeared only 3 times, and bootstrapping didn't seem to be very accurate in general.

### 2011-04-14 paper/paper.tex
more paper edits

@@
 \usepackage{graphicx}
+\usepackage{multirow}
 \title{Word Sense Disambiguation\\
@@
 
-more discussin of graphs
+The naive Bayes classifier had better top-range performance.
 
@@
 
+\subsection{Baseline Results}
+
+We ran two baselines, one with each machine learning algorithm:
+
+\begin{tabular}{l l | r r r}
+& grain& precision& recall& attempted\\
+\hline
+\multirow{3}{*}{Naive Bayes} &
+coarse  &  0.737 & 0.379 &   51.39\\
+&mixed  &  0.730 & 0.375 &   51.39\\
+& fine  &  0.693 & 0.356 &   51.39\\
+\multirow{3}{*}{Decision Tree} &
+coarse  &  0.612 & 0.612 &  100.00\\
+&mixed  &  0.594 & 0.594 &  100.00\\
+& fine  &  0.552 & 0.552 &  100.00\\
+\end{tabular}
+
 \subsection{Best Run Results}
+
+Our run with the highest overall F-measure (overall precision 0.718, overall
+recall 0.610), used cooccurrence, colocation out to a distance of 2, base word,
+no dependency parsing, and bootstrapped once:
 

### 2011-04-14 paper/paper.tex

--- 2011-04-14 paper/paper.tex
@@
 We wrote our main control program, classify.py, so that it can choose either
-Naive Bayes or Decision Trees classifier and any 
+[we're just doing nb and decision trees now right?] classifier and any
 combination of  features. On top of this we wrote bash scripts that automated
@@
 
+\section{Looking through Different Corpora}
+
+In order to get more data to use with the bootstrapping algorithm, we attempted
+to search through the Brown corpus and return all of the words that were being
+disambiguated in the Senseval 3 task.  To do this we needed to find all of the
+instances of the words that we needed to disambiguate and return a context
+(list of words) and the position of the word in that list.  We also made sure
+that the context that we returned both started at the beginning of the
+sentence and ended at the end of a sentence and had a minimum of 25 words
+returned on either side of the word.  This data would then be converted into
+the form of the data that we received from the Senseval document and ran
+through the bootstrapping algorithm to have more data to train with.  However
+when we actually tested this feature alone we found it to be very
+uninformative.  First, there were very few instances of the words that we were
+looking for (ex: activate only appeared 3 times), which made searching through
+the entire corpus to find these words more time consuming than it was helpful.
+Therefore, we decided not to use it for the actual test because it was not
+informative enough by itself.
+
 \subsection{Base Word}
@@
 %\subsubsection{Bootstrapping on the Brown Corpus} 
-
-\subsection{Looking through Different Corpora}
-
-In order to get more data to use with the bootstrapping algorithm, we attempted
-to search through the Brown corpus and return all of the words that were being
-disambiguated in the Senseval 3 task.  To do this we needed to find all of the
-instances of the words that we needed to disambiguate and return a context
-(list of words) and the position of the word in that list.  We also made sure
-that the context that we returned both started at the beginning of the
-sentence and ended at the end of a sentence and had a minimum of 25 words
-returned on either side of the word.  This data would then be converted into
-the form of the data that we received from the Senseval document and ran
-through the bootstrapping algorithm to have more data to train with.  However
-when we actually tested this feature alone we found it to be very
-uninformative.  First, there were very few instances of the words that we were
-looking for (ex: activate only appeared 3 times), which made searching through
-the entire corpus to find these words more time consuming than it was helpful.
-Therefore, we decided not to use it for the actual test because it was not
-informative enough by itself.
-
 %The instances of the target words in the Brown corpus were very few, e.g., activate appeared only 3 times, and bootstrapping didn't seem to be very accurate in general.

### 2011-04-14 paper/paper.tex

--- 2011-04-14 paper/paper.tex
@@
 
+\newcommand{\naive}{na\"ive}
+\newcommand{\Naive}{Na\"ive}
+
 \begin{document}
@@
 We  chose to implement our system in Python, and chose to use the machine
-learning algorithms in NLTK which is also Python-based.
-We also used NLTK for its part of speech tagger, dependecy parser, and to import the Senseval data.
+learning algorithms in NLTK which is also Python-based.  We also used NLTK for
+its part of speech tagger, dependency parser, and to import the Senseval data.
 We coded the rest of the assignment on our own.
@@
 
-We used a \ward stepwise approach to indentifying optimal feature combinations.
+We used a \ward stepwise approach to identifying optimal feature combinations.
 We first ran the system with all features on, producing a total of $256=2^8$
@@
 
-The NLTK was used to implement two machine learning algorithms, naive Bayes and
+The NLTK was used to implement two machine learning algorithms, \naive{} Bayes and
 decision trees.
@@
 
-The NLTK implements a naïve bayes classifier which chooses the best sense given a
+The NLTK implements a \naive{} Bayes classifier which chooses the best sense given a
 dictionary of features and assigns confidence probabilities to the chosen
-sense. Naive bayes does assume an independence of features. The probability of
+sense. \Naive{} Bayes does assume an independence of features. The probability of
 each feature contributes to the overall choice.
@@
 NLTK provides probability measures for each of its guesses when using the
-maximum entropy and the naive Bayes learning methods.  We harnessed these to
-determine the cutoff for making a guess, or resorting to a ``U'' if we were
-unconfident in the tagging.  Occasional unknowns also occur because such
-unknowns are present in the training data, and we made no effort to remove
-them, so the learning algorithm views them as any other label.
+maximum entropy and the \naive{} Bayes learning methods.  We harnessed these to
+determine the cutoff for making a guess, or resorting to a ``U'' if we were not
+confident in the tagging.  Occasional unknowns also occur because such unknowns
+are present in the training data, and we made no effort to remove them, so the
+learning algorithm views them as any other label.
 
@@
 
-We also used nltk's part of speech tagger to tag the context, and included those
-as we did the literal words in the feature set.  This was trained on nltk's
-\verb+maximum entropy treebank pos tagger+ data, which is included with the nltk
+We also used NLTK's part of speech tagger to tag the context, and included those
+as we did the literal words in the feature set.  This was trained on NLTK's
+\verb+maximum entropy treebank pos tagger+ data, which is included with the NLTK
 package.
 
-\subsection{Cooccurrence}
+\subsection{Co-occurrence}
 
@@
 keys of the feature vector when using the test data as a list of words that may
-cooccur with each item in the data. The value associated with each key in the
+co-occur with each item in the data. The value associated with each key in the
 feature vector starts out as 0 (for occurring 0 times in the window near a test
@@
 \begin{itemize}
-\item Classifier (naive Bayes or decision list)
+\item Classifier (\naive{} Bayes or decision list)
 \item Collocation window length (0--8)
-\item Cooccurrence handling (on or off)
+\item Co-occurrence handling (on or off)
 \item Base word handling (on or off)
@@
 
-The predictor combination yeilding the lowest value of the Akaike information criterion
+The predictor combination yielding the lowest value of the Akaike information criterion
 included the following parameters.
@@
 \item Collocation window size
-\item Coocurrence
+\item Co-occurrence
 \item Base word handling
 \item Classifier$\times$collocation window size interaction
-\item Classifier$\times$cooccurrence interaction
+\item Classifier$\times$co-occurrence interaction
 \end{itemize}
@@
 
-The naive Bayes classifier had better top-range performance.
+The \naive{} Bayes classifier had better top-range performance.
 
@@
 Our run with the highest overall F-measure (overall precision 0.718, overall
-recall 0.610), used cooccurrence, colocation out to a distance of 2, base word,
+recall 0.610), used co-occurrence, collocation out to a distance of 2, base word,
 no dependency parsing, and bootstrapped once:
@@
 An idea for a feature extractor was to take the most common words in a context
-of a lexeme and use those words as features. Based off of the cooccurrence code,
+of a lexeme and use those words as features. Based off of the co-occurrence code,
 this would generate a vector from the training data, find the most common words
@@
 precision and recall for this feature extractor alone on the EnglishLS test data
-were 0.039. This is to be expected since it is essentially the cooccurrence
+were 0.039. This is to be expected since it is essentially the co-occurrence
 feature extractor but without grouping data into buckets. The sparsity problem
@@
 
-Collocation seemed to be a fairly powerful disambugator, which is to be
+Collocation seemed to be fairly powerful at disambiguating, which is to be
 expected, since function words near to the target word can be very strong

### 2011-04-14 paper/paper.tex
conclusion

@@
 
+\section{Conclusion}
+
+The \naive Bayes and decision tree classifiers are not smart enough to sort out
+a large number of features when the data sets are of small or moderate size,
+which requires judicious choosing of features.  Co-occurrence, base word and
+collocation with part of speech collocation seem to be more powerful features
+than dependency parsing, and bootstrapping on the data in an attempt to get a
+larger training base was ineffective because precision was too low.
+
 \end{document}

### 2011-04-14 paper/paper.tex
fix
fixed a few naiveties

@@
 We wrote our main control program, classify.py, so that it can choose either
-Naive Bayes or Decision Trees classifier and any 
+\Naive{} Bayes or Decision Trees classifier and any 
 combination of  features. On top of this we wrote bash scripts that automated
@@
 
-\subsubsection{Naive Bayes}
+\subsubsection{\Naive{} Bayes}
 
@@
 
-Naive Bayes supported probability estimation, while the decision tree did not.
+\Naive{} Bayes supported probability estimation, while the decision tree did not.
 
@@
 
+\begin{figure}
+\includegraphics[width=\textwidth]{baseline}
+\caption{\label{fig:base}Baseline scores for our two baseline systems}
+\end{figure}
+
+\begin{figure}
 \includegraphics[width=\textwidth]{pg_0001}
+\caption{\label{fig1}}
+\end{figure}
+
+Collocation window of size 2--4 had the best performance (figure \ref{fig2}), so we looked more closely at those.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{pg_0002}
 %stepwise graph 1
@@
 %Interpret this graph
-
-Collocation window of size 2--4 had the best performance, so we looked more closely at those.
-
-\includegraphics[width=\textwidth]{pg_0002}
+\caption{\label{fig2}}
+\end{figure}
 
@@
 
+\begin{figure}
 \includegraphics[width=\textwidth]{pg_0003}
+\caption{\label{fig3}}
+\end{figure}
 
+\begin{figure}
 \includegraphics[width=\textwidth]{pg_0004}
+\caption{\label{fig4}}
+\end{figure}
 
@@
 \hline
-\multirow{3}{*}{Naive Bayes} &
+\multirow{3}{*}{\Naive{} Bayes} &
 coarse  &  0.737 & 0.379 &   51.39\\
@@
 
-\subsection{Looking through Different Corpora}
+\subsubsection{Looking through Different Corpora}
 
@@
 
-The \naive Bayes and decision tree classifiers are not smart enough to sort out
+The \naive{} Bayes and decision tree classifiers are not smart enough to sort out
 a large number of features when the data sets are of small or moderate size,

### 2011-04-14 paper/paper.tex
fixing conflicts

--- 2011-04-14 paper/paper.tex
@@
 \usepackage{graphicx}
-\usepackage{multirow}
 \title{Word Sense Disambiguation\\
@@
 
-\newcommand{\naive}{na\"ive}
-\newcommand{\Naive}{Na\"ive}
-
 \begin{document}
@@
 We  chose to implement our system in Python, and chose to use the machine
-learning algorithms in NLTK which is also Python-based.  We also used NLTK for
-its part of speech tagger, dependency parser, and to import the Senseval data.
-We coded the rest of the assignment on our own.
+learning algorithms in NLTK which is also Python-based.  We also used
+NLTK for its part of speech tagger, dependecy parser, and to import
+the Senseval data. We coded the rest of the assignment on our own.
 
 We wrote our main control program, classify.py, so that it can choose either
-Naive Bayes or Decision Trees classifier and any 
-combination of  features. On top of this we wrote bash scripts that automated
+Naive Bayes or Decision Trees classifier and any combination of
+features. On top of this we wrote bash scripts that automated 
 looping through every combination of classifiers and features, along with
@@
 \subsection{Selecting optimal feature combination}
-\newcommand\ward{forward} %or maybe backwards
+\newcommand\ward{backward} %or maybe backwards
 
-We used a \ward stepwise approach to identifying optimal feature combinations.
+We used a \ward stepwise approach to indentifying optimal feature combinations.
 We first ran the system with all features on, producing a total of $256=2^8$
@@
 
-The NLTK was used to implement two machine learning algorithms, \naive{} Bayes and
+The NLTK was used to implement two machine learning algorithms, Naive Bayes and
 decision trees.
@@
 
-The NLTK implements a \naive{} Bayes classifier which chooses the best sense given a
+The NLTK implements a naïve bayes classifier which chooses the best sense given a
 dictionary of features and assigns confidence probabilities to the chosen
-sense. \Naive{} Bayes does assume an independence of features. The probability of
+sense. Naive Bayes does assume an independence of features. The probability of
 each feature contributes to the overall choice.
@@
 NLTK provides probability measures for each of its guesses when using the
-maximum entropy and the \naive{} Bayes learning methods.  We harnessed these to
-determine the cutoff for making a guess, or resorting to a ``U'' if we were not
-confident in the tagging.  Occasional unknowns also occur because such unknowns
-are present in the training data, and we made no effort to remove them, so the
-learning algorithm views them as any other label.
+maximum entropy and the naive Bayes learning methods.  We harnessed these to
+determine the cutoff for making a guess, or resorting to a ``U'' if we were
+unconfident in the tagging.  Occasional unknowns also occur because such
+unknowns are present in the training data, and we made no effort to remove
+them, so the learning algorithm views them as any other label.
 
@@
 % many iterations?
+
+\subsection{Looking through Different Corpora}
+
+In order to get more data to use with the bootstrapping algorithm, we attempted
+to search through the Brown corpus and return all of the words that were being
+disambiguated in the Senseval 3 task.  To do this we needed to find all of the
+instances of the words that we needed to disambiguate and return a context
+(list of words) and the position of the word in that list.  We also made sure
+that the context that we returned both started at the beginning of the
+sentence and ended at the end of a sentence and had a minimum of 25 words
+returned on either side of the word.  This data would then be converted into
+the form of the data that we received from the Senseval document and ran
+through the bootstrapping algorithm to have more data to train with.  However
+when we actually tested this feature alone we found it to be very
+uninformative.  First, there were very few instances of the words that we were
+looking for (ex: activate only appeared 3 times), which made searching through
+the entire corpus to find these words more time consuming than it was helpful.
+Therefore, we decided not to use it for the actual test because it was not
+informative enough by itself.
 
@@
 
-We also used NLTK's part of speech tagger to tag the context, and included those
-as we did the literal words in the feature set.  This was trained on NLTK's
-\verb+maximum entropy treebank pos tagger+ data, which is included with the NLTK
+We also used nltk's part of speech tagger to tag the context, and included those
+as we did the literal words in the feature set.  This was trained on nltk's
+\verb+maximum entropy treebank pos tagger+ data, which is included with the nltk
 package.
 
-\subsection{Co-occurrence}
+\subsection{Cooccurrence}
 
-Looks through the training data and compiles a list of most common words for
-each item in the data. When the test data is run, the feature looks for the
-created vector and uses that instead of trying to make a new one. Next the
-extractor takes a window of words around the head word and generates the 0, 1
-tuple of features for inclusion to the dictionary. This word list is used as the
-keys of the feature vector when using the test data as a list of words that may
-co-occur with each item in the data. The value associated with each key in the
-feature vector starts out as 0 (for occurring 0 times in the window near a test
-word) If a key in the feature vector does occur with a word in the test data,
-the value associated with the key changes to 1 even if the key occurs more than
-once.  This is necessary because the machine learning algorithm we used does not
-attempt to analyze the keys beyond simple equality, so higher numbers than one
-could have masked the possibly more important distinction between 0 and not-0.
-In other words, keeping track of the instances of occurrence vs clustering them
-into 2 groups reduces the sparsity of the data and allows for a higher chance of
-accurate classifications based on the limited training data that we have. This
-is an especially important consideration since the feature vectors that select
-the most common words by looking through all the instances of unique lexical
+Looks through the training data and compiles a list of most common
+words for each item in the data in the form of a vector. When the test
+data is run, the feature looks for the previously made vector and uses that instead of
+trying to make a new one. Next the extractor takes a window of words
+around the head word and generates the 0, 1 tuple of features for
+inclusion to the dictionary. This list constitues the features in the
+feature vector rather than the list of common words. The value
+associated with each key in the feature vector starts out as 0 (for
+occurring 0 times in the window near a test word) If a key in the
+feature vector does occur with a word in the test data, the value
+associated with the key changes to 1 even if the key occurs more than
+once.  This is necessary because the machine learning algorithm we
+used does not attempt to analyze the keys beyond simple equality, so
+higher numbers than one could have masked the possibly more important
+distinction between 0 and not-0. In other words, keeping track of the
+instances of occurrence vs clustering them into 2 groups reduces the
+sparsity of the data and allows for a higher chance of accurate classifications
+based on the limited training data that we have. This is an especially
+important consideration since the feature vectors that select the most
+common words by looking through all the instances of unique lexical
 items in the training data are unsupervised.
@@
 \begin{itemize}
-\item Classifier (\naive{} Bayes or decision list)
+\item Classifier (naive Bayes or decision list)
 \item Collocation window length (0--8)
-\item Co-occurrence handling (on or off)
+\item Cooccurrence handling (on or off)
 \item Base word handling (on or off)
@@
 
-The predictor combination yielding the lowest value of the Akaike information criterion
+The predictor combination yeilding the lowest value of the Akaike information criterion
 included the following parameters.
@@
 \item Collocation window size
-\item Co-occurrence
+\item Coocurrence
 \item Base word handling
 \item Classifier$\times$collocation window size interaction
-\item Classifier$\times$co-occurrence interaction
+\item Classifier$\times$cooccurrence interaction
 \end{itemize}
@@
 
-%The negative interaction terms may indicate that the interacting features provide
-similar functionality and blah blah blah
+As the regression table above shows, it seems that substituting the
+Decision Tree classifier for the Naive Bayes baseline provides the
+most significant boost to our f measure. It can also be seen here that
+increasing the collocation window will increase the f measure by about 0.003
+for each additional word added to the window. Additionally, enabling
+the cooccurrence feature extractor with the Naive Bayes classifier
+will increase the f measure by a significant amount as well.
+
+The rows that contain negative terms may indicate that the interacting
+features provide similar functionality. That is, the enabled features
+are interfering with each other so that their final influence on the f
+measure may affect the f measure negatively. For instance, the row
+showing ``classifiert:collocation'' indicates a run where the Decision
+Tree classifier was used and the collocation feature was enabled has
+resulted in a lower accuracy. This seems to be the general trend for
+all of the interacting features. It may be interesting to note that
+the interaction between collocation and cooccurrence1 as well as
+collocation and dependency parsing produce the most innocuous
+cumulative effect. Perhaps this may be why collocation and
+cooccurrence are often advocated to be used together.
 
@@
 
-The \naive{} Bayes classifier had better top-range performance.
+more discussin of graphs
 
@@
 
-\subsection{Baseline Results}
-
-We ran two baselines, one with each machine learning algorithm:
-
-\begin{tabular}{l l | r r r}
-& grain& precision& recall& attempted\\
-\hline
-\multirow{3}{*}{Naive Bayes} &
-coarse  &  0.737 & 0.379 &   51.39\\
-&mixed  &  0.730 & 0.375 &   51.39\\
-& fine  &  0.693 & 0.356 &   51.39\\
-\multirow{3}{*}{Decision Tree} &
-coarse  &  0.612 & 0.612 &  100.00\\
-&mixed  &  0.594 & 0.594 &  100.00\\
-& fine  &  0.552 & 0.552 &  100.00\\
-\end{tabular}
-
 \subsection{Best Run Results}
-
-Our run with the highest overall F-measure (overall precision 0.718, overall
-recall 0.610), used co-occurrence, collocation out to a distance of 2, base word,
-no dependency parsing, and bootstrapped once:
 
@@
 An idea for a feature extractor was to take the most common words in a context
-of a lexeme and use those words as features. Based off of the co-occurrence code,
+of a lexeme and use those words as features. Based off of the cooccurrence code,
 this would generate a vector from the training data, find the most common words
@@
 precision and recall for this feature extractor alone on the EnglishLS test data
-were 0.039. This is to be expected since it is essentially the co-occurrence
+were 0.039. This is to be expected since it is essentially the cooccurrence
 feature extractor but without grouping data into buckets. The sparsity problem
@@
 
-Collocation seemed to be fairly powerful at disambiguating, which is to be
+Collocation seemed to be a fairly powerful disambugator, which is to be
 expected, since function words near to the target word can be very strong

### 2011-04-14 paper/paper.tex

--- 2011-04-14 paper/paper.tex
@@
 We wrote our main control program, classify.py, so that it can choose either
-Naive Bayes or Decision Trees classifier and any 
-combination of  features. On top of this we wrote bash scripts that automated
+Naive Bayes or Decision Trees classifier and any combination of
+features. On top of this we wrote bash scripts that automated 
 looping through every combination of classifiers and features, along with
@@
 \subsection{Selecting optimal feature combination}
-\newcommand\ward{forward} %or maybe backwards
+\newcommand\ward{backward} %or maybe backwards
 
@@
 
-\section{Conclusion}
-
-The \naive Bayes and decision tree classifiers are not smart enough to sort out
-a large number of features when the data sets are of small or moderate size,
-which requires judicious choosing of features.  Co-occurrence, base word and
-collocation with part of speech collocation seem to be more powerful features
-than dependency parsing, and bootstrapping on the data in an attempt to get a
-larger training base was ineffective because precision was too low.
+\end{description}
 

### 2011-04-14 paper/paper.tex

@@
 
-\end{description}
+\section{Conclusion}
+
+The \naive Bayes and decision tree classifiers are not smart enough to sort out
+a large number of features when the data sets are of small or moderate size,
+which requires judicious choosing of features.  Co-occurrence, base word and
+collocation with part of speech collocation seem to be more powerful features
+than dependency parsing, and bootstrapping on the data in an attempt to get a
+larger training base was ineffective because precision was too low.
 

### 2011-04-14 paper/paper.tex
putting in final segment

--- 2011-04-14 paper/paper.tex
@@
 We wrote our main control program, classify.py, so that it can choose either
-Naive Bayes or Decision Trees classifier and any combination of
-features. On top of this we wrote bash scripts that automated 
+Naive Bayes or Decision Trees classifier and any 
+combination of  features. On top of this we wrote bash scripts that automated
 looping through every combination of classifiers and features, along with
@@
 \subsection{Selecting optimal feature combination}
-\newcommand\ward{backward} %or maybe backwards
+\newcommand\ward{forward} %or maybe backwards
 
@@
 
-As the regression table above shows, it seems that substituting the
-Decision Tree classifier for the Naive Bayes baseline provides the
-most significant boost to our f measure. It can also be seen here that
-increasing the collocation window will increase the f measure by about 0.003
-for each additional word added to the window. Additionally, enabling
-the cooccurrence feature extractor with the Naive Bayes classifier
-will increase the f measure by a significant amount as well.
-
-The rows that contain negative terms may indicate that the interacting
-features provide similar functionality. That is, the enabled features
-are interfering with each other so that their final influence on the f
-measure may affect the f measure negatively. For instance, the row
-showing ``classifiert:collocation'' indicates a run where the Decision
-Tree classifier was used and the collocation feature was enabled has
-resulted in a lower accuracy. This seems to be the general trend for
-all of the interacting features. It may be interesting to note that
-the interaction between collocation and cooccurrence1 as well as
-collocation and dependency parsing produce the most innocuous
-cumulative effect. Perhaps this may be why collocation and
-cooccurrence are often advocated to be used together.
+%The negative interaction terms may indicate that the interacting features provide
+similar functionality and blah blah blah
 
@@
 
-\end{description}
+\section{System's Output During Processing}
+
+Because we automated all of the tests we wrote the output to files as we tested it.
+The results are included in the folder experiment/allruns.
+The calls.csv file shows the features that were used in each test and the output for each test.
+The output was formatted in a way that the scorer would accept.
 

### 2011-04-14 paper/paper.tex

@@
 
+\section{Conclusion}
+
+The \naive{} Bayes and decision tree classifiers are not smart enough to sort out
+a large number of features when the data sets are of small or moderate size,
+which requires judicious choosing of features.  Co-occurrence, base word and
+collocation with part of speech collocation seem to be more powerful features
+than dependency parsing, and bootstrapping on the data in an attempt to get a
+larger training base was ineffective because precision was too low.
+
 \end{document}

### 2011-04-14 paper/paper.tex
fixed conflicts
Baseline graph discussion added. w00t

--- 2011-04-14 paper/paper.tex
@@
 could reuse parsing information across runs of our program.  Because this file
-is several hundred megabytes in size, it is not included in our submitted code.
+is several hundred megabytes in size, it is not included in our
+submitted code.
+
 \subsection{Collocation}
@@
 \end{figure}
+
+Figure \ref{fig:base} shows our results for running just the Decision
+Tree classifier and the \naive{} Bayes classifier with no features
+enabled. With no bootstrapping, the Decision Tree classifier has a
+much higher f-measure. With bootstrapping, the Decision Tree
+classifier decreases in f-measure while the \naive{} Bayes classifier
+improves in f-measure.
 

### 2011-04-14 paper/paper.tex

@@
 We wrote our main control program, classify.py, so that it can choose either
-Naive Bayes or Decision Trees classifier and any combination of
-features. On top of this we wrote bash scripts that automated 
+\Naive{} Bayes or Decision Trees classifier and any 
+combination of  features. On top of this we wrote bash scripts that automated
 looping through every combination of classifiers and features, along with

### 2011-04-14 paper/paper.tex
fixed recall

--- 2011-04-14 paper/paper.tex
@@
 \hline
-provide.v	&	1094	&	0.906	&	0.015	&	0.938	&	0.015	&	0.922	&	0.015\\
-watch.v	&	806	&	0.878	&	0.011	&	0.918	&	0.011	&	0.918	&	0.011\\
-remain.v	&	1118	&	0.871	&	0.015	&	0.871	&	0.015	&	0.871	&	0.015\\
-hot.a	&	696	&	0.853	&	0.007	&	0.853	&	0.007	&	0.853	&	0.007\\
-arm.n	&	2137	&	0.841	&	0.027	&	0.841	&	0.027	&	0.841	&	0.027\\
-eat.v	&	1463	&	0.833	&	0.018	&	0.833	&	0.018	&	0.833	&	0.018\\
-add.v	&	2148	&	0.806	&	0.026	&	0.806	&	0.026	&	0.806	&	0.026\\
-plan.n	&	1353	&	0.797	&	0.016	&	0.835	&	0.017	&	0.835	&	0.017\\
-talk.v	&	1174	&	0.797	&	0.014	&	0.797	&	0.014	&	0.797	&	0.014\\
-use.v	&	214	&	0.786	&	0.003	&	0.786	&	0.003	&	0.786	&	0.003\\
-smell.v	&	874	&	0.784	&	0.01	&	0.804	&	0.01	&	0.804	&	0.01\\
-audience.n	&	1637	&	0.768	&	0.019	&	0.96	&	0.024	&	0.904	&	0.023\\
-expect.v	&	1275	&	0.756	&	0.015	&	0.756	&	0.015	&	0.756	&	0.015\\
-mean.v	&	646	&	0.737	&	0.007	&	0.737	&	0.007	&	0.737	&	0.007\\
-appear.v	&	2139	&	0.731	&	0.024	&	0.731	&	0.024	&	0.731	&	0.024\\
-express.v	&	887	&	0.731	&	0.01	&	0.769	&	0.01	&	0.769	&	0.01\\
-interest.n	&	1489	&	0.728	&	0.015	&	0.728	&	0.015	&	0.728	&	0.015\\
-sort.n	&	1566	&	0.728	&	0.017	&	0.88	&	0.021	&	0.853	&	0.02\\
-begin.v	&	1478	&	0.723	&	0.012	&	0.723	&	0.012	&	0.723	&	0.012\\
-note.v	&	1064	&	0.712	&	0.012	&	0.712	&	0.012	&	0.712	&	0.012\\
-receive.v	&	422	&	0.708	&	0.004	&	0.708	&	0.004	&	0.708	&	0.004\\
-decide.v	&	982	&	0.705	&	0.011	&	0.705	&	0.011	&	0.705	&	0.011\\
-wash.v	&	534	&	0.7	&	0.005	&	0.867	&	0.007	&	0.717	&	0.005\\
-climb.v	&	1073	&	0.698	&	0.011	&	0.698	&	0.011	&	0.698	&	0.011\\
-degree.n	&	2085	&	0.695	&	0.021	&	0.78	&	0.023	&	0.775	&	0.023\\
-bank.n	&	2113	&	0.684	&	0.02	&	0.744	&	0.022	&	0.718	&	0.021\\
-ask.v	&	2150	&	0.659	&	0.015	&	0.659	&	0.015	&	0.659	&	0.015\\
-rule.v	&	478	&	0.655	&	0.005	&	0.655	&	0.005	&	0.655	&	0.005\\
-activate.v	&	1874	&	0.65	&	0.017	&	0.65	&	0.017	&	0.65	&	0.017\\
-organization.n	&	905	&	0.648	&	0.009	&	0.778	&	0.011	&	0.75	&	0.01\\
-operate.v	&	286	&	0.643	&	0.002	&	0.714	&	0.003	&	0.714	&	0.003\\
-hear.v	&	510	&	0.633	&	0.005	&	0.7	&	0.005	&	0.7	&	0.005\\
-win.v	&	631	&	0.633	&	0.005	&	0.633	&	0.005	&	0.633	&	0.005\\
-shelter.n	&	1604	&	0.63	&	0.013	&	0.63	&	0.013	&	0.63	&	0.013\\
-party.n	&	1863	&	0.622	&	0.014	&	0.622	&	0.014	&	0.622	&	0.014\\
-source.n	&	527	&	0.607	&	0.004	&	0.607	&	0.004	&	0.607	&	0.004\\
-difference.n	&	1841	&	0.604	&	0.014	&	0.637	&	0.015	&	0.632	&	0.015\\
-write.v	&	355	&	0.579	&	0.003	&	0.579	&	0.003	&	0.579	&	0.003\\
-argument.n	&	1831	&	0.577	&	0.01	&	0.676	&	0.012	&	0.669	&	0.012\\
-atmosphere.n	&	1332	&	0.574	&	0.009	&	0.574	&	0.009	&	0.574	&	0.009\\
-paper.n	&	1914	&	0.574	&	0.009	&	0.721	&	0.011	&	0.689	&	0.011\\
-lose.v	&	574	&	0.552	&	0.004	&	0.552	&	0.004	&	0.552	&	0.004\\
-produce.v	&	1496	&	0.538	&	0.012	&	0.538	&	0.012	&	0.538	&	0.012\\
-encounter.v	&	1046	&	0.534	&	0.008	&	0.966	&	0.014	&	0.615	&	0.009\\
-image.n	&	1176	&	0.508	&	0.008	&	0.508	&	0.008	&	0.508	&	0.008\\
-disc.n	&	1633	&	0.488	&	0.005	&	0.488	&	0.005	&	0.488	&	0.005\\
-difficulty.n	&	378	&	0.474	&	0.002	&	0.842	&	0.004	&	0.719	&	0.003\\
-suspend.v	&	1032	&	0.456	&	0.007	&	0.456	&	0.007	&	0.456	&	0.007\\
-treat.v	&	903	&	0.442	&	0.005	&	0.465	&	0.005	&	0.465	&	0.005\\
-important.a	&	305	&	0.438	&	0.002	&	0.562	&	0.002	&	0.531	&	0.002\\
-miss.v	&	470	&	0.435	&	0.003	&	0.435	&	0.003	&	0.435	&	0.003\\
-judgment.n	&	502	&	0.429	&	0.003	&	0.429	&	0.003	&	0.429	&	0.003\\
-performance.n	&	1398	&	0.396	&	0.005	&	0.562	&	0.007	&	0.521	&	0.006\\
-play.v	&	838	&	0.389	&	0.004	&	0.389	&	0.004	&	0.389	&	0.004\\
-different.a	&	796	&	0.378	&	0.004	&	0.556	&	0.006	&	0.489	&	0.006\\
-solid.a	&	475	&	0.25	&	0.001	&	0.25	&	0.001	&	0.25	&	0.001\\
-simple.a	&	298	&	0.182	&	0.001	&	0.545	&	0.002	&	0.409	&	0.001\\
+provide.v   	&	1094	&	0.906	&	0.858	&	0.938	&	0.858	&	0.922	&	0.858\\
+watch.v     	&	806 	&	0.878	&	0.851	&	0.918	&	0.851	&	0.918	&	0.851\\
+remain.v    	&	1118	&	0.871	&	0.845	&	0.871	&	0.845	&	0.871	&	0.845\\
+hot.a       	&	696 	&	0.853	&	0.642	&	0.853	&	0.642	&	0.853	&	0.642\\
+arm.n       	&	2137	&	0.841	&	0.801	&	0.841	&	0.801	&	0.841	&	0.801\\
+eat.v       	&	1463	&	0.833	&	0.816	&	0.833	&	0.816	&	0.833	&	0.816\\
+add.v       	&	2148	&	0.806	&	0.777	&	0.806	&	0.777	&	0.806	&	0.777\\
+plan.n      	&	1353	&	0.797	&	0.751	&	0.835	&	0.798	&	0.835	&	0.798\\
+talk.v      	&	1174	&	0.797	&	0.757	&	0.797	&	0.757	&	0.797	&	0.757\\
+use.v       	&	214 	&	0.786	&	0.845	&	0.786	&	0.845	&	0.786	&	0.845\\
+smell.v     	&	874 	&	0.784	&	0.717   &	0.804	&	0.717   &	0.804	&	0.717\\
+audience.n    	&	1637	&	0.768	&	0.750	&	0.96	&	0.947	&	0.904	&	0.907\\
+expect.v    	&	1275	&	0.756	&	0.759	&	0.756	&	0.759	&	0.756	&	0.759\\
+mean.v      	&	646 	&	0.737	&	0.690	&	0.737	&	0.690	&	0.737	&	0.690\\
+appear.v    	&	2139	&	0.731	&	0.712	&	0.731	&	0.712	&	0.731	&	0.712\\
+express.v    	&	887 	&	0.731	&	0.717   &	0.769	&	0.717   &	0.769	&	0.717\\
+interest.n    	&	1489	&	0.728	&	0.636	&	0.728	&	0.636	&	0.728	&	0.636\\
+sort.n      	&	1566	&	0.728	&	0.699	&	0.88	&	0.863	&	0.853	&	0.822\\
+begin.v     	&	1478	&	0.723	&	0.599	&	0.723	&	0.599	&	0.723	&	0.599\\
+note.v      	&	1064	&	0.712	&	0.707	&	0.712	&	0.707	&	0.712	&	0.707\\
+receive.v    	&	422 	&	0.708	&	0.584	&	0.708	&	0.584	&	0.708	&	0.584\\
+decide.v    	&	982 	&	0.705	&	0.700	&	0.705	&	0.700	&	0.705	&	0.700\\
+wash.v      	&	534 	&	0.700	&	0.580	&	0.867	&	0.812	&	0.717	&	0.580\\
+climb.v     	&	1073	&	0.698	&	0.648	&	0.698	&	0.648	&	0.698	&	0.648\\
+degree.n    	&	2085	&	0.695	&	0.647	&	0.78	&	0.709	&	0.775	&	0.709\\
+bank.n      	&	2113	&	0.684	&	0.598   &	0.744	&	0.658	&	0.718	&	0.628\\
+ask.v       	&	2150	&	0.659	&	0.452	&	0.659	&	0.452	&	0.659	&	0.452\\
+rule.v      	&	478 	&	0.655	&	0.658	&	0.655	&	0.658	&	0.655	&	0.658\\
+activate.v    	&	1874	&	0.65	&	0.588	&	0.65	&	0.588	&	0.65	&	0.588\\
+organization.n	&	905 	&	0.648	&	0.634	&	0.778	&	0.775	&	0.75	&	0.704\\
+operate.v    	&	286 	&	0.643	&	0.438	&	0.714	&	0.658	&	0.714	&	0.658\\
+hear.v      	&	510 	&	0.633	&	0.616	&	0.700	&	0.616	&	0.700	&	0.616\\
+win.v       	&	631 	&	0.633	&	0.506	&	0.633	&	0.506	&	0.633	&	0.506\\
+shelter.n    	&	1604	&	0.63	&	0.523	&	0.63	&	0.523	&	0.63	&	0.523\\
+party.n     	&	1863	&	0.622	&	0.476	&	0.622	&	0.476	&	0.622	&	0.476\\
+source.n    	&	527 	&	0.607	&	0.493	&	0.607	&	0.493	&	0.607	&	0.493\\
+difference.n	&	1841	&	0.604	&	0.484	&	0.637	&	0.519	&	0.632	&	0.519\\
+write.v     	&	355 	&	0.579	&	0.493	&	0.579	&	0.493	&	0.579	&	0.493\\
+argument.n    	&	1831	&	0.577	&	0.355   &	0.676	&	0.426	&	0.669	&	0.426\\
+atmosphere.n	&	1332	&	0.574	&	0.438	&	0.574	&	0.438	&	0.574	&	0.438\\
+paper.n     	&	1914	&	0.574	&	0.303	&	0.721	&	0.371	&	0.689	&	0.371\\
+lose.v      	&	574 	&	0.552	&	0.438	&	0.552	&	0.438	&	0.552	&	0.438\\
+produce.v    	&	1496	&	0.538	&	0.504	&	0.538	&	0.504	&	0.538	&	0.504\\
+encounter.v    	&	1046	&	0.534	&	0.486	&	0.966	&	0.850	&	0.615	&	0.546\\
+image.n     	&	1176	&	0.508	&	0.426	&	0.508	&	0.426	&	0.508	&	0.426\\
+disc.n      	&	1633	&	0.488	&	0.197	&	0.488	&	0.197	&	0.488	&	0.197\\
+difficulty.n	&	378 	&	0.474	&	0.343	&	0.842	&	0.686	&	0.719	&	0.515\\
+suspend.v    	&	1032	&	0.456	&	0.431	&	0.456	&	0.431	&	0.456	&	0.431\\
+treat.v        	&	903 	&	0.442	&	0.346	&	0.465	&	0.346	&	0.465	&	0.346\\
+important.a    	&	305 	&	0.438	&	0.415	&	0.562	&	0.415	&	0.531	&	0.415\\
+miss.v        	&	470 	&	0.435	&	0.395	&	0.435	&	0.395	&	0.435	&	0.395\\
+judgment.n    	&	502 	&	0.429	&	0.370	&	0.429	&	0.370	&	0.429	&	0.370\\
+performance.n	&	1398	&	0.396	&	0.227	&	0.562	&	0.317	&	0.521	&	0.272\\
+play.v        	&	838 	&	0.389	&	0.303	&	0.389	&	0.303	&	0.389	&	0.303\\
+different.a    	&	796 	&	0.378	&	0.316	&	0.556	&	0.473	&	0.489	&	0.473\\
+solid.a        	&	475 	&	0.25	&	0.136	&	0.25	&	0.136	&	0.25	&	0.136\\
+simple.a    	&	298 	&	0.182	&	0.219	&	0.545	&	0.438	&	0.409	&	0.219\\
 
@@
 
-\section{System's Output During Processing}
-
-Because we automated all of the tests we wrote the output to files as we tested it.
-The results are included in the folder experiment/allruns.
-The calls.csv file shows the features that were used in each test and the output for each test.
-The output was formatted in a way that the scorer would accept.
-
 \section{Conclusion}

### 2011-04-14 paper/paper.tex
confidence info
Collocation Window graph elaborated...

--- 2011-04-14 paper/paper.tex
@@
 
-Collocation window of size 2--4 had the best performance (figure \ref{fig2}), so we looked more closely at those.
+Collocation window of size 2--4 had the best performance (figure
+\ref{fig2}), so we looked more closely at those. What this seems to
+imply is that words very close to the head word are the most
+important, as expected.
 

### 2011-04-14 paper/paper.tex
nothing important

--- 2011-04-14 paper/paper.tex
@@
 are present in the training data, and we made no effort to remove them, so the
-learning algorithm views them as any other label.
+learning algorithm views them as any other label.  Where we used confidence
+cutoffs, we used .5 as our cutoff.
 
@@
 system spends is in reading input and building feature sets, which don't need
-to be repeated, so bootstrapping is very cheap to include.
+to be repeated, so bootstrapping is very cheap to include.  The probability measure that we used for the algorithm was 0.8
 

### 2011-04-14 paper/paper.tex

@@
 system spends is in reading input and building feature sets, which don't need
-to be repeated, so bootstrapping is very cheap to include.  The probability measure that we used for the algorithm was 0.8
+to be repeated, so bootstrapping is very cheap to include.
 

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/config/ConfigurationDir.java
removed MaltParser

@@ -1,796 +1,0 @@
-package org.maltparser.core.config;
-
-import java.io.BufferedInputStream;
-import java.io.BufferedOutputStream;
-import java.io.BufferedReader;
-import java.io.BufferedWriter;
-import java.io.File;
-import java.io.FileInputStream;
-import java.io.FileNotFoundException;
-import java.io.FileOutputStream;
-import java.io.FileReader;
-import java.io.FileWriter;
-import java.io.IOException;
-import java.io.InputStreamReader;
-import java.io.OutputStreamWriter;
-import java.io.UnsupportedEncodingException;
-import java.net.URL;
-import java.util.Date;
-import java.util.HashSet;
-import java.util.SortedSet;
-import java.util.TreeSet;
-import java.util.jar.JarEntry;
-import java.util.jar.JarInputStream;
-import java.util.jar.JarOutputStream;
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.helper.SystemInfo;
-import org.maltparser.core.helper.SystemLogger;
-import org.maltparser.core.helper.Util;
-import org.maltparser.core.options.OptionManager;
-
-/**
-* This class contains methods for handle the configuration directory.
-*
-* @author Johan Hall
-*/
-public class ConfigurationDir  {
-	protected static final int BUFFER = 4096;
-	protected File configDirectory;
-	protected String name;
-	protected String type;
-	protected File workingDirectory;
-	protected URL url = null;
-	protected int containerIndex;
-	protected BufferedWriter infoFile = null;
-	protected String createdByMaltParserVersion;
-
-	
-	/**
-	 * Creates a configuration directory from a mco-file specified by an URL.
-	 * 
-	 * @param url	an URL to a mco-file
-	 * @throws MaltChainedException
-	 */
-	public ConfigurationDir(URL url) throws MaltChainedException {
-		initWorkingDirectory();
-		setUrl(url);
-		initNameNTypeFromInfoFile(url);
-	}
-	
-	/**
-	 * Creates a new configuration directory or a configuration directory from a mco-file
-	 * 
-	 * @param name	the name of the configuration
-	 * @param type	the type of configuration
-	 * @param containerIndex	the container index
-	 * @throws MaltChainedException
-	 */
-	public ConfigurationDir(String name, String type, int containerIndex) throws MaltChainedException {
-		setContainerIndex(containerIndex);
-		initWorkingDirectory();
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/config/ConfigurationRegistry.java

@@ -1,14 +1,0 @@
-package org.maltparser.core.config;
-
-import java.util.HashMap;
-/**
-*
-* @author Johan Hall
-**/
-public class ConfigurationRegistry extends HashMap<Class<?>, Object> {
-	public final static long serialVersionUID = 3256444702936019250L;
-	
-	public ConfigurationRegistry() {
-		super();
-	}
-}

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/feature/map/MergeFeature.java

@@ -1,157 +1,0 @@
-package org.maltparser.core.feature.map;
-
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.feature.FeatureException;
-import org.maltparser.core.feature.function.FeatureFunction;
-import org.maltparser.core.feature.function.FeatureMapFunction;
-import org.maltparser.core.feature.value.FeatureValue;
-import org.maltparser.core.feature.value.FunctionValue;
-import org.maltparser.core.feature.value.SingleFeatureValue;
-import org.maltparser.core.symbol.SymbolTable;
-import org.maltparser.core.symbol.SymbolTableHandler;
-/**
-*
-*
-* @author Johan Hall
-*/
-public class MergeFeature implements FeatureMapFunction {
-	protected FeatureFunction firstFeature;
-	protected FeatureFunction secondFeature;
-	protected SymbolTableHandler tableHandler;
-	protected SymbolTable table;
-	protected SingleFeatureValue singleFeatureValue;
-	
-	public MergeFeature(SymbolTableHandler tableHandler) throws MaltChainedException {
-		super();
-		setTableHandler(tableHandler);
-		singleFeatureValue = new SingleFeatureValue(this);
-	}
-	
-	public void initialize(Object[] arguments) throws MaltChainedException {
-		if (arguments.length != 2) {
-			throw new FeatureException("Could not initialize MergeFeature: number of arguments are not correct. ");
-		}
-		if (!(arguments[0] instanceof FeatureFunction)) {
-			throw new FeatureException("Could not initialize MergeFeature: the first argument is not a feature. ");
-		}
-		if (!(arguments[1] instanceof FeatureFunction)) {
-			throw new FeatureException("Could not initialize MergeFeature: the second argument is not a feature. ");
-		}
-		setFirstFeature((FeatureFunction)arguments[0]);
-		setSecondFeature((FeatureFunction)arguments[1]);
-		setSymbolTable(tableHandler.addSymbolTable("MERGE2_"+firstFeature.getSymbolTable().getName()+"_"+secondFeature.getSymbolTable().getName(), firstFeature.getSymbolTable()));
-	}
-	
-	public void update() throws MaltChainedException {
-//		multipleFeatureValue.reset();
-		singleFeatureValue.reset();
-		firstFeature.update();
-		secondFeature.update();
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/feature/map/SuffixFeature.java

@@ -1,159 +1,0 @@
-package org.maltparser.core.feature.map;
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.feature.FeatureException;
-import org.maltparser.core.feature.function.FeatureFunction;
-import org.maltparser.core.feature.function.FeatureMapFunction;
-import org.maltparser.core.feature.value.FeatureValue;
-import org.maltparser.core.feature.value.FunctionValue;
-import org.maltparser.core.feature.value.MultipleFeatureValue;
-import org.maltparser.core.feature.value.SingleFeatureValue;
-import org.maltparser.core.symbol.SymbolTable;
-import org.maltparser.core.symbol.SymbolTableHandler;
-/**
-*
-*
-* @author Johan Hall
-*/
-public class SuffixFeature implements FeatureMapFunction {
-	protected FeatureFunction parentFeature;
-	protected MultipleFeatureValue multipleFeatureValue;
-	protected SymbolTableHandler tableHandler;
-	protected SymbolTable table;
-	protected int suffixLength;
-
-	public SuffixFeature(SymbolTableHandler tableHandler) throws MaltChainedException {
-		super();
-		setTableHandler(tableHandler);
-		multipleFeatureValue = new MultipleFeatureValue(this);
-	}
-	
-	public void initialize(Object[] arguments) throws MaltChainedException {
-		if (arguments.length != 2) {
-			throw new FeatureException("Could not initialize SuffixFeature: number of arguments are not correct. ");
-		}
-		if (!(arguments[0] instanceof FeatureFunction)) {
-			throw new FeatureException("Could not initialize SuffixFeature: the first argument is not a feature. ");
-		}
-		if (!(arguments[1] instanceof Integer)) {
-			throw new FeatureException("Could not initialize SuffixFeature: the second argument is not a string. ");
-		}
-		setParentFeature((FeatureFunction)arguments[0]);
-		setSuffixLength(((Integer)arguments[1]).intValue());
-		setSymbolTable(tableHandler.addSymbolTable("SUFFIX_"+suffixLength+"_"+parentFeature.getSymbolTable().getName(), parentFeature.getSymbolTable()));
-	}
-	
-	public Class<?>[] getParameterTypes() {
-		Class<?>[] paramTypes = { org.maltparser.core.syntaxgraph.feature.InputColumnFeature.class, java.lang.Integer.class };
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/feature/value/FeatureValue.java

@@ -1,64 +1,0 @@
-package org.maltparser.core.feature.value;
-
-import org.maltparser.core.feature.function.Function;
-
-/**
- *  
- *
- * @author Johan Hall
- * @since 1.0
-**/
-public abstract class FeatureValue extends FunctionValue {
-	protected boolean nullValue;
-	protected int cardinality;
-	
-	public FeatureValue(Function function) {
-		super(function);
-		setNullValue(true);
-		setCardinality(0);
-	}
-	
-	public void reset() {
-		setNullValue(true);
-	}
-
-	public boolean isNullValue() {
-		return nullValue;
-	}
-
-	public void setNullValue(boolean nullValue) {
-		this.nullValue = nullValue;
-	}
-
-	/**
-	 * Returns the cardinality (the number of distinct values) of the feature 
-	 * 
-	 * @return the cardinality (the number of distinct values) of the feature 
-	 */
-	public int getCardinality() {
-		return cardinality;
-	}
-
-	/**
-	 * Sets the cardinality (the number of distinct values) of the feature
-	 * 
-	 * @param cardinality  the cardinality (the number of distinct values)
-	 */
-	public void setCardinality(int cardinality) {
-		this.cardinality = cardinality;
-	}
-
-	public boolean equals(Object obj) {
-		if (this == obj)
-			return true;
-		if (obj == null)
-			return false;
-		if (getClass() != obj.getClass())
-			return false;
-		return super.equals(obj);
-	}
-	
-	public String toString() {
-		return super.toString()+ "[ null=" + nullValue + ", cardinality="+cardinality+" ] ";
-	}
-}

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/helper/Util.java

@@ -1,181 +1,0 @@
-package org.maltparser.core.helper;
-
-
-import java.io.File;
-import java.io.IOException;
-import java.io.InputStream;
-import java.net.MalformedURLException;
-import java.net.URL;
-
-import org.apache.log4j.Logger;
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.plugin.Plugin;
-import org.maltparser.core.plugin.PluginLoader;
-
-/**
-*
-*
-* @author Johan Hall
-*/
-public class Util {
-	  private static final char AMP_CHAR = '&';
-	  private static final char LT_CHAR = '<';
-	  private static final char GT_CHAR = '>';
-	  private static final char QUOT_CHAR = '"';
-	  private static final char APOS_CHAR = '\'';
-	
-	  public static String xmlEscape(String str) {
-		  boolean needEscape = false;
-		  char c;
-		  for (int i = 0; i < str.length(); i++) {
-			  c = str.charAt(i);
-			  if (c == AMP_CHAR || c == LT_CHAR || c == GT_CHAR || c == QUOT_CHAR || c == APOS_CHAR) {
-				  needEscape = true;
-				  break;
-			  }
-		  }
-		  if (!needEscape) {
-			  return str;
-		  }
-		  final StringBuilder sb = new StringBuilder();
-		  for (int i = 0; i < str.length(); i++) {
-			  c = str.charAt(i);
-			  if (str.charAt(i) == AMP_CHAR) {
-				  sb.append("&amp;");
-			  } else if ( str.charAt(i) == LT_CHAR) {
-				  sb.append("&lt;");
-			  } else if (str.charAt(i) == GT_CHAR) {
-				  sb.append("&gt;");
-			  } else if (str.charAt(i) == QUOT_CHAR) {
-				  sb.append("&quot;");
-			  } else if (str.charAt(i) == APOS_CHAR) {
-				  sb.append("&apos;");
-			  } else {
-				  sb.append(c);
-			  }
-		  }
-		  return sb.toString();
-	  }
-
-	/**
-	 * Search for a file according the following priority:
-	 * <ol>
-	 * <li>The local file system
-	 * <li>Specified as an URL (starting with http:, file:, ftp: or jar:
-	 * <li>MaltParser distribution file (malt.jar)
-	 * <li>MaltParser plugins
-	 * </ol>
-	 * 
-	 * If the file string is found, an URL object is returned, otherwise <b>null</b>
-	 * 
-	 * @param fileString	the file string to convert into an URL.
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/options/OptionDescriptions.java

@@ -1,409 +1,0 @@
-package org.maltparser.core.options;
-
-import java.net.URL;
-import java.util.Collection;
-import java.util.HashMap;
-import java.util.HashSet;
-import java.util.Set;
-import java.util.TreeSet;
-
-import javax.xml.parsers.DocumentBuilder;
-import javax.xml.parsers.DocumentBuilderFactory;
-import javax.xml.parsers.ParserConfigurationException;
-
-import org.apache.log4j.Logger;
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.helper.SystemLogger;
-import org.maltparser.core.options.option.BoolOption;
-import org.maltparser.core.options.option.ClassOption;
-import org.maltparser.core.options.option.EnumOption;
-import org.maltparser.core.options.option.IntegerOption;
-import org.maltparser.core.options.option.Option;
-import org.maltparser.core.options.option.StringEnumOption;
-import org.maltparser.core.options.option.StringOption;
-import org.maltparser.core.options.option.UnaryOption;
-import org.w3c.dom.Element;
-import org.w3c.dom.NodeList;
-import org.xml.sax.SAXException;
-
-/**
- * Organizes all the option descriptions. Option descriptions can be loaded from the application data <code>/appdata/options.xml</code>, but also 
- * from a plugin option description file (always with the name <code>plugin.xml</code>).
- * 
-* @author Johan Hall
-* @since 1.0
-**/
-public class OptionDescriptions {
-//	private static Logger logger = SystemLogger.logger();
-	private HashMap<String, OptionGroup> optionGroups;
-	private TreeSet<String> ambiguous;
-	private HashMap<String, Option> unambiguousOptionMap;
-	private HashMap<String, Option> ambiguousOptionMap;
-	private HashMap<String, Option> flagOptionMap;
-
-	/**
-	 * Creates the Option Descriptions
-	 */
-	public OptionDescriptions() {
-		optionGroups = new HashMap<String, OptionGroup>();
-		ambiguous = new TreeSet<String>();
-		unambiguousOptionMap = new HashMap<String, Option>();
-		ambiguousOptionMap = new HashMap<String, Option>();
-		flagOptionMap = new HashMap<String, Option>();
-	}
-	
-	
-	/**
-	 * Returns an option based on the option name and/or the option group name 
-	 * 
-	 * @param optiongroup	the name of the option group
-	 * @param optionname	the option name
-	 * @return an option based on the option name and/or the option group name 
-	 * @throws MaltChainedException
-	 */
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/symbol/SymbolTable.java

@@ -1,26 +1,0 @@
-package org.maltparser.core.symbol;
-
-import java.io.BufferedReader;
-import java.io.BufferedWriter;
-import java.util.Set;
-
-import org.apache.log4j.Logger;
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.symbol.nullvalue.NullValues.NullValueId;
-
-public interface SymbolTable extends Table {
-	public int addSymbol(StringBuilder symbol) throws MaltChainedException;
-	public boolean getKnown(int code);
-	public boolean getKnown(String symbol);
-	public void makeKnown(int code);
-	public Set<Integer> getCodes();
-	public void printSymbolTable(Logger logger) throws MaltChainedException;
-	public void save(BufferedWriter out) throws MaltChainedException;
-	public void load(BufferedReader in) throws MaltChainedException;
-	public int getValueCounter();
-	public int getNullValueCode(NullValueId nullValueIdentifier) throws MaltChainedException;
-	public String getNullValueSymbol(NullValueId nullValueIdentifier) throws MaltChainedException;
-	public boolean isNullValue(String value) throws MaltChainedException;
-	public boolean isNullValue(int code) throws MaltChainedException;
-	public void copy(SymbolTable fromTable) throws MaltChainedException;
-}

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/symbol/nullvalue/InputNullValues.java

@@ -1,60 +1,0 @@
-package org.maltparser.core.symbol.nullvalue;
-
-import org.maltparser.core.symbol.SymbolTable;
-/**
-
-
-@author Johan Hall
-@since 1.0
- */
-public class InputNullValues extends NullValues {
-	
-	public InputNullValues(String nullValueStrategy, SymbolTable table) {
-		super(table);
-		setNullValueEncoding(nullValueStrategy);
-		makeNullValues();
-	}
-	
-	protected void makeNullValues() {
-		if (nullValueEncoding == NullValueDegree.NONE || nullValueEncoding == NullValueDegree.ONE) {
-			nullValue2SymbolMap.put(NullValueId.NO_NODE, "#null#");
-			nullValue2SymbolMap.put(NullValueId.ROOT_NODE, "#null#");
-			nullValue2CodeMap.put(NullValueId.NO_NODE, 0);
-			nullValue2CodeMap.put(NullValueId.ROOT_NODE, 0);
-			symbol2CodeMap.put("#null#", 0);
-			code2SymbolMap.put(0, "#null#");
-			setNextCode(1);
-		} else if (nullValueEncoding == NullValueDegree.ROOTNODE) {
-			nullValue2SymbolMap.put(NullValueId.NO_NODE, "#null#");
-			nullValue2SymbolMap.put(NullValueId.ROOT_NODE, "#rootnode#");
-			nullValue2CodeMap.put(NullValueId.NO_NODE, 0);
-			nullValue2CodeMap.put(NullValueId.ROOT_NODE, 1);
-			symbol2CodeMap.put("#null#", 0);
-			symbol2CodeMap.put("#rootnode#", 1);
-			code2SymbolMap.put(0, "#null#");
-			code2SymbolMap.put(1, "#rootnode#");
-			setNextCode(2);
-		} 
-	}
-	
-	protected void setNullValueEncoding(String nullValueStrategy) {
-		setNullValueStrategy(nullValueStrategy);
-		if (nullValueStrategy.equalsIgnoreCase("none")) {
-			nullValueEncoding = NullValueDegree.NONE;
-		} else if (nullValueStrategy.equalsIgnoreCase("rootlabel")) {
-			nullValueEncoding = NullValueDegree.ONE;
-		} else if (nullValueStrategy.equalsIgnoreCase("rootnode")) {
-			nullValueEncoding = NullValueDegree.ROOTNODE;
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/syntaxgraph/feature/ColumnFeature.java

@@ -1,102 +1,0 @@
-package org.maltparser.core.syntaxgraph.feature;
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.feature.function.FeatureFunction;
-import org.maltparser.core.feature.function.Modifiable;
-import org.maltparser.core.feature.value.FeatureValue;
-import org.maltparser.core.feature.value.SingleFeatureValue;
-import org.maltparser.core.io.dataformat.ColumnDescription;
-import org.maltparser.core.symbol.SymbolTable;
-import org.maltparser.core.symbol.nullvalue.NullValues.NullValueId;
-
-/**
-*
-*
-* @author Johan Hall
-*/
-public abstract class ColumnFeature implements FeatureFunction, Modifiable {
-	protected ColumnDescription column;
-	protected SingleFeatureValue featureValue;
-	
-	public ColumnFeature() throws MaltChainedException {
-		featureValue = new SingleFeatureValue(this);
-	}
-	
-	public abstract void update() throws MaltChainedException;
-	public abstract void initialize(Object[] arguments) throws MaltChainedException;
-	public abstract Class<?>[] getParameterTypes();
-	
-	public String getSymbol(int value) throws MaltChainedException {
-		return column.getSymbolTable().getSymbolCodeToString(value);
-	}
-	
-	public int getCode(String value) throws MaltChainedException {
-		return column.getSymbolTable().getSymbolStringToCode(value);
-	}
-	
-	public ColumnDescription getColumn() {
-		return column;
-	}
-	
-	protected void setColumn(ColumnDescription column) {
-		this.column = column;
-	}
-	
-	public void updateCardinality() {
-		featureValue.setCardinality(column.getSymbolTable().getValueCounter()); 
-	}
-	
-	public void setFeatureValue(int value) throws MaltChainedException {
-		if (column.getSymbolTable().getSymbolCodeToString(value) == null) {
-			featureValue.setCode(value);
-			featureValue.setKnown(column.getSymbolTable().getKnown(value));
-			featureValue.setSymbol(column.getSymbolTable().getNullValueSymbol(NullValueId.NO_NODE));
-			featureValue.setNullValue(true);
-		} else {
-			featureValue.setCode(value);
-			featureValue.setKnown(column.getSymbolTable().getKnown(value));
-			featureValue.setSymbol(column.getSymbolTable().getSymbolCodeToString(value));
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/syntaxgraph/node/Token.java

@@ -1,951 +1,0 @@
-package org.maltparser.core.syntaxgraph.node;
-
-import java.util.NoSuchElementException;
-import java.util.Set;
-import java.util.SortedSet;
-import java.util.TreeSet;
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.helper.SystemLogger;
-import org.maltparser.core.symbol.SymbolTable;
-import org.maltparser.core.syntaxgraph.LabelSet;
-import org.maltparser.core.syntaxgraph.SyntaxGraphException;
-import org.maltparser.core.syntaxgraph.edge.Edge;
-
-
-public class Token extends GraphNode implements TokenNode, DependencyNode, PhraseStructureNode {
-	/**
-	 * the previous terminal node in the linear precedence
-	 */
-	protected TokenNode predecessor = null;
-	/**
-	 * the next terminal node in the linear precedence
-	 */
-	protected TokenNode successor = null;
-
-	/**
-	 * a reference to a node where the node is part of a component. If the node is unconnected it will reference to it self. 
-	 */
-	protected DependencyNode component;
-	protected int rank;
-	
-	protected int index;
-	
-	protected PhraseStructureNode parent;
-	protected final SortedSet<DependencyNode> heads;
-	protected final SortedSet<DependencyNode> leftDependents;
-	protected final SortedSet<DependencyNode> rightDependents;
-	
-	
-	public Token() throws MaltChainedException { 
-		parent = null;
-		heads = new TreeSet<DependencyNode>();
-		leftDependents = new TreeSet<DependencyNode>();
-		rightDependents = new TreeSet<DependencyNode>();
-		clear();
-	}
-	
-	/**
-	 * Sets the predecessor terminal node in the linear order of the terminal nodes.
-	 * 
-	 * @param predecessor the predecessor terminal node
-	 */
-	public void setPredecessor(TokenNode predecessor) {
-		this.predecessor = predecessor;
-	}
-	
-	/**
-	 * Sets the predecessor terminal node in the linear order of the terminal nodes.
-	 * 
-	 * @param successor the successor terminal node
-	 */
-	public void setSuccessor(TokenNode successor) {
-		this.successor = successor;
-	}
-	
-	/**
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/syntaxgraph/reader/BracketReader.java

@@ -1,320 +1,0 @@
-package org.maltparser.core.syntaxgraph.reader;
-
-import java.io.BufferedReader;
-import java.io.FileInputStream;
-import java.io.FileNotFoundException;
-import java.io.IOException;
-import java.io.InputStream;
-import java.io.InputStreamReader;
-import java.io.UnsupportedEncodingException;
-import java.net.URL;
-import java.util.Iterator;
-import java.util.SortedMap;
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.io.dataformat.ColumnDescription;
-import org.maltparser.core.io.dataformat.DataFormatException;
-import org.maltparser.core.io.dataformat.DataFormatInstance;
-import org.maltparser.core.syntaxgraph.MappablePhraseStructureGraph;
-import org.maltparser.core.syntaxgraph.PhraseStructure;
-import org.maltparser.core.syntaxgraph.TokenStructure;
-import org.maltparser.core.syntaxgraph.edge.Edge;
-import org.maltparser.core.syntaxgraph.node.PhraseStructureNode;
-import org.maltparser.core.syntaxgraph.node.TokenNode;
-/**
-*
-*
-* @author Johan Hall
-*/
-public class BracketReader implements SyntaxGraphReader {
-	private BufferedReader reader;
-	private DataFormatInstance dataFormatInstance;
-	private int sentenceCount;
-	private StringBuilder input;
-	private int terminalCounter; 
-	private int nonTerminalCounter;
-	private String optionString;
-	private SortedMap<String,ColumnDescription> inputColumns;
-	private SortedMap<String,ColumnDescription> edgeLabelColumns;
-	private SortedMap<String,ColumnDescription> phraseLabelColumns;
-	private char STARTING_BRACKET = '(';
-	private char CLOSING_BRACKET = ')';
-	private char INPUT_SEPARATOR = ' ';
-	private char EDGELABEL_SEPARATOR = '-';
-	private char SENTENCE_SEPARATOR = '\n';
-	private char BLANK = ' ';
-	private char CARRIAGE_RETURN = '\r';
-	private char TAB = '\t';
-	
-	public BracketReader() { 
-		input = new StringBuilder();
-	}
-	
-	public void open(String fileName, String charsetName) throws MaltChainedException {
-		try {
-			open(new FileInputStream(fileName), charsetName);
-		}catch (FileNotFoundException e) {
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/syntaxgraph/reader/ReadChartItem.java

@@ -1,237 +1,0 @@
-package org.maltparser.core.syntaxgraph.reader;
-
-import java.io.File;
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.flow.FlowChartInstance;
-import org.maltparser.core.flow.item.ChartItem;
-import org.maltparser.core.flow.spec.ChartItemSpecification;
-import org.maltparser.core.helper.Util;
-import org.maltparser.core.io.dataformat.DataFormatException;
-import org.maltparser.core.io.dataformat.DataFormatInstance;
-import org.maltparser.core.options.OptionManager;
-import org.maltparser.core.syntaxgraph.TokenStructure;
-
-public class ReadChartItem extends ChartItem {
-	private String inputFormatName;
-	private String inputFileName;
-	private String inputCharSet;
-	private String readerOptions;
-	private Class<? extends SyntaxGraphReader> graphReaderClass;
-	
-	private String nullValueStrategy;
-	private String rootLabels;
-	
-	private SyntaxGraphReader reader;
-	private String targetName;
-	private String optiongroupName;
-	private DataFormatInstance inputDataFormatInstance;
-	private TokenStructure cachedGraph = null;
-	
-	public ReadChartItem() { super(); }
-
-	public void initialize(FlowChartInstance flowChartinstance, ChartItemSpecification chartItemSpecification) throws MaltChainedException {
-		super.initialize(flowChartinstance, chartItemSpecification);
-		
-		for (String key : chartItemSpecification.getChartItemAttributes().keySet()) {
-			if (key.equals("target")) {
-				targetName = chartItemSpecification.getChartItemAttributes().get(key);
-			} else if (key.equals("optiongroup")) {
-				optiongroupName = chartItemSpecification.getChartItemAttributes().get(key);
-			}
-		}
-		
-		if (targetName == null) {
-			targetName = getChartElement("read").getAttributes().get("target").getDefaultValue();
-		} else if (optiongroupName == null) {
-			optiongroupName = getChartElement("read").getAttributes().get("optiongroup").getDefaultValue();
-		}
-		
-		setInputFormatName(OptionManager.instance().getOptionValue(getOptionContainerIndex(), optiongroupName, "format").toString());
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/syntaxgraph/writer/TigerXMLWriter.java

@@ -1,399 +1,0 @@
-package org.maltparser.core.syntaxgraph.writer;
-
-import java.io.BufferedWriter;
-import java.io.FileNotFoundException;
-import java.io.FileOutputStream;
-import java.io.IOException;
-import java.io.OutputStream;
-import java.io.OutputStreamWriter;
-import java.io.UnsupportedEncodingException;
-import java.util.SortedMap;
-import java.util.TreeMap;
-import java.util.regex.PatternSyntaxException;
-
-import org.maltparser.core.exception.MaltChainedException;
-
-import org.maltparser.core.helper.Util;
-import org.maltparser.core.io.dataformat.ColumnDescription;
-import org.maltparser.core.io.dataformat.DataFormatException;
-import org.maltparser.core.io.dataformat.DataFormatInstance;
-import org.maltparser.core.syntaxgraph.PhraseStructure;
-import org.maltparser.core.syntaxgraph.TokenStructure;
-import org.maltparser.core.syntaxgraph.node.NonTerminalNode;
-import org.maltparser.core.syntaxgraph.node.PhraseStructureNode;
-import org.maltparser.core.syntaxgraph.node.TokenNode;
-import org.maltparser.core.syntaxgraph.reader.TigerXMLHeader;
-import org.maltparser.ml.libsvm.LibsvmException;
-/**
-*
-*
-* @author Johan Hall
-*/
-public class TigerXMLWriter implements SyntaxGraphWriter {
-	private enum RootHandling {
-		TALBANKEN, NORMAL  
-	};
-
-	private BufferedWriter writer;
-	private DataFormatInstance dataFormatInstance;
-	private String optionString;
-	private int sentenceCount;
-	private TigerXMLHeader header;
-//	private boolean hasWriteTigerXMLHeader = false;
-	private RootHandling rootHandling;
-	private String sentencePrefix = "s";
-	private StringBuilder sentenceID;
-	private StringBuilder tmpID;
-	private StringBuilder rootID;
-	private int START_ID_OF_NONTERMINALS = 500;
-	private boolean labeledTerminalID;
-	private String VROOT_SYMBOL = "VROOT";
-	private boolean useVROOT = false;
-//	private String fileName = null;
-//	private String charsetName = null;
-	
-	public TigerXMLWriter() { 
-		sentenceID = new StringBuilder();
-		tmpID = new StringBuilder();
-		rootID = new StringBuilder();
-		labeledTerminalID = false;
-	}
-	
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/core/syntaxgraph/writer/WriteChartItem.java

@@ -1,245 +1,0 @@
-package org.maltparser.core.syntaxgraph.writer;
-
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.flow.FlowChartInstance;
-import org.maltparser.core.flow.item.ChartItem;
-import org.maltparser.core.flow.spec.ChartItemSpecification;
-import org.maltparser.core.io.dataformat.DataFormatException;
-import org.maltparser.core.io.dataformat.DataFormatInstance;
-import org.maltparser.core.options.OptionManager;
-import org.maltparser.core.syntaxgraph.TokenStructure;
-
-/**
-*
-*
-* @author Johan Hall
-*/
-public class WriteChartItem extends ChartItem {
-	private String outputFormatName;
-	private String outputFileName;
-	private String outputCharSet;
-	private String writerOptions;
-	private Class<? extends SyntaxGraphWriter> graphWriterClass;
-	
-	private String nullValueStrategy;
-	private String rootLabels;
-	
-	private SyntaxGraphWriter writer;
-	private String sourceName;
-	private String optiongroupName;
-	private DataFormatInstance outputDataFormatInstance;
-	private TokenStructure cachedGraph = null;
-	
-	public WriteChartItem() { super(); }
-	
-	public void initialize(FlowChartInstance flowChartinstance, ChartItemSpecification chartItemSpecification) throws MaltChainedException {
-		super.initialize(flowChartinstance, chartItemSpecification);
-		
-		for (String key : chartItemSpecification.getChartItemAttributes().keySet()) {
-			if (key.equals("source")) {
-				sourceName = chartItemSpecification.getChartItemAttributes().get(key);
-			} else if (key.equals("optiongroup")) {
-				optiongroupName = chartItemSpecification.getChartItemAttributes().get(key);
-			}
-		}
-		
-		if (sourceName == null) {
-			sourceName = getChartElement("write").getAttributes().get("source").getDefaultValue();
-		} else if (optiongroupName == null) {
-			optiongroupName = getChartElement("write").getAttributes().get("optiongroup").getDefaultValue();
-		}
-		
-		setOutputFormatName(OptionManager.instance().getOptionValue(getOptionContainerIndex(), optiongroupName, "format").toString());
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/ml/libsvm/Libsvm.java

@@ -1,978 +1,0 @@
-package org.maltparser.ml.libsvm;
-
-import java.io.BufferedReader;
-import java.io.BufferedWriter;
-import java.io.File;
-import java.io.FileNotFoundException;
-import java.io.IOException;
-import java.io.InputStream;
-import java.io.InputStreamReader;
-import java.io.OutputStreamWriter;
-import java.io.PrintStream;
-import java.text.DecimalFormat;
-import java.text.DecimalFormatSymbols;
-import java.util.ArrayList;
-import java.util.Set;
-import java.util.regex.Pattern;
-import java.util.regex.PatternSyntaxException;
-
-import libsvm.svm;
-import libsvm.svm_model;
-import libsvm.svm_node;
-import libsvm.svm_parameter;
-import libsvm.svm_problem;
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.feature.FeatureVector;
-import org.maltparser.core.feature.function.FeatureFunction;
-import org.maltparser.core.feature.value.FeatureValue;
-import org.maltparser.core.feature.value.MultipleFeatureValue;
-import org.maltparser.core.feature.value.SingleFeatureValue;
-import org.maltparser.core.helper.NoPrintStream;
-import org.maltparser.core.syntaxgraph.DependencyStructure;
-import org.maltparser.ml.LearningMethod;
-import org.maltparser.ml.libsvm.LibsvmException;
-import org.maltparser.parser.DependencyParserConfig;
-import org.maltparser.parser.guide.instance.InstanceModel;
-import org.maltparser.parser.history.action.SingleDecision;
-import org.maltparser.parser.history.kbest.KBestList;
-
-/**
-Implements an interface to the LIBSVM learner (currently the LIBSVM 2.86 is used). More information
-about LIBSVM can be found at 
-<a href="http://www.csie.ntu.edu.tw/~cjlin/libsvm/" target="_blank">LIBSVM -- A Library for Support Vector Machines</a>.
-
-@author Johan Hall
-@since 1.0
-*/
-public class Libsvm implements LearningMethod {
-	public final static String LIBSVM_VERSION = "2.86";
-	public enum Verbostity {
-		SILENT, ERROR, ALL
-	}
-	protected InstanceModel owner;
-	protected int learnerMode;
-	protected String name;
-	protected int numberOfInstances;
-	protected boolean saveInstanceFiles;
-	protected boolean excludeNullValues;
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/parser/algorithm/helper/TransitionTableHandler.java

@@ -1,32 +1,0 @@
-package org.maltparser.parser.algorithm.helper;
-
-import java.util.HashMap;
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.symbol.Table;
-import org.maltparser.core.symbol.TableHandler;
-/**
-*
-* @author Johan Hall
-* @since 1.1
-**/
-public class TransitionTableHandler implements TableHandler{
-	private final HashMap<String, TransitionTable> transitionTables;
-
-	public TransitionTableHandler() {
-		transitionTables = new HashMap<String, TransitionTable>();
-	}
-	
-	public Table addSymbolTable(String tableName) throws MaltChainedException {
-		TransitionTable table = transitionTables.get(tableName);
-		if (table == null) {
-			table = new TransitionTable(tableName);
-			transitionTables.put(tableName, table);
-		}
-		return table;
-	}
-
-	public Table getSymbolTable(String tableName) throws MaltChainedException {
-		return transitionTables.get(tableName);
-	}
-}

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/parser/algorithm/nivre/malt04/NivreMalt04.java

@@ -1,125 +1,0 @@
-package org.maltparser.parser.algorithm.nivre.malt04;
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.symbol.SymbolTable;
-import org.maltparser.core.syntaxgraph.DependencyStructure;
-import org.maltparser.core.syntaxgraph.node.DependencyNode;
-import org.maltparser.parser.SingleMalt;
-import org.maltparser.parser.algorithm.nivre.Nivre;
-
-/**
- * 
- * @author Joakim Nivre
- * @author Johan Hall
- * @since 1.0
-*/
-public abstract class NivreMalt04 extends Nivre {
-	protected SymbolTable deprel;
-	protected boolean inPostProcessingMode = false;
-	
-
-	public NivreMalt04(SingleMalt configuration) throws MaltChainedException {
-		super(configuration);
-	}
-	
-	public DependencyStructure parse(DependencyStructure parseDependencyGraph) throws MaltChainedException {
-		clear(parseDependencyGraph);
-		inPostProcessingMode = false;
-		while (!input.isEmpty()) {
-			currentAction = history.getEmptyGuideUserAction();
-			if (rootHandling != NORMAL && stack.peek().isRoot()) {
-				updateActionContainers(SHIFT, null);
-			} else {
-				configuration.predict(currentAction); 
-			}
-			transition(parseDependencyGraph);
-		}
-
-		if (postProcessing == true) {
-			input.clear();
-			inPostProcessingMode = true;
-			
-			for (int i = parseDependencyGraph.getHighestTokenIndex(); i > 0; i--) {
-				DependencyNode node = parseDependencyGraph.getDependencyNode(i);
-				if (node != null) { 
-					input.push(node);
-				}
-			}
-			int last = input.size();
-			for (int i = 1; i < stack.size(); i++) {
-				if (!stack.get(i).hasHead() || stack.get(i).getHead().isRoot()) {
-					input.set(--last, stack.get(i));
-				} 
-			}
-			stack.clear();
-			stack.push(parseDependencyGraph.getDependencyRoot());
-			while (!input.isEmpty() && input.size() > last) {
-				currentAction = history.getEmptyGuideUserAction();
-				if (rootHandling != NORMAL && stack.peek().isRoot()) {
-					updateActionContainers(SHIFT, null);
-				} else {
-					configuration.predict(currentAction); 
-				}
-				transition(parseDependencyGraph);
-			}
-		}
[…]

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/parser/guide/Model.java

@@ -1,18 +1,0 @@
-package org.maltparser.parser.guide;
-
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.syntaxgraph.DependencyStructure;
-/**
-*
-* @author Johan Hall
-* @since 1.0
-**/
-public interface Model {
-	public void finalizeSentence(DependencyStructure dependencyGraph) throws MaltChainedException;
-	public void noMoreInstances() throws MaltChainedException;
-	public void terminate() throws MaltChainedException;
-	
-	public Guide getGuide();
-	public String getModelName() throws MaltChainedException;
-}

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/parser/history/container/ActionContainer.java

@@ -1,98 +1,0 @@
-package org.maltparser.parser.history.container;
-
-
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.symbol.Table;
-/**
-*
-* @author Johan Hall
-* @since 1.1
-**/
-public class ActionContainer {
-	protected int actionCode;
-	protected String actionSymbol;
-	protected Table table;
-	protected String name;
-	
-	public ActionContainer(TableContainer tableContainer) {
-		setTable(tableContainer.getTable());
-		setName(tableContainer.getTableContainerName());
-		clear();
-	}
-	
-	public void clear() {
-		actionCode = -1;
-		actionSymbol = null;
-	}
-
-	public String getActionSymbol() {
-		return actionSymbol;
-	}
-	
-	public int getActionCode() {
-		return actionCode;
-	}
-	
-	public String setAction(int code) throws MaltChainedException {
-		if (actionCode != code) {
-			if (code < 0) {
-				clear();
-			} else {
-				actionSymbol = table.getSymbolCodeToString(code);
-				if (actionSymbol == null) {
-					clear();
-				} else {
-					actionCode = code;
-				}
-			}
-		}
-		return actionSymbol;
-	}
-	
-	public int setAction(String symbol) throws MaltChainedException {
-		if (symbol == null) {
-			clear();
-		} else {
-			actionCode = table.getSymbolStringToCode(symbol);
-			if (actionCode == -1) {
-				clear();
-			} else {
-				actionSymbol = symbol;
-			}
-		}
-		return actionCode;
-	}
-	
-	public Table getTable() {
-		return table;
-	}
-	
-	public String getTableName() {
-		if (table == null) {
-			return null;
-		}
-		return table.getName();		
-	}
-	
-	public String getTableContainerName() {
-		return name;
-	}
-
-	public void setTable(Table table) {
-		this.table = table;
-	}
-	
-	protected void setName(String name) {
-		this.name = name;
-	} 
-	
-	public String toString() {
-		final StringBuilder sb = new StringBuilder();
-		sb.append(name);
-		sb.append(" -> ");
-		sb.append(actionSymbol);
-		sb.append(" = ");
-		sb.append(actionCode);
-		return sb.toString();
-	}
-}

### 2011-04-14 MaltParser/malt-1.2/src/org/maltparser/transform/pseudo/PseudoProjectivity.java

@@ -1,713 +1,0 @@
-package org.maltparser.transform.pseudo;
-
-import java.util.Vector;
-
-import org.apache.log4j.Logger;
-import org.maltparser.core.exception.MaltChainedException;
-import org.maltparser.core.symbol.SymbolTable;
-import org.maltparser.core.symbol.SymbolTableHandler;
-import org.maltparser.core.syntaxgraph.DependencyStructure;
-import org.maltparser.core.syntaxgraph.node.DependencyNode;
-
-/**
- * This class contains methods for projectivizing and deprojectivizing
- * 
- * @author Jens Nilsson
- * @since 1.0
- */
-public class PseudoProjectivity {
-	static int id = 0;
-
-	private enum PseudoProjectiveEncoding {
-		NONE, BASELINE, HEAD, PATH, HEADPATH, TRACE
-	};
-
-	private enum CoveredRootAttachment {
-		NONE, LEFT, RIGHT, HEAD
-	};
-
-	private enum LiftingOrder {
-		SHORTEST, DEEPEST
-	};
-
-	private PseudoProjectiveEncoding markingStrategy;
-	private CoveredRootAttachment rootAttachment;
-	private LiftingOrder liftingOrder;
-	private Logger configLogger;
-
-	private SymbolTable deprelSymbolTable;
-	private SymbolTable pppathSymbolTable;
-	private SymbolTable ppliftedSymbolTable;
-	private SymbolTable ppcoveredRootSymbolTable;
-	private Vector<Boolean> nodeLifted;
-	private Vector<Vector<DependencyNode>> nodeTrace;
-	private Vector<DependencyNode> headDeprel;
-	private Vector<Boolean> nodePath;
-	private Vector<Boolean> isCoveredRoot;
-	private Vector<Integer> nodeRelationLength;
-	private Vector<String> synacticHeadDeprel;
-
-
-	public PseudoProjectivity() { }
-
-	public void initialize(String markingStrategyString, String coveredRoot, String liftingOrder, Logger configLogger,
-			SymbolTableHandler symbolTables) throws MaltChainedException {
-		nodeLifted = new Vector<Boolean>();
-		nodeTrace = new Vector<Vector<DependencyNode>>();
-		headDeprel = new Vector<DependencyNode>();
-		nodePath = new Vector<Boolean>();
-		isCoveredRoot = new Vector<Boolean>();
[…]

### 2011-04-14 src/cooccurrence.py
removed extraneous source directory

@@ -1,90 +1,0 @@
-#!/usr/bin/env python
-import os, os.path
-import nltk
-from nltk.corpus import senseval
-
-# get the senseval 3 data from system folder
-path = os.path.relpath('nltk_data')
-nltk.data.path[0]=path
-
-items = senseval.fileids()
-
-# the feature extractor code is below here -----------------------------------
-windowSize = 10     # number of words before and after to look for
-vectorSize = 12     # size of your feature vector for cooccurrence
-cooccur_vect = {}   # store the feature vector keys in here
-
-# I copied pasted the english stopwords corpus from the nltk package here
-# for convenience; however, there are also corpus specific stopwords here too
-stopwords = ['i', 'me', 'my', 'myself', 'we', 'our', 'ours', 'ourselves',\
-             'you', 'your', 'yours', 'yourself', 'yourselves', 'he', 'him',\
-             'his', 'himself', 'she', 'her', 'hers', 'herself', 'it', 'its',\
-             'itself', 'they', 'them', 'their', 'theirs', 'themselves',\
-             'what', 'which', 'who', 'whom', 'this', 'that', 'these', 'those',\
-             'am', 'is', 'are', 'was', 'were', 'be', 'been', 'being', 'have',\
-             'has', 'had', 'having', 'do', 'does', 'did', 'doing', 'a', 'an',\
-             'the', 'and', 'but', 'if', 'or', 'because', 'as', 'until',\
-             'while', 'of', 'at', 'by', 'for', 'with', 'about', 'against',\
-             'between', 'into', 'through', 'during', 'before', 'after',\
-             'above', 'below', 'to', 'from', 'up', 'down', 'in', 'out', 'on',\
-             'off', 'over', 'under', 'again', 'further', 'then', 'once',\
-             'here', 'there', 'when', 'where', 'why', 'how', 'all', 'any',\
-             'both', 'each', 'few', 'more', 'most', 'other', 'some', 'such',\
-             'no', 'nor', 'not', 'only', 'own', 'same', 'so', 'than', 'too',\
-             'very', 's', 't', 'can', 'will', 'just', 'don', 'should', 'now',\
-             
-             '.', ',', '(', ')', '{', '}', '[', ']', '-', '?', '!', "n't", "'",\
-             'r1', 'r2', 'r3', 'r4', 'r5', 'r6', 'r7', 'fig.', 'ref', '20', 'b1',\
-             "'ve", "'d", "'s", ":", ";", 'one', 'two', 'may', 'also', 'many', '%',\
[…]

### 2011-04-14 src/scripts/calls2csv.sh

@@ -1,15 +1,0 @@
-#!/bin/bash
-#Run the calls through this
-#./scripts/make_calls.sh |
-
-#Header
-echo 'classifier,bootstrap,colocation,cooccurrence,base_word,dependency_parsing,run_id'
-#Fill in empty flags
-sed -e '/#!/d' -e 's+> experiment/[^/]*/tmp+,+'|
-sed -e 's/  / -z 0 /g'|
-sed -e 's/  / -z 0 /g'|
-sed -e 's/\(-[ablrepz]\) \([-,]\)/\1 1 \2/g'|
-sed -e 's/\(-[ablrepz]\) \([-,]\)/\1 1 \2/g'|
-
-#Format as csv
-sed -e 's+^./classify.py -++' -e 's/-[ablrepz]*/,/g' -e 's/ //g'

### 2011-04-14 src/scripts/import.sh

@@ -1,11 +1,0 @@
-#!/bin/bash
-#This takes the directory of split instances and the resulting directory as arguments
-train="$1"
-dir="$2"
-
-#Convert to Senseval-2--like format
-for instance in `grep -l ^\<instance "$train"/*`
-do
-word=`sed -n 's/<instance id="\([^.]*\.[a-z]\)\..*$/\1/p' "$instance"`
-cat "$instance" >> $dir/$word.pos
-done

### 2011-04-14 src/scripts/make_calls-all.sh

@@ -1,29 +1,0 @@
-#!/bin/bash
-#Run this in the root directory like so
-#wsd.sh [test data key] 
-key=$1
-batch=$2
-
-#Edit the nested for loops to select a series of feature combinations
-run=9000
-echo '#!/bin/bash'
-for classifier in -pn -t; do
-  for bootstrap in '' '-b 1' '-b 2' '-b 4'; do #Fix how a lack of bootstrapping for trees doesn't work well here
-    for colocation in '-l 0' '-l 1' '-l 2' '-l 4' '-l 8'; do # -l NUM is the colocation distance, 0 is "don't use it"
-      for coocurrence in '' -r; do # -r enables cooccurrence usage
-        for base_word in '' -e; do # -e enables base word usage
-          for dependency in '' -a; do
-
-#Run the actual system
-#echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
-echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word $dependency > experiment/$batch/tmp$run"|
-#Remove runs with bootstrapping and trees
-grep -v '\-t \-b' 
-run=$((run+1))
-
-          done
-        done
-      done
-    done
-  done
-done

### 2011-04-14 src/scripts/score_calls-aggregated.sh

@@ -1,24 +1,0 @@
-#!/bin/bash
-#This takes
-# 1 the directory with the tmp files and
-# 2 the key file
-
-tmps=$1
-key=$2
-#run=`echo $tmp|sed s/^.*tmp//`
-echo run_id,grain,precision,recall,attempted
-for tmp in $tmps/tmp*[0-9]; do
-for grain in coarse mixed; do
-	#Remove un-answered
-	grep -v U$ $tmp > $tmp-attempted
-	#Convert to a nice format
-	./scoring/scorer2 $tmp-attempted EnglishLS.test/EnglishLS.test.key EnglishLS.test/EnglishLS.sensemap -g "$grain"|
-	sed -e 's+^.*score for.*/tmp+"tmp+' -e 's+ using key.*$++' -e 's+(.*)++' -e 's+^.*:++' -e 's/[ %]//g' -e '/^$/d ' |tr '\n' ','|sed -e 's/,$//' -e "s/,/,$grain,/"
-	echo ''
-done
-grain=fine
-	#Fine-grained
-	./scoring/scorer2 $tmp-attempted EnglishLS.test/EnglishLS.test.key|
-	sed -e 's+^.*score for.*/tmp+"tmp+' -e 's+ using key.*$++' -e 's+(.*)++' -e 's+^.*:++' -e 's/[ %]//g' -e '/^$/d ' |tr '\n' ','|sed -e 's/,$//' -e "s/,/,$grain,/"
-	echo ''
-done|sed s/-attempted//

### 2011-04-14 src/scripts/scores_by_word.sh

@@ -1,20 +1,0 @@
-#!/bin/bash
-system=$1
-
-wc -l nltk_data/corpora/senseval/*.pos|sed 's+ nltk_data/corpora/senseval/+,+'|grep -v total$ > tmp-trainingsize
-
-echo run_id,grain,precision,recall,corpus_size
-for word in nltk_data/corpora/senseval/*.pos
-do
-word=`echo $word|sed -e s+nltk_data/corpora/senseval/++ -e s+\.pos$++`
-grep "^$word" $system|grep -v U$ > tmp-$word
-for grain in coarse mixed; do
-	./scoring/scorer2 tmp-$word EnglishLS.test/EnglishLS.test.key EnglishLS.test/EnglishLS.sensemap -g "$grain"|
-        sed -e 's+^.*tmp-+"+' -e 's+ using key.*$++' -e 's+(.*)++' -e 's+^.*:++' -e 's/[ %]//g' -e '/^$/d ' |tr '\n' ','|sed -e 's/,$//' -e "s/,/,$grain,/"
-        echo ',' `grep $word tmp-trainingsize | cut -d , -f 1`
-done
-grain=fine
-        ./scoring/scorer2 tmp-$word EnglishLS.test/EnglishLS.test.key |
-        sed -e 's+^.*tmp-+"+' -e 's+ using key.*$++' -e 's+(.*)++' -e 's+^.*:++' -e 's/[ %]//g' -e '/^$/d ' |tr '\n' ','|sed -e 's/,$//' -e "s/,/,$grain,/"
-        echo ',' `grep $word tmp-trainingsize | cut -d , -f 1`
-done

### 2011-04-14 src/wsd-alec.sh

@@ -1,8 +1,0 @@
-#!/bin/bash
-batch=batch$1
-key=EnglishLS.test/EnglishLS.test.key
-mkdir experiment/$batch
-bash scripts/make_calls-alec.sh $key $batch> experiment/$batch/calls.sh
-cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
-bash experiment/$batch/calls.sh
-bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-14 experiment/analyze.R
?

@@ -166,7 +166,7 @@ plot.step1=function(){
 	ag=plot.step.import()
 	ggplot(ag,aes(colocation,f,group=c(cooccurrence)))+
 	geom_point(aes(color=cooccurrence),position=position_jitter(w=0.1, h=0))+
-	opts(title = expression("The optimal colocation window is between 2 and 4 words"))
+	opts(title = expression("The optimal colocation window is between 3 and 4 words"))
 #	opts(title = expression("Performance of all of our systems"))+
 #	scale_x_continuous('Colocation window size') + scale_y_continuous('Mixed-grained F-measure')
 }
@@ -174,8 +174,8 @@ plot.step1=function(){
 #Select optimal colocation window and keep looking
 plot.step2=function(){
 	ag=subset(plot.step.import(),colocation>=2&colocation<=4)
-	ggplot(ag,aes(classifier,f,group=c(base_word)))+
-	geom_point(aes(colour=base_word),position=position_jitter(w=0.1, h=0))+
+	ggplot(ag,aes(classifier,f,group=c(base_word,dependency_parsing)))+
+	geom_point(aes(colour=base_word,shape=dependency_parsing),position=position_jitter(w=0.1, h=0))+
 	opts(title=expression('Performance by classifier'))
 #	opts(title=expression('Performance of the systems with colocation windows between 2 and 4'))+
 #	scale_x_continuous('Classifier') + scale_y_continuous('Mixed-grained F-measure')
@@ -234,6 +234,6 @@ byword=function(file){
 
 main=function(){
 	stepping()
-#	pdf('baseline.pdf');plot.baseline();dev.off()
+# 	pdf('baseline.pdf');plot.baseline();dev.off()
 	byword('../byword_tmp28')
 }

### 2011-04-14 src/scripts/make_calls-smp2.sh
zipped all of our scripts and .py files into a src folder

@@ -1,0 +1,29 @@
+#!/bin/bash
+#Run this in the root directory like so
+#wsd.sh [test data key] 
+key=$1
+batch=$2
+
+#Edit the nested for loops to select a series of feature combinations
+run=2000
+echo '#!/bin/bash'
+for classifier in -pn -t; do
+  for bootstrap in '' '-b 2' '-b 4' ; do #Fix how a lack of bootstrapping for trees doesn't work well here
+    for colocation in '-l 0' '-l 1' '-l 2' '-l 3'; do # -l NUM is the colocation distance, 0 is "don't use it"
+      for coocurrence in '' -r; do # -r enables cooccurrence usage
+        for base_word in '' -e; do # -e enables base word usage
+          for dependency in '' -a; do
+
+#Run the actual system
+#echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word -i EnglishLS.train/EnglishLS.subtest > experiment/trainingSystem/tmp$run"|
+echo "./classify.py $classifier $bootstrap $colocation $coocurrence $base_word $dependency > experiment/$batch/tmp$run"|
+#Remove runs with bootstrapping and trees
+grep -v '\-t \-b' 
+run=$((run+1))
+
+          done
+        done
+      done
+    done
+  done
+done

### 2011-04-14 src/wsd-alec.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+batch=batch$1
+key=EnglishLS.test/EnglishLS.test.key
+mkdir experiment/$batch
+bash scripts/make_calls-alec.sh $key $batch> experiment/$batch/calls.sh
+cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
+bash experiment/$batch/calls.sh
+bash scripts/score_calls.sh experiment/$batch $key

### 2011-04-14 src/wsd.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+batch=batch$1
+key=EnglishLS.test/EnglishLS.test.key
+mkdir experiment/$batch
+bash scripts/make_calls.sh $key $batch> experiment/$batch/calls.sh
+cat experiment/$batch/calls.sh|bash scripts/calls2csv.sh > experiment/$batch/calls.csv
+bash experiment/$batch/calls.sh
+bash scripts/score_calls.sh experiment/$batch $key
+bash scripts/score_calls-aggregated experiment/$batch $key| sed 's/-attempted//' > experiment/$batch/scores.csv

### 2011-04-14 src/wsd3.sh

@@ -1,0 +1,8 @@
+#!/bin/bash
+batch=batch$1
+key=EnglishLS.test/EnglishLS.test.key
+mkdir experiment/$batch
+bash scripts/make_calls-smp3.sh $key $batch> experiment/$batch/calls3.sh
+cat experiment/$batch/calls3.sh|bash scripts/calls2csv.sh > experiment/$batch/calls3.csv
+bash experiment/$batch/calls3.sh
+bash scripts/score_calls3.sh experiment/$batch $key

### 2011-04-14 paper/paper.tex
remove fig1
meh
remove junk from paper

@@
 
-\subsection{Selecting optimal feature combination}
-\newcommand\ward{backward} %or maybe backwards
-
-We used a \ward stepwise approach to identifying optimal feature combinations.
-We first ran the system with all features on, producing a total of $256=2^8$
-combinations.  We then used backwards stepwise regression to identify feature
-combinations with a small number of features but with high performance
-
 \section{System}
@@
 \section{Methods}
-\newcommand\few{few}
-
 We ran the system with several hundred different combinations of features over
@@
 
-We ran a more detailed analysis on the top \few systems.  This analysis included
+We ran a more detailed analysis on the top system.  This analysis included
 consideration of all three grain-levels of score and scores by word.
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[width=\textwidth]{baseline}
@@
 
-\begin{figure}
-\includegraphics[width=\textwidth]{pg_0001}
-\caption{\label{fig1}}
-\end{figure}
+%\begin{figure}[H]
+%\includegraphics[width=\textwidth]{pg_0001}
+%\caption{\label{fig1}}
+%\end{figure}
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[width=\textwidth]{pg_0002}
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[width=\textwidth]{pg_0003}
@@
 
-\begin{figure}
+\begin{figure}[H]
 \includegraphics[width=\textwidth]{pg_0004}

### 2011-04-14 paper/paper.tex
Merged the discarded collocation section with the original
paper captions

@@
 \includegraphics[width=\textwidth]{pg_0004}
-\caption{\label{fig4}}
+\caption{\label{fig4}The scores of systems with colocation window between 2 and 4, cooccurrence handling on, \naive{} Bayes classifier and dependency parsing off are presented here.
+Each plotted number corresponds to a system, and the number refers to the colocation window}
 \end{figure}
@@
 
-We ran two baselines, one with each machine learning algorithm:
+We ran two baselines, one with each machine learning algorithm (table \ref{tab:base} and figure \ref{fig:base}).
 
+\begin{table}
 \begin{tabular}{l l | r r r}
@@
 \end{tabular}
+\caption{\label{tab:base}Scores for the baseline system}
+\end{table}
 

### 2011-04-14 paper/paper.tex

@@
 We rendered a feature for each position covered, and set its value to be the
-word at that position.
+word at that position. We also used NLTK's part of speech tagger to
+tag the context, and included those as we did the literal words in the
+feature set.  This was trained on NLTK's
+\verb+maximum entropy treebank pos tagger+ data, which is included
+with the NLTK package.
 
-We also used NLTK's part of speech tagger to tag the context, and included those
-as we did the literal words in the feature set.  This was trained on NLTK's
-\verb+maximum entropy treebank pos tagger+ data, which is included with the NLTK
-package.
+Collocation seemed to be fairly powerful at disambiguating, which is to be
+expected, since function words near to the target word can be very strong
+predictors of how the word is being used in context.  Effectiveness was
+strongest with words close to the target, and weaker the farther away we
+extended the feature.
 
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 \includegraphics[width=\textwidth]{baseline}
@@
 
-%\begin{figure}[H]
+%\begin{figure}[h]
 %\includegraphics[width=\textwidth]{pg_0001}
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 \includegraphics[width=\textwidth]{pg_0002}
@@
 
-\begin{figure}[H]
+\begin{figure}
 \includegraphics[width=\textwidth]{pg_0003}
@@
 
-\begin{figure}[H]
+According to Figure \ref{fig3}, when the base word feature vector was
+enabled and the dependency parsing was disabled, the \naive{} Bayes
+classifier improved in performance. On the other hand, the performance
+of the Decision Tree classifier seems to be independent of the base
+word and dependency parsing features.
+
+\begin{figure}
 \includegraphics[width=\textwidth]{pg_0004}
@@
 
-\subsubsection{Collocation}
-
-Collocation seemed to be fairly powerful at disambiguating, which is to be
-expected, since function words near to the target word can be very strong
-predictors of how the word is being used in context.  Effectiveness was
-strongest with words close to the target, and weaker the farther away we
-extended the feature.
-
 \subsubsection{Interactions Between Features}

### 2011-04-14 paper/paper.tex

--- 2011-04-14 paper/paper.tex
@@
 
-%\begin{figure}[H]
-%\includegraphics[width=\textwidth]{pg_0001}
-%\caption{\label{fig1}}
-%\end{figure}
+\begin{figure}[h]
+\includegraphics[width=\textwidth]{pg_0001}
+\caption{\label{fig1}}
+\end{figure}
 

### 2011-04-14 paper/paper.tex

@@
 allowing for multiple senses) again to match the Senseval-2  format.
+
+\subsection{Selecting optimal feature combination}
+\newcommand\ward{backward} %or maybe backwards
+
+We used a \ward stepwise approach to identifying optimal feature combinations.
+We first ran the system with all features on, producing a total of $256=2^8$
+combinations.  We then used backwards stepwise regression to identify feature
+combinations with a small number of features but with high performance
 
@@
 \section{Methods}
+\newcommand\few{few}
+
 We ran the system with several hundred different combinations of features over
@@
 
-We ran a more detailed analysis on the top system.  This analysis included
+We ran a more detailed analysis on the top \few systems.  This analysis included
 consideration of all three grain-levels of score and scores by word.

### 2011-04-14 paper/paper.tex

--- 2011-04-14 paper/paper.tex
@@
 \includegraphics[width=\textwidth]{pg_0004}
-\caption{\label{fig4}The scores of systems with colocation window between 2 and 4, cooccurrence handling on, \naive{} Bayes classifier and dependency parsing off are presented here.
-Each plotted number corresponds to a system, and the number refers to the colocation window}
+\caption{\label{fig4}The scores of systems with collocation window between 2 and 4, cooccurrence handling on, \naive{} Bayes classifier and dependency parsing off are presented here.
+Each plotted number corresponds to a system, and the number refers to the collocation window}
 \end{figure}

### 2011-04-14 paper/paper.tex
commas
meh

@@
 \author{
-Alec Story
-Ansu Abraham
-Craig Frey\\
-Dustin Tiedemann
-Michael Zhu
-Thomas Levine
+Alec Story,
+Ansu Abraham,
+Craig Frey,\\
+Dustin Tiedemann,
+Michael Zhu,
+Thomas Levine,
 Whitney Foster\\
@@
 
-%\begin{figure}[h]
-%\includegraphics[width=\textwidth]{pg_0001}
-%\caption{\label{fig1}}
-%\end{figure}
-
 Collocation window of size 2--4 had the best performance (figure
@@
 \includegraphics[width=\textwidth]{pg_0003}
-\caption{\label{fig3}}
+\caption{\label{fig3}Performance for systems with collocation window of size between 2 and 4}
 \end{figure}
@@
 no dependency parsing, and bootstrapped once:
-
+\newpage
 \begin{longtable}{l | r r r r r r r}

### 2011-04-14 experiment/analyze.R
fix plot

@@ -166,7 +166,7 @@ plot.step1=function(){
 	ag=plot.step.import()
 	ggplot(ag,aes(colocation,f,group=c(cooccurrence)))+
 	geom_point(aes(color=cooccurrence),position=position_jitter(w=0.1, h=0))+
-	opts(title = expression("The optimal colocation window is between 3 and 4 words"))
+	opts(title = expression("The optimal colocation window is between 2 and 4 words"))
 #	opts(title = expression("Performance of all of our systems"))+
 #	scale_x_continuous('Colocation window size') + scale_y_continuous('Mixed-grained F-measure')
 }

### 2011-04-14 paper/paper.tex
paper edits 1 2

@@
 
-We wrote our main control program, classify.py, so that it can choose either
-\Naive{} Bayes or Decision Trees classifier and any 
-combination of  features. On top of this we wrote bash scripts that automated
-looping through every combination of classifiers and features, along with
-porting the results directly into the scorer.  Classify.py includes a help
-switch -h, that explains the switches that control the different classifiers
-and features along with any additional parameters that a certain feature might
-support (for example, collocation has a window size parameter which defaults to
-0) Performance was excellent for most of the features, allowing us to typically
-run all of the words in the test set through every combination a classifier and
-feature set in under an hour. (The number of runs can get quite high when you
-factor in several parameters per feature, not just on/off)
+We wrote our main control program, classify.py, so that it can choose either the
+\naive{} Bayes or decision tree classifier and any combination of  features. On
+top of this we wrote bash scripts that automated looping through every
+combination of classifiers and features, along with porting the results directly
+into the scorer.  \verb+classify.py+ includes a help switch -h, that explains
+the switches that control the different classifiers and features along with any
+additional parameters that a certain feature might support (for example,
+collocation has a window size parameter which defaults to 0) Performance was
+excellent for most of the features, allowing us to typically run all of the
+words in the test set through every combination a classifier and feature set in
+under an hour, although dependency parsing was slow (The number of runs can get
+quite high when you factor in several parameters per feature, not just on/off)
 
@@
 
-The NLTK was used to implement two machine learning algorithms, \naive{} Bayes and
-decision trees.
+NLTK provided several machine learning algorithms, and we used the two that we
+were able to get running on our systems, \naive{} Bayes and decision tree.
 
@@
 
-The NLTK implements a \naive{} Bayes classifier which chooses the best sense given a
+NLTK implements a \naive{} Bayes classifier which chooses the best sense given a
 dictionary of features and assigns confidence probabilities to the chosen
@@
 
-\subsubsection{Decision Tree}
+\subsubsection{decision tree}
 
-The NLTK also implements a decision list classifier in which a sequence of
-tests is applied to each target-word feature vector. Each test indicates a
-particular sense of the word: if the test succeeds, the sense of the test is
-returned otherwise the next test in the sequence is performed.
+NLTK also implements a decision tree classifier in which a sequence of tests is
+applied to each target word feature vector. Each test indicates a particular
+sense of the word: if the test succeeds, the sense of the test is returned
+otherwise the next test in the sequence is performed.
 
@@
 Fortunately, the classifiers were very fast, and almost all of the time the
-system spends is in reading input and building feature sets, which don't need
-to be repeated, so bootstrapping is very cheap to include.  The probability measure that we used for the algorithm was 0.8
+system spends is in reading input and building feature sets, which don't need to
+be repeated, so bootstrapping is very cheap to include.  The probability measure
+that we used for the algorithm was 0.8
 
-% Should we mention which probability measure we used?  Which did we use?  How
-% many iterations?
+For simplicity, we did not vary the cutoff values for bootstrapping or for
+confidence.
 
@@
 As the regression table above shows, it seems that substituting the
-Decision Tree classifier for the Naive Bayes baseline provides the
+decision tree classifier for the \naive{} Bayes baseline provides the
 most significant boost to our f measure. It can also be seen here that
@@
 measure may affect the f measure negatively. For instance, the row
-showing ``classifiert:collocation'' indicates a run where the Decision
-Tree classifier was used and the collocation feature was enabled has
+showing ``classifiert:collocation'' indicates a run where the decision
+tree classifier was used and the collocation feature was enabled has
 resulted in a lower accuracy. This seems to be the general trend for
@@
 
-Figure \ref{fig:base} shows our results for running just the Decision
-Tree classifier and the \naive{} Bayes classifier with no features
-enabled. With no bootstrapping, the Decision Tree classifier has a
-much higher f-measure. With bootstrapping, the Decision Tree
+Figure \ref{fig:base} shows our results for running just the decision
+tree classifier and the \naive{} Bayes classifier with no features
+enabled. With no bootstrapping, the decision tree classifier has a
+much higher f-measure. With bootstrapping, the decision tree
 classifier decreases in f-measure while the \naive{} Bayes classifier
@@
 classifier improved in performance. On the other hand, the performance
-of the Decision Tree classifier seems to be independent of the base
+of the decision tree classifier seems to be independent of the base
 word and dependency parsing features.

### 2011-04-14 paper/paper.tex
minor

@@
 combination of classifiers and features, along with porting the results directly
-into the scorer.  \verb+classify.py+ includes a help switch -h, that explains
-the switches that control the different classifiers and features along with any
-additional parameters that a certain feature might support (for example,
-collocation has a window size parameter which defaults to 0) Performance was
-excellent for most of the features, allowing us to typically run all of the
-words in the test set through every combination a classifier and feature set in
-under an hour, although dependency parsing was slow (The number of runs can get
-quite high when you factor in several parameters per feature, not just on/off)
+into the scorer.  \verb+classify.py+ includes a help switch \verb+-h+, that
+explains the switches that control the different classifiers and features along
+with any additional parameters that a certain feature might support (for
+example, collocation has a window size parameter which defaults to 0)
+Performance was excellent for most of the features, allowing us to typically run
+all of the words in the test set through every combination a classifier and
+feature set in under an hour, although dependency parsing was slow (The number
+of runs can get quite high when you factor in several parameters per feature,
+not just on/off)
 
